### 2019-11-25 main.tex
move the paper to an independent git repository

\documentclass[aps,twocolumn,showpacs,groupedaddress, nofootinbib]{revtex4}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
%\usepackage{graphicx}  % needed for figures
\usepackage{graphicx} % omit 'demo' for real document
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage{acronym}   % for acronym
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage{url}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{natbib}
%\usepackage[natbib, maxcitenames=3]{biblatex}
%\usepackage[maxnames=3]{biblatex}
\usepackage{subfigure}
\usepackage{amsmath}
%\usepackage[font=small,labelfont=bf,justification=justified,format=plain]{caption}
%\usepackage{booktabs, siunitx}

%\usepackage[numbers,sort]{natbib}
\bibliographystyle{unsrt3}
%\usepackage{subcaption}
%\captionsetup[figure]{slc=off} % "slc" is an abbreviation for "singlelinecheck"

% avoids incorrect hyphenation, added Nov/08 by SSR
%\hyphenation{ALPGEN}
%\hyphenation{EVTGEN}
%\hyphenation{PYTHIA}
%\renewcommand{\bibfont}{\normalfont\small}

%\renewcommand*{\footnote}{\arabic{footnote}}

%\renewcommand{\thempfootnote}{\arabic{mpfootnote}}

\newcommand{\dcc}{LIGO-P1700428}
\newcommand{\cm}[1]{\textbf{\textcolor{red}{CM: #1}}}
\newcommand{\MC}[1]{\textcolor{red}{MC: #1}}

\def\ra{\ensuremath\rightarrow}

%% ----- input git-version tag
%\input{tag.tex}

\begin{document}

% The following information is for internal review, please remove them for submission
\widetext
%\leftline{Version xx as of \today}

% the following line is for submission, including submission to the arXiv!!
%\hspace{5.2in} \mbox{Fermilab-Pub-04/xxx-E}

\title{Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach}
%\input author_list.tex       % D0 authors (remove the first 3 lines
                             % of this file prior to submission, they
                             % contain a time stamp for the authorlist)
                             % (includes institutions and visitors)
%\author{Man Leong Chan$^1$, Chris Messenger$^1$, Ik Siong Heng$^1$, Martin Hendry$^1$ $\&$ Yan Bei Chen$^2$}
%\affiliation{[1.0\linewidth]$^1$SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, UK\\
%$^2$ Caltech, Pasadena, California 91125, USA}
 %$^2$ TianQin Research Center for Gravitational Physics, Sun Yat-sen University, China\\
 %$^3$ Tsinghua University, Beijing, China\\
 %$^4$ University of Western Australia, Australia\\
 %$^5$ Caltech, California, United States}

\author{Authors$^{12}$}
\affiliation{
$^1$Department of Applied Physics, Fukuoka University, Nanakuma 8-19-1, Fukuoka 814-0180, Japan\\
$^2$SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, UK}
%$^2$Caltech CaRT, Pasadena, California 91125, USA}
%\date{\today}
%\date{\commitDATE\\\mbox{\small \commitID}\\\mbox{\dcc}}

\begin{abstract}
We demonstrate the application of a convolutional neural network 
to the gravitational wave signals from core collapse supernovae.
Using simulated time series of gravitational wave detectors, 
we show that a convolutional neural network can be used to detect and classify, based on the explosion mechanisms,  
the gravitational wave signals buried in noise.
For the waveforms used in the training of the convolutional neural network, 
our results suggest that a network of advanced LIGO, advanced VIRGO and KAGRA, or a network of LIGO A+, advanced VIRGO and KAGRA
is likely to detect a magnetorotational core collapse supernovae within the Large and Small Magellanic Clouds, or 
a Galactic event if the explosion mechanism is the neutrino-driven mechanism.
By testing the convolutional neural network with waveforms not used for training, 
we show that the true alarm probabilities are $52\%$ and $83\%$ at $60$kpc for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$.
For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the true alarm probabilities are $70\%$ and $93\%$ respectively. All at false alarm probability equal to $0.1$.
\end{abstract}
\pacs{}
\maketitle
\acrodef{GW}[GW]{gravitational wave}
\acrodef{BNS}[BNS]{binary neutron star}
\acrodef{BBH}[BBH]{binary black hole}
\acrodef{NSBH}[NSBH]{neutron star black hole}
\acrodef{EM}[EM]{electromagnetic}
\acrodef{CBC}[CBC]{compact binary coalescence}
\acrodef{CNN}[CNN]{Convolutional neural network}
\acrodef{CCSN}[CCSN]{core collapse supernova}
\acrodefplural{CCSN}[CCSNe]{core collapse supernovae}
\acrodef{ROC}[ROC]{receiver operator characteristic}
\acrodef{TAP}[TAP]{true alarm probability}
\acrodef{FAP}[FAP]{false alarm probability}
\acrodef{aLIGO}[aLIGO]{advanced LIGO}
\acrodef{AdVirgo}[AdVirgo]{advanced VIRGO}

\section{Introduction}
Since 2015 when LIGO has made the first direct observation of \acp{GW} from the merger of a binary black hole\cite{abbott2016observation},
there have been numerous observations of \acp{GW} from similar systems in the observation runs of LIGO 
and VIRGO \cite{abbott2016gw151226, abbott2017gw170608, abbott2017gw170814}.
These discoveries have been a crucial milestone in \ac{GW} astronomy and have opened up a new window on the sky.
More recently, LIGO and VIRGO have observed the \acp{GW} from a binary neutron star merger\cite{abbott2017gw170817, abbott2017gravitational, abbott2017multi}.
For this event, the \acp{GW} and the associated gamma-ray burst were observed simultaneously. 
Other counterparts across the electromagnetic spectrum were also observed by later follow-up observations \cite{abbott2017multi}.
In the near future, many more observations of \acp{GW} from similar compact binary coalescence systems can be expected
as KAGRA starts joint observations with LIGO and VIRGO \cite{aso2013interferometer, somiya2012detector, abbott2018prospects}.

In addition to compact binary coalescences, massive stars with $10-100 \text{M}_\odot $ at zeros-age main sequence ending their lives by becoming 
%with core of $10-100 \text{M}_\odot $ prior to collapse 
\acp{CCSN} are also considered to be potential sources to the second generation detectors such as the \ac{aLIGO} \cite{aasi2015advanced}, 
\ac{AdVirgo} \cite{acernese2014advanced} and KAGRA interferometers \cite{aso2013interferometer, gossan2016observing, abbott2016first}.
It is currently not entirely clear to astronomers how such a massive star becomes supernova. 
The basic theory of the explosion, confirmed by the neutrino events observed from SN1987A\cite{sato1987analysis}, goes as the following.
A massive star at the final stage of its life will form core that is composed of iron nuclei after it has burned all its stellar fuel via nuclear reaction.
The iron core is supported by the pressure of relativistic degenerate electrons.
If the mass of the core exceeds the effective Chandrasekhar mass\cite{baron1990effect, bethe1990supernova}, core collapse will ensue and continue until it reaches nuclear density.
The nuclear equation of state will then stiffens by the strong nuclear force above the nuclear density and stops 
the core collapse.
The inner core will bounce back and a shock wave will be sent through the infalling matter.
By losing energy to the dissociation of the iron nuclei and to neutrino cooling, the shock wave will stall.
For the star to become a supernova, the shock wave will need to be revived\cite{o2011black}.  
The mechanism via which the shock wave is revived and causes the explosion has been the subject of intense study.
However, it still remains an unsolved problem.

There exist two most popular theories, the neutrino-driven mechanism\cite{bethe1985revival, bethe1990supernova} and the magnetorotational mechanism\cite{janka2012explosion, kotake2012core, mezzacappa2014two}.
For supernova progenitors with core rotation too slow to affect the dynamics\cite{takiwaki2016three, summa2018rotation}, the neutrino-driven mechanism is believed to be the active mechanism.
The majority of the observed \acp{CCSN} can be explained by the neutrino mechanism\cite{bruenn2016development}.
The neutrino mechanism\cite{bethe1985revival, janka2007theory} suggests that about $5-10\%$ of the outgoing neutrino luminosity is stored below the shock, 
which causes turbulence to occur and thermal pressure to increase.
The stalled shock can be revived by their combined effects\cite{couch2015role}. 
Producing a \ac{CCSN} via the neutrino mechanism may also require convection and the standing accretion shock instability\cite{blondin2003stability}.
On the other hand, the magnetorotational mechanism requires rapid core spin and strong magnetic field\cite{leblanc1970numerical, burrows2007simulations, takiwaki2009special, moiseenko2006magnetorotational,mosta2014magnetorotational}. 
Together, they may produce an outflow that may cause the most energetic \acp{CCSN} observed.
The magnetorotational mechanism may be able to explain the extreme hypernovae and the observed long gamma-ray bursts\cite{woosley2006progenitor, yoon2005evolution, de2013rotation}.

Correctly classifying the \ac{GW} from a \ac{CCSN} is important in understanding the explosion mechanism.
%Electromagnetic observations provide only indirect informations about the mechanism of a \ac{CCSN} 
%because photons interact strongly with matter and only information from the optically thin regions far from the central core could reach us. 
%However, 
As \acp{GW} are emitted in the central core of a \ac{CCSN}, 
they are likely to carry direct information of the \ac{CCSN} and therefore provide a probe of the explosion mechanism that produces them.
In \ac{GW} astronomy, when it comes to the search for signals from compact binary coalescences, the established routine is matched filtering.
However, as the emission process of the \acp{GW} from \acp{CCSN} is affected by turbulence in the post-bounce and is stochastic in nature,  
the signal evolution cannot be predicted robustly\cite{ott2009gravitational, kotake2013multiple, kotake2009stochastic}.
This in turn prevents the match filtering routine to be applied to \acp{CCSN}.
%Although, Neutrino radiation-hydrodynamics simulations have been an ongoing effort to decode and understand explosion mechanism of \acp{CCSN} and the \acp{GW} they produce\cite{ott2009gravitational}.
Methods and algorithms have been developed for the detection and classification of signals from \acp{CCSN}. 
For example, a method known as principle component analysis has been developed\cite{heng2009rotating, rover2009bayesian, powell2015classification, powell2017classification, suvorova2019reconstructing}.
This method creates a set of component basis vectors from a set of \ac{CCSN} waveforms of a particular mechanism
that represent the common features of the waveforms of that mechanism.
There have been other approaches developed in the literature such as Bayesian inference\cite{rover2009bayesian}, Bayesian model selection\cite{logue2012inferring}
, multivariate regression model\cite{engels2014multivariate}, maximum entropy\cite{summerscales2008maximum}, 
maximum likelihood\cite{gursel1989near} and Tikhonov regularization scheme\cite{rakhmanov2006rank, hayama2007coherent}.

In recent years, the field of machine learning and its sub-field, deep learning, have been rapidly developing because of 
its potentials in many fields \cite{krizhevsky2012imagenet, NIPS2014_5423, simonyan2014very, chen2014semantic, zeiler2014visualizing, szegedy2015going}.
For example, deep learning have been successfully applied to fields including medical diagnosis\cite{kononenko2001machine}, object detection\cite{redmon2016you}, image recognition/processing/generation\cite{he2016deep, krizhevsky2012imagenet, zhang2016colorful, karpathy2015deep},    and  language processing\cite{lample2016neural}.
In \ac{GW} astronomy, deep learning has mostly been applied to both the identifications of glitch\cite{mukund2017transient, zevin2017gravity, george2017deep, gabbard2018matching} and signals\cite{george2018deep, astone2018new}. 
\ac{CNN} is a deep learning algorithm that has the advantage of capturing spatial and temporal features of the input data.
Another advantage of the use of a \ac{CNN} in the detection of a signal is that a \ac{CNN} is relatively computationally cheap compared to other more traditional methods.
This is because the heavy computational work is usually done during the training stage of a \ac{CNN} prior to its actual application\cite{goodfellow2016deep}.

In this work, we demonstrate a \ac{CNN} can be applied to the detection of the \acp{GW} from \acp{CCSN}
and the classification of their explosion mechanisms.
To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a number of studies and simlate sources 
at a range of distances from $10$ to $200$ kpc for two networks of four detectors.
The first network consists of \ac{aLIGO}, \ac{AdVirgo} and KAGRA.
For the second network, we still include the detectors of \ac{AdVirgo} and KAGRA,  
but replace the two detectors of \ac{aLIGO} with 
a modest set of planned upgrade version of them - LIGO A+ in Hanford and Livingston\cite{miller2015prospects, LIGOW}.
We will then apply the \ac{CNN} to waveforms excluded from the training session to show that the \ac{CNN} 
is not only able to identify the waveforms it familiarised itself with during training, but also new waveforms.

The remaining of this paper is constructed as follows. 
In section \ref{sec:CNN}, we will present a brief explanation of the concept of \ac{CNN} as well as the \ac{CNN} we used for this work.
In section \ref{sec:spwf}, we introduce the waveforms we use for the training of the \ac{CNN} in this work. We will also discuss the procedure with which we generated the data for the \ac{CNN}.
The results will be shown in sections \ref{sec:result} and \ref{sec:unseen}, followed by a conclusion in section \ref{sec:conclusion}.
%\section{Supernova waveform}\label{sec:spwf}

\section{Convolutional Neural network}\label{sec:CNN}
A \ac{CNN} is a computational processing system that is composed of interconnected layers of computational nodes\cite{o2015introduction}.
The nodes are known as neurons and are associated with an activation function.
The activation function can perform an elementwise nonlinear operation to the input of the layer. 
In a \ac{CNN}, there are three types of layers: convolutional layer, max-pooling layer, and fully connected layer\cite{o2015introduction}.
Convolutional layer performs the mathematical operation of convolution between the weights of the layer's neurons and the input to that layer.
Max-pooling layer is just a down-sampling layer that down samples the input along its dimensionality.
It can reduce the computational cost by decreasing the number of parameters of the \ac{CNN}.
Fully connected layer is a layer that connects every neuron in its layer to every neuron of its immediate previous and next layer.
In the case of detection and classification, fully connected layers are used to compute class scores.

When multiple layers of these three types are stacked and connected one after the other, 
a \ac{CNN} has been formed, where the output of each layer is the input of the next layer.
How these layers are connected in a \ac{CNN} is known as the architecture of the \ac{CNN}.
It describes the structure of a \ac{CNN} and the number of neurons in each layer. % (width and depth) 
In general, the first layer in a \ac{CNN}, also known as the input layer, is often a convolutional layer, 
while the last layer or the output layer is often a fully connected layer with an associated loss function. 
The architecture of the rest of the \ac{CNN} should depend on the specific task that the \ac{CNN} is trained to solve. 
An over-complicated model with too many trainable parameters 
is easier to result in overfit and harder to train, 
while a too-simple \ac{CNN} will have a hard time capturing the feature inherent to the input.
In addition, the number of layers and neurons of each layer in a \ac{CNN} are known as hyperparameters.
Other hyperparameters include the parameters of max-pooling layers, type of activation functions, 
learning rate of the \ac{CNN}, and the application of specific deep learning techniques if there is any.
The optimal combination of hyperparameters and the architecture is sought by trail and error, and fine tunning.

During the training stage, the weights of the neurons in a \ac{CNN} are updated using an algorithm called back propagation\cite{lecun1988theoretical}.
The output of the \ac{CNN} is used as an input to the loss function associated with the output layer. 
The back propagation algorithm will then compute the gradient of the loss function 
which is used to adjust the values of the weights of the neurons in each layer and minimise the loss function.
When the loss function is minimised, the \ac{CNN} will classify its input into the correct category with the highest confidence. 
The process of achieving the minimisation of the loss function during the training stage is referred to as learning.

In this work, we employ a \ac{CNN} of $8$ convolutional layers, $3$ max-pooling layers, and $3$ fully connected layers.
The exact architecture of the \ac{CNN} is shown in Table \ref{table:architecture} and illustrated in Figure \ref{fig:CNN}.
\begin{table}[]
\centering
\begin{threeparttable}
\caption{The architecture of the \ac{CNN}}
\label{table:architecture}
\begin{tabular}{ccccc}
\\
\toprule
Layer & Type      & Neurons  & Filter size & Act. Fun \\ \hline
1     & Conv      & 11        & 32          & Elu      \\ 
2     & Max-pool  &          & 8          &          \\
3     & Conv      & 11        & 8          & Elu      \\
4     & Max-pool  &          & 6           &          \\
5     & Conv      & 11       & 6           & Elu      \\
6     & Conv      & 11       & 4           & Elu      \\
7     & Conv      & 13       & 4           & Elu      \\
8     & Conv      & 13       & 4           & Elu      \\
9     & Conv      & 13       & 4           & Elu      \\
10    & Conv      & 13       & 4           & Elu      \\
11    & Max-pool  &          & 2           &          \\
12    & Fully-con & 64(50\%) &             & Elu      \\
13    & Fully-con & 32(50\%) &             & Elu      \\
14    & Fully-con & 3        &             & Softmax      \\ 
\hline
\hline
\end{tabular}
\begin{tablenotes}
\setlength\labelsep{0pt}
\normalfont{
\item The architecture of the \ac{CNN} used in this work for the purpose of distinguishing supernova signal mechanisms and background noise.
In the table, Conv means convolutional neural layer, Max-pool max-pooling layer, and Fully-con fully-connected layers.
Neuron and Act. Fun mean the number of neurons and the activation function for the layer respectively. 
The numbers in the bracket for the fully-connected layers are the number used for drop-out.}
\end{tablenotes}
\end{threeparttable}
\end{table}
\begin{figure}
\includegraphics[width=0.48\textwidth]{CNN2.png}
\caption{An illustration of the architecture of the \ac{CNN} used in this paper for the detection and classification of \ac{CCSN} signals in noisy data.
The \ac{CNN} consists of $8$ convolutional layers, $3$ max-pooling layers and $3$ fully connected layer including the output layer.
The input layer takes the simulated time series of the detectors as input, feeding through the \ac{CNN}. The \ac{CNN} will output three probabilities at the last layer.
The numbers above or below each layer indicate the kernal size of the layer. For example, the first convolutional layer has $11$ filters, 
each of which is $1$ by $32$ in size. 
The elements in the figure are not to scale.
\label{fig:CNN}}
\end{figure}
Since the problem we are trying to solve is a problem of multi-class classification, 
the loss function employed for this work is categorical cross entropy\cite{abadi2016tensorflow}, given by
\begin{equation}\label{eq:cce}
 L(y,\hat{y}) = -\sum^M_{j=1}\sum^C_{i=1}(y_{ij}log(\hat{y}_{ij})),
\end{equation}
where $C$ is the number of the classes and $M$ is the number of the training samples.
For the $j^{\text{th}}$ sample and the $i^{th}$ class, $y_{ij}$ is the correponding class value. It is equal to $1$ for the true class and $0$ otherwise.
Similarly, $\hat{y}_{ij}$ is the predicted probability from the \ac{CNN} for the $i^{th}$ class and the $j^{\text{th}}$ sample.

\section{Data}\label{sec:spwf}
We establish a \ac{CNN} for the purpose of distinguishing detector time series among three classes, 
i.e., magnetorotational signals + background noise, neutrino-driven signals + background noise, and pure background noise. 
For this purpose, it is necessary to prepare training, validation and testing data of these three classes.
The training data is used for tuning the weights of the neurons in the layers in the \ac{CNN}, 
while validating data is to verify that the \ac{CNN} is learning the features inherent to the data and testing data is to test the performance of the trained \ac{CNN}.

In general, the input of a \ac{CNN} is numerical data.
In our case, a data sample is a set of simulated time series stacked together as a $k \times p$ matrix 
where $k$ is the number of detectors and $p$ the number of elements in the time series.
To this end, we use simulated waveforms in the literature.
The magnetorotational \ac{CCSN} signals are taken from\cite{abdikamalov2014measuring, dimmelmeier2008gravitational, richers2017equation}. 
The simulations in \cite{abdikamalov2014measuring} were focused on the dependence of the waveforms on the angular momentum distrubion of the progenitors and generated 92 waveforms.
In \cite{dimmelmeier2008gravitational}, 136 waveforms were generated to investigate a variety of rotation rates and masses of the progenitors.
The simulations in \cite{richers2017equation} covered a parameter space of $18$ different equations of state and $98$ rotation profiles for a progenitor of $12M_{\odot}$ generating in total $1824$ waveforms.
All the simulations from the studies were 2D.
For the neutrino-driven mechanism, we employ the waveforms from\cite{10.1093mnrasstz990, kuroda2017correlated, muller2012parametrized, powell2019gravitational, 
radice2019characterizing, yakunin2015gravitational, yakunin2017gravitational, ott2009gravitational, murphy2009model, ott2013general}.
The simulations in \cite{10.1093mnrasstz990, kuroda2017correlated, muller2012parametrized, powell2019gravitational, 
radice2019characterizing, yakunin2017gravitational} were 3D while the simulations in \cite{yakunin2015gravitational, ott2009gravitational, murphy2009model, ott2013general} were 2D.
These simulations cover a wide range of progenitor masses from $9\text{M}_\odot$ to $60\text{M}_\odot$.
The progenitor masses of the simulations are shown in Table \ref{table:waveforms}.
\begin{table}[]
\centering
\begin{threeparttable}
\caption{Waveforms}
\label{table:waveforms}
\begin{tabular}{rccc}
\toprule
                         & Mechanism         & Mass ($\text{M}_\odot$)                         & No.  \\
\hline                         
Abdikamalov\cite{abdikamalov2014measuring} & M   & 12.0                          & 92   \\
Dimmelmeier\cite{dimmelmeier2008gravitational} & M   & 11.2,15.0,20.0,40.0        & 136  \\
Richers\cite{richers2017equation}     & M   & 12.0                          & 1824 \\
Andresen\cite{10.1093mnrasstz990}    & N   & 15.0                          & 6    \\
Kuroda\cite{kuroda2017correlated}      & N   & 11.2,15.0                    & 2    \\
Muller\cite{muller2012parametrized}      & N   & 15.0,20.0                    & 6    \\
Murphy\cite{murphy2009model}      & N   & 12.0,15.0,20.0,40.0        & 16   \\
Ott$_1$\cite{ott2009gravitational}       & N   & 15.0                          & 2    \\
Ott$_2$\cite{ott2013general}       & N   & 27.0                          & 8    \\
Powell\cite{powell2019gravitational}      & N   & 3.5,18.0                      & 2    \\
Radice\cite{radice2019characterizing}      & N   & 9,10,11,12,13,19,25,60 & 8    \\
Yakunin$_1$\cite{yakunin2015gravitational}   & N   & 12,15,20,25                & 4    \\
Yakunin$_2$\cite{yakunin2017gravitational}   & N   & 15                            & 1   \\
\hline
\hline
\end{tabular}
\begin{tablenotes}
\setlength\labelsep{0pt}
\normalfont{
\item The mass range of the progenitors of the simulated waveforms used in this work.
The first column refers to the studies. Mechanism indicates the explosion mechanism for 
the waveforms, with M for the magnetorotational mechanism and N for the neutrino-driven mechanism.
Mass refers the mass, in solar mass, of the progenitors in the simulations. No. means the number of waveforms available from the study.}
\end{tablenotes}
\end{threeparttable}
\end{table}
%Anderson 2016 also does 3d, 20 mass, 11 mass
%kuroda 2017 3d, 15mass, 11mass
%powell 2018 3d 18mass, one model
%radics 9, 10, 11, 12, 13, 19, 25 and 60 mass 3d
%yakunin2015
%yakunin2017
%ott2009
%murphy2009model
%ott2013
%which cover both 2D simulations with masses of $15M_{\odot}$\cite{ott2009gravitational}, 
%and $12, 15, 20$ and $40M_{\odot}$\cite{murphy2009model}, and 3D simulations for a progenitor of $27M_{\odot}$\cite{ott2013general}.$26$ 
Examples of the simulated waveforms for both mechanisms are shown in Figures \ref{fig:magwaveforms} and \ref{fig:neuwaveforms}.
\begin{figure}
\includegraphics[width=0.5\textwidth]{mag_waveforms.png}
\caption{Examples of simulated waveforms used in the work for which the explosion mechanism is magnetorotational mechanism.
The top panel shows a waveform from\cite{abdikamalov2014measuring}. 
The progenitor is $12\text{M}_\odot$ with differential rotation parameter $A=300\text{km}$. 
The initial angular velocity at the core $\Omega_c$ is $8.5\text{rads/s}$.
The middle panel shows that from \cite{dimmelmeier2008gravitational}.
The simulation is done assuming a progenitor of $15\text{M}_\odot$ with $A=50$km and $\Omega_c = 1.91\text{rads/s}$.
The panel in the bottom shows a waveform from \cite{richers2017equation}. For this simulation, the progenitor is $12\text{M}_\odot$,  $A$ and $\Omega_c$ are $10000$km and $0.5\text{rad/s}$ respectively.
In all panels, only the $h+$ polarisations are shown because the simulations are axis-symmetric or 2D, and described by only one polarisation. 
The sources are assumed to be at $10$ kpc from earth. The time is not related to the time at core bounce.
\label{fig:magwaveforms}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{neu_waveforms.png}
\caption{Examples of simulated waveforms used in the work for which the explosion mechanism is neutrino-driven mechanism.
From the top to the bottom, the panels show waveforms from\cite{10.1093mnrasstz990, murphy2009model, radice2019characterizing}, with progenitors of masses equal to $15\text{M}_\odot$,
$15\text{M}_\odot$ and $60\text{M}_\odot$ respectively. 
The sources are assumed to be at $10$ kpc from earth. The time is not related to the time at core bounce.
\label{fig:neuwaveforms}}
\end{figure}
Introducing waveforms from a variety of studies essentially introduces a distribution of the waveforms that covers a larger parameter space, 
making the data samples harder for the \ac{CNN} to learn.
As a result, the performance of the trained \ac{CNN} on the testing samples 
may appear to be worse than that if the data were generated using only a subset of the waveforms.
However, a larger parameter space provides the advantage of forcing the \ac{CNN} to 
learn the features common among the waveforms, rather than a subset of the waveforms.
The trained network can thus perform better when facing waveforms with unexpected features, which is more likely in reality.

Since the waveforms are generated at various distances, sampling rates and durations, 
it is necessary to normalise the waveforms before they can be used for the generation of the time series.
To do this, we first scale the amplitudes of the waveforms by moving the sources to $10$ kpc from earth.
We then ensure that the sampling rate are identical for all the waveforms by down sampling 
them to a pre-selected sampling rate (e.g., $4096$Hz).
The longest duration $\tau$ among the waveforms is then identified and each of the remaining waveforms is padded with zeros
to this duration.
To introduce as less artefact as possible, a high pass filter with a low cut-off frequency equal to $11$Hz 
and a tukey window ($\alpha = 0.08$) are applied prior to the zero padding. 
To balance the difference in the number of waveforms 
between the two mechanisms in the final data set, $36$ copies of each neutrino-driven waveform are duplicated.
After this procedure, the simulated 
waveforms are then $\bold{S}(t) = \{\bold{s}_{1}(t), \bold{s}_{2}(t), ..., \bold{s}_{m}(t)\}$, where $m$ is the number of the waveforms and 
$\bold{s}_{q}$ is the $q^{\text{th}}$ waveform, defined by,
\begin{equation}\label{eq:ht}
 \bold{s}_q(t) = \left(\begin{array}{c}
                        h_q^+(t) \\
                        h_q^\times(t)
                       \end{array}\right),
\end{equation}
where $h_q^+(t)$ and $h_q^\times(t)$ are the two polarisations of the waveform and $t$ the time. 
As mentioned, some of the waveforms used in the work are generated with the simulations being axis-symmetric, the \acp{GW} are entirely described by one polarisation $h_q^+(t)$. 
The corresponding $h_q^\times(t)$ for these waveforms are a zero vector. 
In this work, we perform simulations for distances equal to $10$, $20$, $30$, $40$, $50$, $60$, $80$, $100$, $150$ and $200$ kpc.
If for a training session, the distance $d_\text{L}$ interested is not $10$ kpc, the following relationship is employed to scale the amplitudes of the waveforms,
\begin{equation}\label{eq:sap}
 \bold{s}^{d_\text{L}}_q(t) =  \frac{10\text{kpc}\times\bold{s}_q(t)}{d_\text{L}},
\end{equation}
where $\bold{s}^{d_\text{L}}_q(t)$ is the waveform if the source is at $d_\text{L}$ from earth.

The next step is to generate simulated time series for the \ac{GW} detectors in a network using $\bold{S}(t)$.
%The input data consist of simulated time-series from a network of \ac{GW} detectors.
Since the purpose of building a \ac{CNN} is to categorise an input data into three exclusive classes,
in total three types of time-series are generated.
For the time series containing either a magnetorotational signal or a neutrino-driven signal, 
we start by selecting a waveform $\bold{s}_q$ from $\bold{S}(t)$.
A random location of (right ascension, declination) $=(\alpha, \delta)$ in the sky is selected from a uniform distribution on $\alpha$ and a uniform distribution on the sine of $\delta$.
The corresponding antenna patterns $\bold{F}(\alpha, \delta, t)$, given by the following equation,
\begin{equation}\label{eq:ap}
\bold{F}(\alpha, \delta, t)= \left(\begin{array}{cc}
f_1^+(\alpha, \delta, t)~~f_1^\times(\alpha, \delta, t) \\
\vdots~~~~~~~~~~~~\vdots \\
f_k^+(\alpha, \delta, t)~~f_k^\times(\alpha, \delta, t) \\
\end{array}\right),
\end{equation}
is computed, 
where $f^+(\alpha, \delta, t)$ and $f^{\times}(\alpha, \delta, t)$ are the antenna pattern functions for the two polarizations and $k$ is the number of detectors as defined above.
The relative delays in the arrival times for the location are also computed and applied to the selected waveform.
The delay in arrival time between a detector and the center of the earth is given by,
\begin{equation}\label{eq:tdetector}
%
\Delta t = \frac{\bold{n} \cdot \bold{r}}{c},
%
\end{equation}
%
where $\bold{n}$ is the propagation direction of the \ac{GW}, $c$ the speed of light, and $\bold{r}$ the location vector of the detector
relative to the center of the Earth. 
The resulting signal $ \bold{h}_j(\alpha, \delta, t)$ as received at the detectors is then given by the following equation,
\begin{equation}\label{eq:ht2}
 \bold{h}_j(\alpha, \delta, t) = \bold{F}(\alpha, \delta, t) \times \bold{s}_q(t),
\end{equation}
where the time delays $\Delta t$ are absorbed into the corresponding notations and the subscript $j$ is defined in Eq.\ref{eq:cce}.
Next, we generate independent Gaussian noise $\bold{N}_j(t) = \{\bold{n}_{1j}(t), \bold{n}_{2j}(t), ..., \bold{n}_{kj}(t)\}'$ 
for each detector in the network using their respective power spectral densities.  
In the above notation, the symbol $'$ indicates transpose. 
%It is worth mentioning that although in reality, 
%noise at \ac{GW} detectors may not be entirely Gaussian and contaminated with glitches,
%the application of \ac{CNN} is actually not limited to time series where the noise is Gaussian.
%Although  we will focus on Gaussian noise in this work, 
%a \ac{CNN} can in fact be trained to identify the presence of a glitch in the data \cite{mukund2017transient, zevin2017gravity, george2017deep, gabbard2018matching}.
The duration of the generated noise is $1.6$ times longer than $ \bold{h}_j(\alpha, \delta, t)$. 
A random number $x$ will then be generated determining where in the generated noise the signal will be placed, as given by,
\begin{equation}
\bold{d}_j(\alpha, \delta, t, x)=
\begin{cases}
\bold{N}_j(t)~~~~~~~~~~~~~~~~~t < x; \\
\bold{N}_j(t) + \bold{h}_j(\alpha, \delta, t)~x \leq t \leq \tau + x; \\
\bold{N}_j(t)~~~~~~~~~~~~~~~~~t > \tau + x. \\
\end{cases}
\end{equation}
This is to avoid the possibility that the \ac{CNN} learns human artefact instead of common features of the waveforms by having the signals always starting at the same place.
For each time series of the background noise class, independently simulated Gaussian background noise of the same duration as that of the other classes 
are generated for each detectors in the network.
This means a data sample for this class is defined as,
\begin{equation}\label{eq:noise}
 \bold{d}_j(t) = \bold{N}_j(t).
\end{equation}

Since training a \ac{CNN} of a given structure to its maximum capacity requires many data samples, we augment our data set by iterating over $\bold{S}(t)$ until 
for each waveform in $\bold{S}(t)$, we have $31$ data samples $\bold{d}$ generated using the procedure described above.
This step is essential for the \ac{CNN} to learn the features of the waveforms and to identify them effectively under different noise scenarios.
After that, we generate independent noise realisations for the background noise class.
The entire data set $\bold{D}$ defined below, has roughly $l = 1.8 \times 10^{5}$ data samples, where each class has approximately $6\times10^{4}$ data samples.
\begin{equation}\label{eq:finaldata}
\bold{D}(\boldsymbol{\alpha}, \boldsymbol{\delta}, \boldsymbol{\delta_t}, \bold{t}, \bold{x}) =  \left(\begin{array}{c}
\bold{d}_1(\alpha, \delta, \delta_t, t, x) \\
\vdots \\
\bold{d}_o(\alpha, \delta, \delta_t, t, x) \\
\vdots \\
\bold{d}_l(t) \\
\end{array}\right).
\end{equation}
In the above equation, the subscript $o$ is the sum of the data samples in which there is a \ac{GW} signal in the time series. 
The final step is to whiten $\bold{D}$ using the power spectral densities.
In Figure \ref{fig:sample}, a representative example  of time series for one detector is shown. 
\begin{figure}
\includegraphics[width=0.5\textwidth]{datasample.png}
\caption{Representative example of the simulated time series used to train/validate/test the \ac{CNN}.
The blue shows a whitened time series with a signal buried in Gaussian noise of unit variance.
The red shows the same signal free of noise and whitened. 
\label{fig:sample}}
\end{figure}
A data sample consists of such time series of the same signal or background noise from all the detectors in the network.
The data samples are then split, with $1\times10^{4}$ samples being randomly taken for validation, $10\%$ of the rest for testing and $90\%$ for training.
When the training is finished for a distance, 
the above described procedure will be repeated for another distance until the training
for all distances have been carried out for a network.
The entire procedure is then repeated for another network of \ac{GW} detectors.
As mentioned previously, the \ac{CNN} will be trained for two networks of \ac{GW} detectors.
We present the networks in Table \ref{table:network}. For the remaining of the paper, we will use their acronyms to refer to the networks.
\begin{table}[]
\centering
\begin{threeparttable}
\caption{Detector networks}
\label{table:network}
\begin{tabular}{ccc}
\toprule
Network            & Detectors                & Acronym                 \\
\hline
\multirow{4}{*}{1} & \ac{aLIGO} H*    & \multirow{4}{*}{HLVK}   \\
                   & \ac{aLIGO} L* &                         \\
                   & \ac{AdVirgo}           &                         \\
                   & KAGRA                    &                         \\
                   \hline
\multirow{4}{*}{2} & LIGO A+ H          & \multirow{4}{*}{H+L+VK} \\
                   & LIGO A+ L       &                         \\
                   & \ac{AdVirgo}           &                         \\
                   & KAGRA                    &                         \\
\hline
\hline
\end{tabular}
\begin{tablenotes}
\setlength\labelsep{0pt}
\normalfont{
\item The networks of detectors used in this work.\\
* H refers to the detector in Hanford and L the detector in Livingston.}
\end{tablenotes}
\end{threeparttable}
\end{table}

\section{Result and discussion}\label{sec:result}
After the \ac{CNN} is trained, we can estimate its performance using the testing samples.
The results are presented in this section.
One of the most used and convenient ways to determine the classifying performance of a model is to plot the \ac{ROC} curve.
A \ac{ROC} shows the performance of a classifying model by showing the \ac{TAP} at a given \ac{FAP}. 
Since \ac{ROC} is usually plotted for model distinguishing two classes, 
for a multi-class classification problem, 
a \ac{ROC} for a class should be viewed as the class versus the others.
This means in this context, \ac{FAP} means the fraction of samples from other 
classes misidentified as a sample from the class the \ac{ROC} is associated with.
\ac{TAP} is identical to that of two-class classification problem and indicates the fraction of samples correctly identified.
For a given \ac{FAP}, a model with a higher \ac{TAP} is considered more capable than a model with a lower \ac{TAP}.
In Figure \ref{fig:ROClog}, we show the \acp{ROC} for both the mechanisms and \ac{GW} detector networks tested in this work. 
For simplicity, we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ROClog1}%
            \includegraphics[width=0.45\textwidth]{ROC_curves_neutrino.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ROClog2}
            \includegraphics[width=0.45\textwidth]{ROC_curves_mag.png}%
        }%
%
    \end{center}
    \caption{ROC curves showing the classification performance of the \ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three distances, $20$, $60$, and $100$kpc.
The left panel shows the results for the neutrino-driven mechanism, while the panel on the right shows those for the magnetorotational mechanism.
In both panels, the solid lines are for the network H+L+VK, while the dashed lines are for HLVK.
\label{fig:ROClog}}%
\end{figure*}
For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any given \acp{FAP} 
for magnetorotational than neutrino-driven signals.
That is not surprising as the amplitudes for magnetorotational signals are higher than that of neutrino-driven signals.

We can also show the classification efficiency of the \ac{CNN}  as a function of distance.
This is done by fixing the \ac{FAP} and plotting the \ac{TAP}. 
The results for three chosen \acp{FAP} are shown in Figure \ref{fig:eff}.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:eff1}%
            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}%
        }\quad
        \subfigure[]{%
            \label{fig:eff2}
            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the classification ability of the \ac{CNN} as a function of distance for both mechanisms and networks.
The left panel shows the results for the neutrino-driven mechanism, while the right shows those for the magnetorotational mechanism. 
In both panels, the solid lines show the results for the network H+L+VK, and the dashed lines for HLVK.
Three \acp{FAP} are chosen, i.e.: blue for \ac{FAP} $=0.1$, green for \ac{FAP} $=0.01$, red for \ac{FAP} $=0.001$.
\label{fig:eff}}%
\end{figure*}
In this figure, a similar trend is seen that magnetorotational signals are easier for the \ac{CNN} to identify than neutrino-driven signals at any distance. 
For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP} of $0.1$, 
the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the networks H+L+VK and HLVK respectively.
At more restrict \acp{FAP} such as $0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at the same distance for the two networks respectively.
For sources that are located at a slightly further distance of $60$ kpc, both networks achieve a \ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$.  
Such a range is well into the Large and Small Magellanic Clouds and covers the satellite galaxies in between\cite{karachentsev2004catalog, belokurov2007cats}.
For sources at $100$ kpc, the \acp{TAP} are close to or larger than $60\%$ for H+L+VK for all chosen \acp{FAP}, and is $73\%$ if the \ac{FAP} is $0.1$.  
Even for sources at $150$ and $200$ kpc, the \acp{TAP} are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with such a \ac{GW} network,
it is possible to detect magnetorotational \ac{CCSN} signals out to such a distance.
On the other hand, it is more difficult for the \ac{CNN} to detect and classify the neutrino-driven signals, due to their weaker amplitudes.
Nonetheless, for sources at $10$ kpc,
the \ac{CNN} achieves a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the \ac{FAP} is $0.1$.
This means that the \ac{GW} from a Galactic \ac{CCSN} signal is possible to be detected and classified with either of these networks.
\begin{figure*}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ROCfixed1}%
            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ROCfixed2}
            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data with a fixed decision threshold(0.5), and their corresponding \acp{FAP}.
    The left panel shows the results for the neutrino-driven mechanism, and the right shows that for the magnetorotational mechanism.
    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the dashed lines show those for HLVK.  
\label{fig:ROCfixed}}%
\end{figure*}

In practice, since the output of a \ac{CNN} is probabilities indicating how likely the input belongs to each of the classes, 
it may be desired to set a threshold on which the decision whether the input belong to a class is made.
For example, an input will be classified into a class if the corresponding probability is larger than the pre-selected threshold.
In such a scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the threshold.
We show such a result in Figure \ref{fig:ROCfixed}, where we employed a threshold of $0.5$. 
For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. 
If the distance is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.
For the largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are $43\%$ and $29\%$ respectively.
For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and $80$ kpc respectively.
%The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
Throughout the distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for both networks.
For neutrino-driven signals, it is shown that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it is $55\%$ at $10$ kpc for HLVK.
Both of the networks have \acp{FAP} close to or less than $0.2$.
It should be noted that the results presented here are averaged over all the data samples in the testing samples.
The performance on any individual waveform may vary depending on the morphology and the amplitudes of the waveform.

%Also shown in this figure is a curve showing the \ac{TAP} for all the classes, defined by,
%\begin{equation}\label{eq:TAPforall}
%\text{TAP}_{\text{all}} = \frac{\text{No. of correctly identified test input}}{\text{No. of test input}}.
%\end{equation}
%This curve provides an overall estimate of the fraction of input that the \ac{CNN} will correctly classify.
%Unsurprisingly, this curve resides between the lines for magnetorotational and neutrino-driven signals.

\section{Waveforms Excluded from Training}\label{sec:unseen}
The above section proves that using a \ac{CNN}, it is possible to detect and classify \ac{CCSN} waveforms 
if the waveforms have been used to train the \ac{CNN}. 
However, in reality, it is likely that the \acp{GW} from a \ac{CCSN} may only be partially similar to the simulated waveforms, 
while having some other features that are different or even unexpected. 
A \ac{CNN} that is only capable of recognising waveforms with which it is familiar may prove to be not entirely applicable.
Therefore, we apply our trained \ac{CNN} to waveforms from other studies that were not used during the training.
Similar to what was done in \cite{roma2019astrophysics}, 
we take the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from \cite{scheidegger2010influence} as the test waveforms for the magnetorotational mechanism.
The test waveforms for the neutrino-driven mechanisms are $\text{s}20$ from \cite{andresen2017gravitational} and $\text{SFHx}$ from \cite{kuroda2016new}.
The waveforms are shown in Figure \ref{fig:Extratestwaveform}.
The test waveforms in this section should not be confused with the testing samples in section \ref{sec:result}, 
which are randomly drawn from the same distribution as the training samples.
\begin{figure}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:ex_waveform_neu}%
            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}%
        }\quad
        \subfigure[]{%
            \label{fig:ex_waveform_mag}
            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}%
        }%
%
    \end{center}
    \caption{The waveforms excluded from the training session of the \ac{CNN} and used as an extra test for the performance of the \ac{CNN}.
    From the top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$(neutrino-driven mechanism), 
    $\text{R3E1AC}$ and $\text{R4E1FC\_L}$(magnetorotational mechanism), respectively. 
    The time in the x-axis is not related to core bounce.
\label{fig:Extratestwaveform}}%
\end{figure}
\begin{figure}
     \begin{center}
%
        \subfigure[]{%
            \label{fig:extra_waveform_test_neu}%
            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}%
        }\quad
        \subfigure[]{%
            \label{fig:extra_waveform_test_mag}
            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}%
        }%
%
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data.
    The upper panel shows the results for the the waveforms $\text{SFHx}$ and $\text{s}20$ (neutrino-driven mechanism), 
    and the lower panel shows that for the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ (the magnetorotational mechanism).
    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for H+L+VK, and the dashed lines show those for HLVK.  
    The waveforms have not been used for the training of the \ac{CNN}.
\label{fig:Extratest}}%
\end{figure}
The performance of the \ac{CNN} on the test waveforms are shown in Figure \ref{fig:Extratest}.
For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$ with H+L+VK and $59\%$ with HLVK respectively.
At $60$kpc, the \acp{TAP} drop slightly to $83\%$ and $52\%$ respectively.
This indicates that with the \ac{CNN}, it is possible to detect these waveforms from sources that are well into the Large and Small Magellanic Clouds.
For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$. 
The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably higher than that for the neutrino-driven mechanism in Figure \ref{fig:eff} for the same distance.
This is because as mentioned before, the detection and classification efficiency in Figure \ref{fig:eff} are the results averaged over the testing samples.
It is possible that individual waveforms may be easier for the \ac{CNN} to detect. The results indicate that the \ac{CNN} has generalised the features of the explosion mechanisms.
\section{Conclusion}\label{sec:conclusion}
We have demonstrated a \ac{CNN} can be applied for the purpose of distinguishing \ac{GW} detector time series 
among pure background noise and \ac{CCSN} explosion mechanisms. 
We trained the \ac{CNN} using $1.8\times10^{5}$ samples of simulated time series for each distance in a number of distances from $10$kpc to $200$kpc.
The data samples for each classes consisted of approximately $4\times10^5$ samples.

We have shown that with a network of HLVK, when the \ac{FAP} was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
for magnetorotational signals from sources at $60$ kpc. 
Using a network of H+L+VK, we showed that the \ac{TAP} could be even more promising at $91\%$. Both the Large and Small Magellanic Clouds are within this distance.
If the distance is extended to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ 
respectively are still achievable for H+L+VK, indicating the possibility of detections within such distances.

For the neutrino-driven mechanism, the weaker amplitudes of the waveforms result in lower \acp{TAP} at the same distances.
For sources at $10$kpc, the trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and $76\%$ for HLVK and H+L+VK respectively.
This indicates a Galactic \ac{CCSN} event is likely to be detectable.

We used four waveforms that were not used for the training of the \ac{CNN} to test the performance of the \ac{CNN} in a more realistic situation.
We found that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at $60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks respectively.
The results prove the possibility of using \ac{CNN} for the detection and classification of \ac{CCSN} \ac{GW} signals.
\\
\section*{ACKNOWLEDGEMENTS}
I.S.H. and C.M. are supported by
the Science and Technology Research Council (grant No.
ST/L000946/1)

\bibliography{main}

\end{document}

### 2019-12-09 main.tex
change the text in the test waveform section
Made a minor change to see if I can commit
Abouthalf wayt through the draft with my comments

@@
 %\renewcommand{\bibfont}{\normalfont\small}
+% test comment
 
@@
 
-\author{Authors$^{12}$}
+\author{Authors$^{12}$\cm{fix}}
 \affiliation{
@@
 \begin{abstract}
-We demonstrate the application of a convolutional neural network 
-to the gravitational wave signals from core collapse supernovae.
-Using simulated time series of gravitational wave detectors, 
-we show that a convolutional neural network can be used to detect and classify, based on the explosion mechanisms,  
-the gravitational wave signals buried in noise.
-For the waveforms used in the training of the convolutional neural network, 
-our results suggest that a network of advanced LIGO, advanced VIRGO and KAGRA, or a network of LIGO A+, advanced VIRGO and KAGRA
-is likely to detect a magnetorotational core collapse supernovae within the Large and Small Magellanic Clouds, or 
-a Galactic event if the explosion mechanism is the neutrino-driven mechanism.
-By testing the convolutional neural network with waveforms not used for training, 
-we show that the true alarm probabilities are $52\%$ and $83\%$ at $60$kpc for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$.
-For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the true alarm probabilities are $70\%$ and $93\%$ respectively. All at false alarm probability equal to $0.1$.
-\end{abstract}
+We demonstrate the application of a convolutional neural network to the
+gravitational wave signals from core collapse supernovae. Using simulated time
+series of gravitational wave detectors, we show that based on the explosion
+mechanisms, a convolutional neural network can be used to detect and classify
+the gravitational wave signals buried in noise. For the waveforms used in the
+training of the convolutional neural network, our results suggest that a
+network of advanced LIGO, advanced VIRGO and KAGRA, or a network of LIGO A+,
+advanced VIRGO and KAGRA is likely to detect a magnetorotational core collapse
+supernovae within the Large and Small Magellanic Clouds, or a Galactic event if
+the explosion mechanism is the neutrino-driven mechanism.  By testing the
+convolutional neural network with waveforms not used for training, we show that
+the true alarm probabilities are $52\%$ and $83\%$ at $60$kpc for waveforms
+$\text{R3E1AC}$ and $\text{R4E1FC\_L}$.  For waveforms $\text{s}20$ and
+$\text{SFHx}$ at $10$ kpc, the true alarm probabilities are $70\%$ and $93\%$
+respectively. All at false alarm probability equal to $0.1$\cm{why is this nopt
+also written as a percentage? Should it be 10\%?}.  \end{abstract}
+
 \pacs{}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Since 2015 when LIGO has made the first direct observation of \acp{GW} from the merger of a binary black hole\cite{abbott2016observation},
-there have been numerous observations of \acp{GW} from similar systems in the observation runs of LIGO 
-and VIRGO \cite{abbott2016gw151226, abbott2017gw170608, abbott2017gw170814}.
-These discoveries have been a crucial milestone in \ac{GW} astronomy and have opened up a new window on the sky.
-More recently, LIGO and VIRGO have observed the \acp{GW} from a binary neutron star merger\cite{abbott2017gw170817, abbott2017gravitational, abbott2017multi}.
-For this event, the \acp{GW} and the associated gamma-ray burst were observed simultaneously. 
-Other counterparts across the electromagnetic spectrum were also observed by later follow-up observations \cite{abbott2017multi}.
-In the near future, many more observations of \acp{GW} from similar compact binary coalescence systems can be expected
-as KAGRA starts joint observations with LIGO and VIRGO \cite{aso2013interferometer, somiya2012detector, abbott2018prospects}.
+%
+% general background on GWs
+%
+Since 2015 when LIGO made the first direct observation of \acp{GW} from the
+merger of a binary black hole~\cite{abbott2016observation}, there have been
+numerous observations of \acp{GW} from similar systems in the subsequent
+observation runs of LIGO and VIRGO~\cite{abbott2016gw151226,
+abbott2017gw170608, abbott2017gw170814}. These discoveries represent a crucial
+milestone in \ac{GW} astronomy and have opened up a new window on the universe.
+More recently, LIGO and VIRGO have observed the \acp{GW} from a binary neutron
+star merger~\cite{abbott2017gw170817, abbott2017gravitational, abbott2017multi}
+where the \acp{GW} and an associated gamma-ray burst were observed
+simultaneously. Other counterparts across the electromagnetic spectrum were
+also observed by later follow-up observations~\cite{abbott2017multi}. In the
+near future, many more observations of \acp{GW} from similar \ac{CBC} systems
+can be expected as KAGRA starts joint observations with LIGO and
+VIRGO~\cite{aso2013interferometer, somiya2012detector, abbott2018prospects}.
 
-In addition to compact binary coalescences, massive stars with $10-100 \text{M}_\odot $ at zeros-age main sequence ending their lives by becoming 
+%
+% intro to core-collapse supernovae
+%
+In addition to \acp{CBC}, massive stars with $10-100 \text{M}_\odot $ at
+zeros-age main sequence ending their lives by becoming 
 %with core of $10-100 \text{M}_\odot $ prior to collapse 
-\acp{CCSN} are also considered to be potential sources to the second generation detectors such as the \ac{aLIGO} \cite{aasi2015advanced}, 
-\ac{AdVirgo} \cite{acernese2014advanced} and KAGRA interferometers \cite{aso2013interferometer, gossan2016observing, abbott2016first}.
-It is currently not entirely clear to astronomers how such a massive star becomes supernova. 
-The basic theory of the explosion, confirmed by the neutrino events observed from SN1987A\cite{sato1987analysis}, goes as the following.
-A massive star at the final stage of its life will form core that is composed of iron nuclei after it has burned all its stellar fuel via nuclear reaction.
-The iron core is supported by the pressure of relativistic degenerate electrons.
-If the mass of the core exceeds the effective Chandrasekhar mass\cite{baron1990effect, bethe1990supernova}, core collapse will ensue and continue until it reaches nuclear density.
-The nuclear equation of state will then stiffens by the strong nuclear force above the nuclear density and stops 
-the core collapse.
-The inner core will bounce back and a shock wave will be sent through the infalling matter.
-By losing energy to the dissociation of the iron nuclei and to neutrino cooling, the shock wave will stall.
-For the star to become a supernova, the shock wave will need to be revived\cite{o2011black}.  
-The mechanism via which the shock wave is revived and causes the explosion has been the subject of intense study.
-However, it still remains an unsolved problem.
+\acp{CCSN} are also considered to be potential sources to the second generation
+detectors such as \ac{aLIGO}~\cite{aasi2015advanced},
+\ac{AdVirgo}~\cite{acernese2014advanced} and KAGRA
+interferometers~\cite{aso2013interferometer, gossan2016observing,
+abbott2016first}. It is currently not entirely clear to astronomers how such
+massive stars become supernovae. The basic theory of the explosion, confirmed
+by the neutrino events observed from SN1987A~\cite{sato1987analysis}, begins
+with a massive star at the final stage of its life forming a core that is
+composed of iron nuclei after it has burned all its stellar fuel via fusion
+reactions. The iron core is supported by the pressure of relativistic
+degenerate electrons and if the mass of the core exceeds the effective
+Chandrasekhar mass~\cite{baron1990effect, bethe1990supernova}, core collapse
+will ensue and continue until the core reaches nuclear density. The nuclear
+equation of state will then stiffens by the strong nuclear force above the
+nuclear density and stops the core collapse. The inner core will bounce back
+and a shock wave will be sent through the infalling matter.  By losing energy
+to the dissociation of the iron nuclei and to neutrino cooling, the shock wave
+will stall. For the star to become a supernova, the shock wave will need to be
+revived~\cite{o2011black}. However the mechanism via which this occurs and the
+supernova explosion is caused has been the subject of intense study and remains
+an unsolved problem.
 
-There exist two most popular theories, the neutrino-driven mechanism\cite{bethe1985revival, bethe1990supernova} and the magnetorotational mechanism\cite{janka2012explosion, kotake2012core, mezzacappa2014two}.
-For supernova progenitors with core rotation too slow to affect the dynamics\cite{takiwaki2016three, summa2018rotation}, the neutrino-driven mechanism is believed to be the active mechanism.
-The majority of the observed \acp{CCSN} can be explained by the neutrino mechanism\cite{bruenn2016development}.
-The neutrino mechanism\cite{bethe1985revival, janka2007theory} suggests that about $5-10\%$ of the outgoing neutrino luminosity is stored below the shock, 
-which causes turbulence to occur and thermal pressure to increase.
-The stalled shock can be revived by their combined effects\cite{couch2015role}. 
-Producing a \ac{CCSN} via the neutrino mechanism may also require convection and the standing accretion shock instability\cite{blondin2003stability}.
-On the other hand, the magnetorotational mechanism requires rapid core spin and strong magnetic field\cite{leblanc1970numerical, burrows2007simulations, takiwaki2009special, moiseenko2006magnetorotational,mosta2014magnetorotational}.
-Together, they may produce an outflow that may cause the most energetic \acp{CCSN} observed.
-The magnetorotational mechanism may be able to explain the extreme hypernovae and the observed long gamma-ray bursts\cite{woosley2006progenitor, yoon2005evolution, de2013rotation}.
+%
+% discussion of the CCSN mechanisms
+%
+There exist two most popular theories~\cm{theories for what?}, the
+neutrino-driven mechanism~\cite{bethe1985revival, bethe1990supernova} and the
+magnetorotational mechanism~\cite{janka2012explosion, kotake2012core,
+mezzacappa2014two}. For supernova progenitors with core rotation too slow to
+affect the dynamics~\cite{takiwaki2016three, summa2018rotation}, the
+neutrino-driven mechanism is believed to be the active mechanism. The majority
+of the observed \acp{CCSN} can be explained by the neutrino
+mechanism~\cite{bruenn2016development}~\cm{why?}. The neutrino
+mechanism~\cite{bethe1985revival, janka2007theory} suggests that approximately
+$5-10\%$ of the outgoing neutrino luminosity is stored below the shock, which
+causes turbulence to occur and thermal pressure to increase. The stalled shock
+can be revived by their combined effects~\cite{couch2015role}. Producing a
+\ac{CCSN} via the neutrino mechanism may also require convection and the
+standing accretion shock instability~\cite{blondin2003stability}. On the other
+hand, the magnetorotational mechanism requires rapid core spin and a strong
+magnetic field~\cite{leblanc1970numerical, burrows2007simulations,
+takiwaki2009special,
+moiseenko2006magnetorotational,mosta2014magnetorotational}. Together, they may
+produce an outflow that may cause the most energetic \acp{CCSN}
+observed~\cm{are you referring to a real observed CCSN, if so you should
+provide a reference.}. The magnetorotational mechanism may \cm{also?} be able
+to explain the extreme hypernovae and the observed long gamma-ray
+bursts\cite{woosley2006progenitor, yoon2005evolution, de2013rotation}.
 
-Correctly classifying the \ac{GW} from a \ac{CCSN} is important in understanding the explosion mechanism.
-%Electromagnetic observations provide only indirect informations about the mechanism of a \ac{CCSN} 
-%because photons interact strongly with matter and only information from the optically thin regions far from the central core could reach us. 
-%However, 
-As \acp{GW} are emitted in the central core of a \ac{CCSN}, 
-they are likely to carry direct information of the \ac{CCSN} and therefore provide a probe of the explosion mechanism that produces them.
-In \ac{GW} astronomy, when it comes to the search for signals from compact binary coalescences, the established routine is matched filtering.
-However, as the emission process of the \acp{GW} from \acp{CCSN} is affected by turbulence in the post-bounce and is stochastic in nature,  
-the signal evolution cannot be predicted robustly\cite{ott2009gravitational, kotake2013multiple, kotake2009stochastic}.
-This in turn prevents the match filtering routine to be applied to \acp{CCSN}.
-%Although, Neutrino radiation-hydrodynamics simulations have been an ongoing effort to decode and understand explosion mechanism of \acp{CCSN} and the \acp{GW} they produce\cite{ott2009gravitational}.
-Methods and algorithms have been developed for the detection and classification of signals from \acp{CCSN}. 
-For example, a method known as principle component analysis has been developed\cite{heng2009rotating, rover2009bayesian, powell2015classification, powell2017classification, suvorova2019reconstructing}.
-This method creates a set of component basis vectors from a set of \ac{CCSN} waveforms of a particular mechanism
-that represent the common features of the waveforms of that mechanism.
-There have been other approaches developed in the literature such as Bayesian inference\cite{rover2009bayesian}, Bayesian model selection\cite{logue2012inferring}
-, multivariate regression model\cite{engels2014multivariate}, maximum entropy\cite{summerscales2008maximum}, 
-maximum likelihood\cite{gursel1989near} and Tikhonov regularization scheme\cite{rakhmanov2006rank, hayama2007coherent}.
+%
+% GWS from CCSN and the existing literature
+%
+Correctly classifying the \ac{GW} signals from a \ac{CCSN} is important in
+understanding the explosion mechanism.
+%Electromagnetic observations provide only indirect informations about the
+%mechanism of a \ac{CCSN} because photons interact strongly with matter and
+%only information from the optically thin regions far from the central core
+%could reach us.  However, 
+As \acp{GW} are emitted\cm{generated?} in the central core of a \ac{CCSN}, they
+are likely to carry direct information of the \ac{CCSN} and therefore provide a
+probe of the explosion mechanism that produces them. In \ac{GW} astronomy, for
+\ac{CBC} events the established method for searching for signals is
+matched-filtering~\cm{give ref for pycbc and gstlal}. However, since the
+emission process of the \acp{GW} from \acp{CCSN} is affected by turbulence in
+the post-bounce and is \cm{expected to be?} stochastic in nature,  the signal
+evolution cannot be predicted robustly~\cite{ott2009gravitational,
+kotake2013multiple, kotake2009stochastic}.  This in turn prevents
+matched-filtering from being applied to \acp{CCSN}.
+%Although, Neutrino radiation-hydrodynamics simulations have been an ongoing
+%effort to decode and understand explosion mechanism of \acp{CCSN} and the
+%\acp{GW} they produce\cite{ott2009gravitational}.
+Methods and algorithms have been developed for the detection and classification
+of signals from \acp{CCSN}.  For example, a method known as principle component
+analysis has been developed~\cite{heng2009rotating, rover2009bayesian,
+powell2015classification, powell2017classification,
+suvorova2019reconstructing}. This method creates a set of component basis
+vectors from a \cm{larger?} set of \ac{CCSN} waveforms belonging to a
+particular mechanism where the basis vectors represent the common features of
+those waveforms.  There have been other approaches developed in the literature
+such as Bayesian inference~\cite{rover2009bayesian}, Bayesian model
+selection~\cite{logue2012inferring} , multivariate regression
+modelling~\cite{engels2014multivariate}, maximum
+entropy~\cite{summerscales2008maximum}, maximum
+likelihood~\cite{gursel1989near} and Tikhonov regularization
+scheme~\cite{rakhmanov2006rank, hayama2007coherent}.
 
-In recent years, the field of machine learning and its sub-field, deep learning, have been rapidly developing because of 
-its potentials in many fields \cite{krizhevsky2012imagenet, NIPS2014_5423, simonyan2014very, chen2014semantic, zeiler2014visualizing, szegedy2015going}.
-For example, deep learning have been successfully applied to fields including medical diagnosis\cite{kononenko2001machine}, object detection\cite{redmon2016you}, image recognition/processing/generation\cite{he2016deep, krizhevsky2012imagenet, zhang2016colorful, karpathy2015deep},    and  language processing\cite{lample2016neural}.
-In \ac{GW} astronomy, deep learning has mostly been applied to both the identifications of glitch\cite{mukund2017transient, zevin2017gravity, george2017deep, gabbard2018matching} and signals\cite{george2018deep, astone2018new}.
-\ac{CNN} is a deep learning algorithm that has the advantage of capturing spatial and temporal features of the input data.
-Another advantage of the use of a \ac{CNN} in the detection of a signal is that a \ac{CNN} is relatively computationally cheap compared to other more traditional methods.
-This is because the heavy computational work is usually done during the training stage of a \ac{CNN} prior to its actual application\cite{goodfellow2016deep}.
+%
+% introduce machine learning
+% 
+In recent years, the field of machine learning and its sub-field, deep
+learning, have been rapidly developing and have shown great potential in many
+scientific fields~\cite{krizhevsky2012imagenet, NIPS2014_5423,
+simonyan2014very, chen2014semantic, zeiler2014visualizing, szegedy2015going}.
+For example, deep learning has been successfully applied to fields including
+medical diagnosis~\cite{kononenko2001machine}, object
+detection~\cite{redmon2016you}, image
+recognition/processing/generation~\cite{he2016deep, krizhevsky2012imagenet,
+zhang2016colorful, karpathy2015deep}, and  language
+processing~\cite{lample2016neural}. In \ac{GW} astronomy, deep learning has
+mostly been applied to the identifications of detector noise artefacts
+(glitches)~\cite{mukund2017transient, zevin2017gravity, george2017deep} and the
+detection of astrophysical signals~\cite{george2018deep, gabbard2018matching,
+astone2018new} and their parameter estimation~\cm{add ref to Hunters latest
+paper}. A \ac{CNN} is a deep learning algorithm that has the advantage of
+capturing spatial and temporal features of the input data~\cm{this doesn't
+really mean anything. Spatial refers to features in certain locations in images
+and temporal refers to locations in a time series of in the time axis of a
+spectrogram image}. Another advantage of the use of a \ac{CNN} in the detection
+of a \ac{GW} signal is that a \ac{CNN} is relatively computationally cheap
+compared to other more traditional methods. This is because the heavy
+computational work is usually done during the training stage of a \ac{CNN}
+prior to its actual application~\cite{goodfellow2016deep}.
 
-In this work, we demonstrate a \ac{CNN} can be applied to the detection of the \acp{GW} from \acp{CCSN}
-and the classification of their explosion mechanisms.
-To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a number of studies and simlate sources 
-at a range of distances from $10$ to $200$ kpc for two networks of four detectors.
-The first network consists of \ac{aLIGO}, \ac{AdVirgo} and KAGRA.
-For the second network, we still include the detectors of \ac{AdVirgo} and KAGRA,  
-but replace the two detectors of \ac{aLIGO} with 
-a modest set of planned upgrade version of them - LIGO A+ in Hanford and Livingston\cite{miller2015prospects, LIGOW}.
-We will then apply the \ac{CNN} to waveforms excluded from the training session to show that the \ac{CNN} 
-is not only able to identify the waveforms it familiarised itself with during training, but also new waveforms.
+%
+% the main point of the paper
+%
+In this work, we demonstrate that a \ac{CNN} can be applied to the detection of
+\acp{GW} from \acp{CCSN} and to the classification of their explosion
+mechanisms.  To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a
+number of studies and simlate sources at a range of distances from $10$ to
+$200$ kpc for two networks of four \ac{GW} detectors. The first network
+consists of \ac{aLIGO}, \ac{AdVirgo} and KAGRA. For the second network, we
+still include the detectors of \ac{AdVirgo} and KAGRA, but replace the two
+detectors of \ac{aLIGO} with a modest set of planned upgrade version of them -
+LIGO A+ in Hanford and Livingston~\cite{miller2015prospects, LIGOW}. We then
+apply the \ac{CNN} to waveforms excluded from the training set to show that the
+\ac{CNN} is not only able to identify the waveforms it familiarised itself with
+during training, but also new waveforms~\cm{this is a strange statement. The
+ability of the CNN to work on the training data is completely outweighed by its
+perfromance on the independent testing set. The testing set perfroamnce is all
+that you should mention here.}.
 
-The remaining of this paper is constructed as follows. 
-In section \ref{sec:CNN}, we will present a brief explanation of the concept of \ac{CNN} as well as the \ac{CNN} we used for this work.
-In section \ref{sec:spwf}, we introduce the waveforms we use for the training of the \ac{CNN} in this work. We will also discuss the procedure with which we generated the data for the \ac{CNN}.
-The results will be shown in sections \ref{sec:result} and \ref{sec:unseen}, followed by a conclusion in section \ref{sec:conclusion}.
+%
+% paper structure
+%
+The remaining of this paper is structured as follows. In Section~\ref{sec:CNN},
+we present a brief explanation of the concept of a \ac{CNN} as well as the
+\ac{CNN} architecture  used for this study. In Section~\ref{sec:spwf}, we
+introduce the waveforms we use for the training of the \ac{CNN} and  also
+discuss the procedure with which we generated the input data for the \ac{CNN}.
+The results are shown in Sections~\ref{sec:result} and~\ref{sec:unseen},
+followed by our conclusions in Section~\ref{sec:conclusion}.
 %\section{Supernova waveform}\label{sec:spwf}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Convolutional Neural network}\label{sec:CNN}
-A \ac{CNN} is a computational processing system that is composed of interconnected layers of computational nodes\cite{o2015introduction}.
-The nodes are known as neurons and are associated with an activation function.
-The activation function can perform an elementwise nonlinear operation to the input of the layer. 
-In a \ac{CNN}, there are three types of layers: convolutional layer, max-pooling layer, and fully connected layer\cite{o2015introduction}.
-Convolutional layer performs the mathematical operation of convolution between the weights of the layer's neurons and the input to that layer.
-Max-pooling layer is just a down-sampling layer that down samples the input along its dimensionality.
-It can reduce the computational cost by decreasing the number of parameters of the \ac{CNN}.
-Fully connected layer is a layer that connects every neuron in its layer to every neuron of its immediate previous and next layer.
-In the case of detection and classification, fully connected layers are used to compute class scores.
 
-When multiple layers of these three types are stacked and connected one after the other, 
-a \ac{CNN} has been formed, where the output of each layer is the input of the next layer.
-How these layers are connected in a \ac{CNN} is known as the architecture of the \ac{CNN}.
-It describes the structure of a \ac{CNN} and the number of neurons in each layer. % (width and depth) 
-In general, the first layer in a \ac{CNN}, also known as the input layer, is often a convolutional layer, 
-while the last layer or the output layer is often a fully connected layer with an associated loss function. 
-The architecture of the rest of the \ac{CNN} should depend on the specific task that the \ac{CNN} is trained to solve. 
-An over-complicated model with too many trainable parameters 
-is easier to result in overfit and harder to train, 
-while a too-simple \ac{CNN} will have a hard time capturing the feature inherent to the input.
-In addition, the number of layers and neurons of each layer in a \ac{CNN} are known as hyperparameters.
-Other hyperparameters include the parameters of max-pooling layers, type of activation functions, 
-learning rate of the \ac{CNN}, and the application of specific deep learning techniques if there is any.
-The optimal combination of hyperparameters and the architecture is sought by trail and error, and fine tunning.
+%
+% describe the components of a CNN
+%
+A \ac{CNN} is a computational processing system that is composed of
+interconnected layers of computational nodes~\cite{o2015introduction}. The
+nodes are known as neurons and the outputs of which are processed with an
+activation function. The activation function performs an elementwise nonlinear
+operation to the output of the layer. In a standard \ac{CNN}, there are
+commonly three types of layers: convolutional layers, max-pooling layers, and
+fully connected layers~\cite{o2015introduction}. Convolutional layers perform
+the mathematical operation of convolution between the weights of the layer's
+neurons and the input to that layer. Max-pooling layers perform a down-sampling
+process that reduces the size of the data by selecting the maximum of data
+samples within fixed size bins. It can reduce the computational cost by
+decreasing the number of trainable parameters (weights and biases) of the
+\ac{CNN}.  Fully connected layers are layers that connect every neuron in its
+layer to every neuron of its immediate previous and next layer. In the case of
+detection and classification, the output layer is also a fully connected layer
+with a softmax activation function with output used to represent the class
+scores or probabilities.~\cm{even after editing, this isn't the clearest
+description of a CNN. You are lacking an initial statement that says what a CNN
+does - it takes in data and is able to classify it as one of the N types it has
+learnt through training.}
 
-During the training stage, the weights of the neurons in a \ac{CNN} are updated using an algorithm called back propagation\cite{lecun1988theoretical}.
-The output of the \ac{CNN} is used as an input to the loss function associated with the output layer. 
-The back propagation algorithm will then compute the gradient of the loss function 
-which is used to adjust the values of the weights of the neurons in each layer and minimise the loss function.
-When the loss function is minimised, the \ac{CNN} will classify its input into the correct category with the highest confidence. 
-The process of achieving the minimisation of the loss function during the training stage is referred to as learning.
+%
+% decribe the structure of the CNN
+%
+When multiple layers of these three types are stacked and connected one after
+the other, a \ac{CNN} has been formed, where the output of each layer is the
+input of the next layer. How these layers are connected in a \ac{CNN}, the
+numbers of layers, their type, the number of neurons, the convolutional filter
+size, max-pooling size, and the activation functions used, describes the
+architecture of the \ac{CNN} (also known as hyper-parameters). The first layer
+in a \ac{CNN}, also known as the input layer, is often a convolutional layer,
+while the last layer or the output layer is often a fully connected layer with
+an associated loss function~\cm{the loss isn't really associated with the
+output layer. It is associated withe whole network.}. The architecture of the
+remainder of the \ac{CNN} should depend on the specific task that it is being
+trained to solve. An over-complicated model with too many trainable parameters
+makes it easier to result in over-fitting (a procedure where the network
+essentially memorises the training data but is unable to generalise to new
+data). Alternatively, an overly simple architecture will struggle to capture
+the features inherent to the input and not perform well in classification.
+Automated schemes do exist for finding the optimal combination of
+hyperparameters but in general (and in our case) the final architecture is
+often obtained through rough trial and error, followed by fine tunning.
 
-In this work, we employ a \ac{CNN} of $8$ convolutional layers, $3$ max-pooling layers, and $3$ fully connected layers.
-The exact architecture of the \ac{CNN} is shown in Table \ref{table:architecture} and illustrated in Figure \ref{fig:CNN}.
+%
+% describe training
+%
+During the training stage, the weights of the neurons in a \ac{CNN} are updated
+using an algorithm called back-propagation~\cite{lecun1988theoretical}. The
+output of the \ac{CNN} is used as an input to the loss-function~\cm{you need to
+define what the loss function is supposed to do and how by minimising it you
+make the network produce the right result. It isn't clear here.} and
+back-propagation then computes the gradient of the loss-function with respect
+to the traininable weights and biases within the network. A gradient descent
+algorithm is then used to adjust the values of the weights and biases of the
+neurons in each layer in order to iteratively minimise the loss-function.  When
+the loss function is minimised and training is therefore complete, the \ac{CNN}
+will be able to take in input in the form of new data and its output will best
+represent the probability of that data belonging to each of the trained
+classes. A well performing network will give high output probabilities to the
+correct class in most cases. The process of achieving the minimisation of the
+loss function during the training stage is the process whereby the machine is
+"learning"..
+
+%
+% describe the specific architecture used here
+% 
+In this work, we employ a \ac{CNN} of $8$ convolutional layers, $3$ max-pooling
+layers, and $3$ fully connected layers. The exact architecture of the \ac{CNN}
+is shown in Table~\ref{table:architecture} and illustrated in
+Fig.~\ref{fig:CNN}.
+
 \begin{table}[]
@@
 \normalfont{
-\item The architecture of the \ac{CNN} used in this work for the purpose of distinguishing supernova signal mechanisms and background noise.
-In the table, Conv means convolutional neural layer, Max-pool max-pooling layer, and Fully-con fully-connected layers.
-Neuron and Act. Fun mean the number of neurons and the activation function for the layer respectively. 
-The numbers in the bracket for the fully-connected layers are the number used for drop-out.}
+\item The architecture of the \ac{CNN} used in this work for the purpose of
+distinguishing supernova signals in backgound \ac{GW} detector noise vs detectr
+noise alone. In the table, Conv means convolutional layer, Max-pool means
+max-pooling layer, and Fully-con means fully-connected layer. Neuron and Act.
+Fun indicate the number of neurons and the activation function used for the
+layer respectively. The numbers in the bracket for the fully-connected layers
+are the number used for drop-out~\cm{You haven't discussed drop-out yet. You
+should mention it earlier when you introduce CNNs}.}
 \end{tablenotes}
@@
 \end{table}
-\begin{figure}
-\includegraphics[width=0.48\textwidth]{CNN2.png}
-\caption{An illustration of the architecture of the \ac{CNN} used in this paper for the detection and classification of \ac{CCSN} signals in noisy data.
-The \ac{CNN} consists of $8$ convolutional layers, $3$ max-pooling layers and $3$ fully connected layer including the output layer.
-The input layer takes the simulated time series of the detectors as input, feeding through the \ac{CNN}. The \ac{CNN} will output three probabilities at the last layer.
-The numbers above or below each layer indicate the kernal size of the layer. For example, the first convolutional layer has $11$ filters, 
-each of which is $1$ by $32$ in size. 
-The elements in the figure are not to scale.
+
+\begin{figure*}
+\includegraphics[width=0.96\textwidth]{CNN2.png}
+\caption{An illustration of the architecture of the \ac{CNN} used in this paper
+for the detection and classification of \ac{CCSN} \ac{GW} signals in noisy data. The
+\ac{CNN} consists of $8$ convolutional layers, $3$ max-pooling layers and $3$
+fully connected layer including the output layer.  The input layer takes the
+simulated time series of the detectors as input, feeding through the \ac{CNN}.
+The \ac{CNN} will output three probabilities at the last layer.  The numbers
+above or below each layer indicate the kernal size of the layer. For example,
+the first convolutional layer has $11$ filters, each of which is $1$ by $32$ in
+size~\cm{this is the only place that you describe the timeseries being the
+input and what the network does in a single sentence. This text should appear
+in the main bodty of the paper}.~\cm{Also, because I'm very picky about plots
+and images - even though I made the image full page width, the timeseries plots
+are TOO small and the axes are insanely small to read. You seem to have
+strecthed curly bracket symbols to the point that they look super-wierd.}
 \label{fig:CNN}}
-\end{figure}
-Since the problem we are trying to solve is a problem of multi-class classification, 
-the loss function employed for this work is categorical cross entropy\cite{abadi2016tensorflow}, given by
+\end{figure*}
+
+%
+% define the loss function 
+%
+The problem we are trying to solve is a problem of multi-class
+classification, and hence the loss function employed for this work is the
+categorical cross-entropy~\cite{abadi2016tensorflow}, defined as
+%
 \begin{equation}\label{eq:cce}
- L(y,\hat{y}) = -\sum^M_{j=1}\sum^C_{i=1}(y_{ij}log(\hat{y}_{ij})),
+ L(y,\hat{y}) = -\sum^M_{j=1}\sum^C_{i=1}y_{ij}\log(\hat{y}_{ij}),
 \end{equation}
-where $C$ is the number of the classes and $M$ is the number of the training samples.
-For the $j^{\text{th}}$ sample and the $i^{th}$ class, $y_{ij}$ is the correponding class value. It is equal to $1$ for the true class and $0$ otherwise.
-Similarly, $\hat{y}_{ij}$ is the predicted probability from the \ac{CNN} for the $i^{th}$ class and the $j^{\text{th}}$ sample.
+%
+where $C$ is the number of the classes and $M$ is the number of the training
+samples~\cm{the loss is computed over batches so here $M$ should be the batch
+size. However, you haven't introduced batches yet, which you need to do when
+you're discussing training}. For the $j^{\text{th}}$ sample and the $i^{th}$
+class, $y_{ij}$ is the correponding class value. It is equal to $1$ for the
+true class and $0$ otherwise.  Similarly, $\hat{y}_{ij}$ is the predicted
+probability from the \ac{CNN} for the $i^{th}$ class and the $j^{\text{th}}$
+sample.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data}\label{sec:spwf}
-We establish a \ac{CNN} for the purpose of distinguishing detector time series among three classes, 
-i.e., magnetorotational signals + background noise, neutrino-driven signals + background noise, and pure background noise. 
-For this purpose, it is necessary to prepare training, validation and testing data of these three classes.
-The training data is used for tuning the weights of the neurons in the layers in the \ac{CNN}, 
-while validating data is to verify that the \ac{CNN} is learning the features inherent to the data and testing data is to test the performance of the trained \ac{CNN}.
+%
+% describe the classes and training, validation, and testing
+%
+We establish a \ac{CNN} for the purpose of distinguishing detector time series
+among three classes, i.e., magnetorotational signals $+$ background noise,
+neutrino-driven signals $+$ background noise, and pure background noise. For
+this purpose, it is necessary to prepare training, validation and testing data
+of these three classes. The training data is used for tuning the weights of
+the neurons in the layers in the \ac{CNN}, while validating data is to verify
+that the \ac{CNN} is learning the features inherent to the data and testing
+data is to test the performance of the trained \ac{CNN}.
 
-In general, the input of a \ac{CNN} is numerical data.
-In our case, a data sample is a set of simulated time series stacked together as a $k \times p$ matrix 
-where $k$ is the number of detectors and $p$ the number of elements in the time series.
-To this end, we use simulated waveforms in the literature.
-The magnetorotational \ac{CCSN} signals are taken from\cite{abdikamalov2014measuring, dimmelmeier2008gravitational, richers2017equation}. 
-The simulations in \cite{abdikamalov2014measuring} were focused on the dependence of the waveforms on the angular momentum distrubion of the progenitors and generated 92 waveforms.
-In \cite{dimmelmeier2008gravitational}, 136 waveforms were generated to investigate a variety of rotation rates and masses of the progenitors.
-The simulations in \cite{richers2017equation} covered a parameter space of $18$ different equations of state and $98$ rotation profiles for a progenitor of $12M_{\odot}$ generating in total $1824$ waveforms.
-All the simulations from the studies were 2D.
-For the neutrino-driven mechanism, we employ the waveforms from\cite{10.1093mnrasstz990, kuroda2017correlated, muller2012parametrized, powell2019gravitational, 
-radice2019characterizing, yakunin2015gravitational, yakunin2017gravitational, ott2009gravitational, murphy2009model, ott2013general}.
-The simulations in \cite{10.1093mnrasstz990, kuroda2017correlated, muller2012parametrized, powell2019gravitational, 
-radice2019characterizing, yakunin2017gravitational} were 3D while the simulations in \cite{yakunin2015gravitational, ott2009gravitational, murphy2009model, ott2013general} were 2D.
-These simulations cover a wide range of progenitor masses from $9\text{M}_\odot$ to $60\text{M}_\odot$.
-The progenitor masses of the simulations are shown in Table \ref{table:waveforms}.
+%
+% describe the magneto waveforms
+%
+In our case, we define an input data sample as a set of simulated time series
+stacked together as a $k \times p$ matrix where $k$ is the number of detectors
+and $p$ the number of elements in the time series. To this end, we use
+simulated waveforms taken from the literature. The magnetorotational \ac{CCSN}
+signals are taken from~\cite{abdikamalov2014measuring,
+dimmelmeier2008gravitational, richers2017equation}. The simulations
+in~\cite{abdikamalov2014measuring} were focused on the dependence of the
+waveforms on the angular momentum distribution of the progenitors and proivide
+us with 92 waveforms. In~\cite{dimmelmeier2008gravitational}, 136 waveforms are
+available from investigations into a variety of rotation rates and masses of
+the progenitors. The simulations in~\cite{richers2017equation} covered a
+parameter space of $18$ different equations of state and $98$ rotation profiles
+for a progenitor of $12M_{\odot}$ providing a total of $1824$ waveforms. All
+the simulations from the studies were based on 2D simulations of supernovae.
+
+%
+% describe the neutrino waveforms
+%
+For the neutrino-driven mechanism, we employ the waveforms
+from~\cite{10.1093mnrasstz990, kuroda2017correlated, muller2012parametrized,
+powell2019gravitational, radice2019characterizing, yakunin2015gravitational,
+yakunin2017gravitational, ott2009gravitational, murphy2009model,
+ott2013general}. The simulations in~\cite{10.1093mnrasstz990,
+kuroda2017correlated, muller2012parametrized, powell2019gravitational,
+radice2019characterizing, yakunin2017gravitational} were from 3D modelling of
+the supernovae while the simulations in~\cite{yakunin2015gravitational,
+ott2009gravitational, murphy2009model, ott2013general} were 2D. These
+simulations cover a wide range of progenitor masses from $9\text{M}_\odot$ to
+$60\text{M}_\odot$ and the specific progenitor masses of the simulations are
+shown in Table~\ref{table:waveforms}. Examples of the simulated waveforms for
+both mechanisms are shown in Figs.~\ref{fig:magwaveforms} and
+\ref{fig:neuwaveforms}.
+
 \begin{table}[]
@@
 \normalfont{
-\item The mass range of the progenitors of the simulated waveforms used in this work.
-The first column refers to the studies. Mechanism indicates the explosion mechanism for 
-the waveforms, with M for the magnetorotational mechanism and N for the neutrino-driven mechanism.
-Mass refers the mass, in solar mass, of the progenitors in the simulations. No. means the number of waveforms available from the study.}
+\item The mass ranges and mechanisms of the progenitors of the simulated
+waveforms used in this work.  The first column refers to the studies. Mechanism
+indicates the explosion mechanism for the waveforms, with M for the
+magnetorotational mechanism and N for the neutrino-driven mechanism.  Mass
+refers the mass, in units of solar mass, of the progenitors in the simulations.
+No. means the number of waveforms available from the study.} 
 \end{tablenotes}
@@
 \end{table}
+
 %Anderson 2016 also does 3d, 20 mass, 11 mass
@@
 %and $12, 15, 20$ and $40M_{\odot}$\cite{murphy2009model}, and 3D simulations for a progenitor of $27M_{\odot}$\cite{ott2013general}.$26$
-Examples of the simulated waveforms for both mechanisms are shown in Figures \ref{fig:magwaveforms} and \ref{fig:neuwaveforms}.
+
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{mag_waveforms.png}
-\caption{Examples of simulated waveforms used in the work for which the explosion mechanism is magnetorotational mechanism.
-The top panel shows a waveform from\cite{abdikamalov2014measuring}. 
-The progenitor is $12\text{M}_\odot$ with differential rotation parameter $A=300\text{km}$. 
-The initial angular velocity at the core $\Omega_c$ is $8.5\text{rads/s}$.
-The middle panel shows that from \cite{dimmelmeier2008gravitational}.
-The simulation is done assuming a progenitor of $15\text{M}_\odot$ with $A=50$km and $\Omega_c = 1.91\text{rads/s}$.
-The panel in the bottom shows a waveform from \cite{richers2017equation}.
-For this simulation, the progenitor is $12\text{M}_\odot$,  $A$ and $\Omega_c$ are $10000$km and $0.5\text{rad/s}$ respectively.
-In all panels, only the $h+$ polarisations are shown because the simulations are axis-symmetric or 2D, and described by only one polarisation. 
-The sources are assumed to be at $10$ kpc from earth. The time is not related to the time at core bounce.
+\caption{Examples of simulated waveforms used in the work for which the
+explosion mechanism is magnetorotational mechanism.  The top panel shows a
+waveform from~\cite{abdikamalov2014measuring}. The progenitor is
+$12\text{M}_\odot$ with differential rotation parameter $A=300\text{km}$. The
+initial angular velocity at the core $\Omega_c$ is $8.5\text{rads/s}$. The
+middle panel shows a waveform from~\cite{dimmelmeier2008gravitational}. The
+simulation corresponds to a progenitor of $15\text{M}_\odot$ with $A=50$km and
+$\Omega_c = 1.91\text{rads/s}$.  The lower panel shows a waveform
+from~\cite{richers2017equation} where the progenitor is $12\text{M}_\odot$, $A$
+and $\Omega_c$ are $10000$km and $0.5\text{rad/s}$ respectively. In all panels,
+only the $h_{+}$ polarisations are shown because the simulations are
+axis-symmetric or 2D, and therefore described by only one polarisation.  The
+sources are assumed to be at a distance of $10$ kpc. The time is not related to
+the time at core bounce~\cm{then what is the time in reference to? Also, these
+plots are too small and squashed. The text is certainly too small to be
+readable and they should all have equal y and x-axis scales for comparison.}.
 \label{fig:magwaveforms}} 
 \end{figure}
+
 \begin{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Result and discussion}\label{sec:result}
@@
 \end{figure}
+Using the procedure described in section \ref{sec:spwf}, we generate $1200$ injections for each distance and each class has around 400 injections.
 The performance of the \ac{CNN} on the test waveforms are shown in Figure \ref{fig:Extratest}.
@@
 the Science and Technology Research Council (grant No.
-ST/L000946/1)
-
+ST/L000946/1) and the European Cooperation in
+Science and Technology (COST) action CA17137. 
 \bibliography{main}

### 2019-12-11 main.tex
Added my comments up to the results and discussion section.

@@
 
+%
+% table of CNN hyper-parameters
+%
 \begin{table}[]
@@
 
+%
+% table of simulation paramaters
+%
 \begin{table}[]
@@
 
+%
+% plot of example magneto waveforms
+%
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{mag_waveforms.png}
-\caption{Examples of simulated waveforms used in the work for which the
-explosion mechanism is magnetorotational mechanism.  The top panel shows a
-waveform from~\cite{abdikamalov2014measuring}. The progenitor is
-$12\text{M}_\odot$ with differential rotation parameter $A=300\text{km}$. The
-initial angular velocity at the core $\Omega_c$ is $8.5\text{rads/s}$. The
-middle panel shows a waveform from~\cite{dimmelmeier2008gravitational}. The
-simulation corresponds to a progenitor of $15\text{M}_\odot$ with $A=50$km and
-$\Omega_c = 1.91\text{rads/s}$.  The lower panel shows a waveform
+\caption{Examples of simulated waveforms for which the explosion is modeled by
+the magnetorotational mechanism. The top panel shows a waveform
+from~\cite{abdikamalov2014measuring}. The progenitor is $12\text{M}_\odot$ with
+differential rotation parameter $A=300\text{km}$. The initial angular velocity
+at the core $\Omega_c$ is $8.5\text{rads/s}$. The middle panel shows a waveform
+from~\cite{dimmelmeier2008gravitational}. The simulation corresponds to a
+progenitor of $15\text{M}_\odot$ with $A=50$km and $\Omega_c =
+1.91\text{rads/s}$.  The lower panel shows a waveform
 from~\cite{richers2017equation} where the progenitor is $12\text{M}_\odot$, $A$
@@
 
+%
+% plot of example neutrino waveforms
+%
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{neu_waveforms.png}
-\caption{Examples of simulated waveforms used in the work for which the explosion mechanism is neutrino-driven mechanism.
-From the top to the bottom, the panels show waveforms from\cite{10.1093mnrasstz990, murphy2009model, radice2019characterizing}, with progenitors of masses equal to $15\text{M}_\odot$,
-$15\text{M}_\odot$ and $60\text{M}_\odot$ respectively. 
-The sources are assumed to be at $10$ kpc from earth. The time is not related to the time at core bounce.
+\caption{Examples of simulated waveforms for which the explosion mechanism is
+modeled by the neutrino-driven mechanism. From the top to the bottom, the
+panels show waveforms from~\cite{10.1093mnrasstz990, murphy2009model,
+radice2019characterizing}, with progenitors of masses equal to
+$15\text{M}_\odot$, $15\text{M}_\odot$ and $60\text{M}_\odot$ respectively.
+The sources are assumed to be at $10$ kpc from earth. The time is not related
+to the time at core bounce.~\cm{then what is the time in reference to? Also, these
+plots are too small and squashed. The text is certainly too small to be
+readable and they should all have equal y and x-axis scales for comparison. Why
+does the x-axis extend to longer than the longest waveform?}
 \label{fig:neuwaveforms}}
 \end{figure}
-Introducing waveforms from a variety of studies essentially introduces a distribution of the waveforms that covers a larger parameter space, 
-making the data samples harder for the \ac{CNN} to learn.
-As a result, the performance of the trained \ac{CNN} on the testing samples 
-may appear to be worse than that if the data were generated using only a subset of the waveforms.
-However, a larger parameter space provides the advantage of forcing the \ac{CNN} to 
-learn the features common among the waveforms, rather than a subset of the waveforms.
-The trained network can thus perform better when facing waveforms with unexpected features, which is more likely in reality.
-
-Since the waveforms are generated at various distances, sampling rates and durations, 
-it is necessary to normalise the waveforms before they can be used for the generation of the time series.
-To do this, we first scale the amplitudes of the waveforms by moving the sources to $10$ kpc from earth.
-We then ensure that the sampling rate are identical for all the waveforms by down sampling 
-them to a pre-selected sampling rate (e.g., $4096$Hz).
-The longest duration $\tau$ among the waveforms is then identified and each of the remaining waveforms is padded with zeros
-to this duration.
-To introduce as less artefact as possible, a high pass filter with a low cut-off frequency equal to $11$Hz 
+
+%
+% discuss the reason of using multiple waveform families
+%
+Introducing waveforms from a variety of studies introduces a distribution of
+the waveforms that covers a larger parameter space, making the data samples
+harder for the \ac{CNN} to learn. As a result, the performance of the trained
+\ac{CNN} on the testing samples may appear to be worse than that if the data
+were generated using only a subset of the waveforms. However, a larger
+parameter space provides the advantage of forcing the \ac{CNN} to learn the
+features common among the waveforms rather than simply a subset of the
+waveforms.  The trained network can thus perform better when presented with
+waveforms with unexpected features, which is more likely in reality.
+
+%
+% describe data pre-processing
+%
+Since the waveforms are generated at various distances, sampling rates and
+durations, it is necessary to normalise the waveforms before they can be used
+for the generation of the time-series. To do this, we first scale the
+amplitudes of the waveforms by moving the sources to $10$ kpc from earth. We
+then ensure that the sampling rate are identical for all the waveforms by down
+sampling them to a pre-selected sampling rate (e.g., $4096$Hz~\cm{e.g. means
+for example, is this an example rate or is it THE rate?}). The longest duration
+$\tau$ among the waveforms is then identified and each of the remaining
+waveforms is padded with zeros to this duration. To introduce as few artefacts
+as possible, a high pass filter with a low cut-off frequency equal to $11$Hz
 and a tukey window ($\alpha = 0.08$) are applied prior to the zero padding.
-To balance the difference in the number of waveforms 
-between the two mechanisms in the final data set, $36$ copies of each neutrino-driven waveform are duplicated.
-After this procedure, the simulated 
-waveforms are then $\bold{S}(t) = \{\bold{s}_{1}(t), \bold{s}_{2}(t), ..., \bold{s}_{m}(t)\}$, where $m$ is the number of the waveforms and 
+
+%
+% data augmentation
+%
+To balance the difference in the number of waveforms between the two mechanisms
+in the final data set~\cm{what is the final dataset? Is it the training,
+validation or test, or all of them? Please be clearer}, $36$ copies of each neutrino-driven waveform are
+made~\cm{please explain this in more detail, why is this done and how is this
+done. Surely they are not simply exact copies? Does each copy get a different
+noise realisation or different arrival time? This leaves many questions. Do
+you simply make the number of magneto and neutrino wavelforms equal? What about
+the sub categories? Do you still have 8 times as many Ott2 waveforms as
+Yakunin2? If so, why?}. After this procedure, the
+simulated waveforms are then $\bold{S}(t) = \{\bold{s}_{1}(t), \bold{s}_{2}(t),
+..., \bold{s}_{m}(t)\}$, where $m$ is the number of the waveforms and
 $\bold{s}_{q}$ is the $q^{\text{th}}$ waveform, defined by, 
+%
 \begin{equation}\label{eq:ht}
- \bold{s}_q(t) = \left(\begin{array}{c}
-                        h_q^+(t) \\
-                        h_q^\times(t)
+\bold{s}_q(t) = \left(\begin{array}{c} h_q^+(t) \\ h_q^\times(t)
 \end{array}\right), 
 \end{equation} 
-where $h_q^+(t)$ and $h_q^\times(t)$ are the two polarisations of the waveform and $t$ the time. 
-As mentioned, some of the waveforms used in the work are generated with the simulations being axis-symmetric, the \acp{GW} are entirely described by one polarisation $h_q^+(t)$. 
-The corresponding $h_q^\times(t)$ for these waveforms are a zero vector. 
-In this work, we perform simulations for distances equal to $10$, $20$, $30$, $40$, $50$, $60$, $80$, $100$, $150$ and $200$ kpc.
-If for a training session, the distance $d_\text{L}$ interested is not $10$ kpc, the following relationship is employed to scale the amplitudes of the waveforms,
+%
+where $h_q^+(t)$ and $h_q^\times(t)$ are the two polarisations of the waveform
+and $t$ is the time. As mentioned, some of the waveforms used in the work are
+generated with the simulations being axisymmetric, in which case the waveforms
+are entirely described by one polarisation $h_q^+(t)$. The corresponding
+$h_q^\times(t)$ for these waveforms are defined as a vector of zeros.~\cm{This
+slightly worries me that classification between models may be artifically
+enhanced by forcing the cross polarisation to be zero. The network might be
+able to easily use this to distinguich between classes when in reality
+waveforms will not show this property. A referee may have the sam concern.}
+
+%
+% rescaling the amplitudes for differnet distances
+%
+In this work, we perform simulations for distances equal to $10$, $20$, $30$,
+$40$, $50$, $60$, $80$, $100$, $150$ and $200$ kpc. If for a training
+procedure, the default distance $d_\text{L}$ of a waveform is not $10$ kpc, the
+following relationship is employed to scale the amplitudes of the waveforms,
+
 \begin{equation}\label{eq:sap} 
- \bold{s}^{d_\text{L}}_q(t) =  \frac{10\text{kpc}\times\bold{s}_q(t)}{d_\text{L}},
+\bold{s}^{d_\text{L}}_q(t) =
+\frac{10\text{kpc}\times\bold{s}_q(t)}{d_\text{L}}, 
 \end{equation} 
-where $\bold{s}^{d_\text{L}}_q(t)$ is the waveform if the source is at $d_\text{L}$ from earth.
-
-The next step is to generate simulated time series for the \ac{GW} detectors in a network using $\bold{S}(t)$.
-%The input data consist of simulated time-series from a network of \ac{GW} detectors.
-Since the purpose of building a \ac{CNN} is to categorise an input data into three exclusive classes,
-in total three types of time-series are generated.
-For the time series containing either a magnetorotational signal or a neutrino-driven signal, 
-we start by selecting a waveform $\bold{s}_q$ from $\bold{S}(t)$.
-A random location of (right ascension, declination) $=(\alpha, \delta)$ in the sky is selected from a uniform distribution on $\alpha$ and a uniform distribution on the sine of $\delta$.
-The corresponding antenna patterns $\bold{F}(\alpha, \delta, t)$, given by the following equation,
+%
+where $\bold{s}^{d_\text{L}}_q(t)$ is the waveform for the source at $d_\text{L}$
+from earth.~\cm{this equation and preceeding text is kind of obvious and could
+be said in far less words. You just simply rescale the amplitude by the
+distance since the amplitude is inversely proportional to the distance.}
+
+%
+% Apply antenna patterns
+%
+The next step is to generate simulated time-series for the \ac{GW} detectors in
+a network using $\bold{S}(t)$.
+%The input data consist of simulated time-series from a network of \ac{GW}
+%detectors.
+Since the purpose of building a \ac{CNN} is to categorise an input data sample
+into three exclusive classes, in total three types of time-series are
+generated.  For the time series containing either a magnetorotational signal or
+a neutrino-driven signal, we start by selecting a waveform $\bold{s}_q$ from
+$\bold{S}(t)$. A random location of (right ascension, declination) $=(\alpha,
+\delta)$ in the sky is selected from a uniform distribution on $\alpha$ and a
+uniform distribution on $\sin\delta$. The corresponding antenna patterns
+$\bold{F}(\alpha, \delta, t)$, given by the following equation~\cm{the
+following equation doesn't give you the antenna patterns. It just lists them as
+an array. Do you really need this array format to explain the waveforms? Does
+it help you?},
+%
 \begin{equation}\label{eq:ap}
@@
 \end{equation}
-is computed, 
-where $f^+(\alpha, \delta, t)$ and $f^{\times}(\alpha, \delta, t)$ are the antenna pattern functions for the two polarizations and $k$ is the number of detectors as defined above.
-The relative delays in the arrival times for the location are also computed and applied to the selected waveform.
-The delay in arrival time between a detector and the center of the earth is given by,
+%
+is computed, where $f^+(\alpha, \delta, t)$ and $f^{\times}(\alpha, \delta, t)$
+are the antenna pattern functions for the two polarizations and $k$ is the
+number of detectors as defined above~\cm{How do you select $t$ and what does it
+represent?}.
+
+%
+% the time delays
+%
+The relative delays in the arrival times of the signals at each
+detector are a function of the sky location and are also computed and applied
+to the selected waveform. The delay in arrival time between a detector and the
+center of the earth is given by,
+%
 \begin{equation}\label{eq:tdetector}
-%
-\Delta t = \frac{\bold{n} \cdot \bold{r}}{c},
-%
+\Delta t = \frac{\bold{n}(\alpha,\delta) \cdot \bold{r}}{c},
 \end{equation}
 %
-where $\bold{n}$ is the propagation direction of the \ac{GW}, $c$ the speed of light, and $\bold{r}$ the location vector of the detector
-relative to the center of the Earth. 
-The resulting signal $ \bold{h}_j(\alpha, \delta, t)$ as received at the detectors is then given by the following equation,
+where $\bold{n}(\alpha,\delta)$ is the propagation direction of the \ac{GW},
+$c$ is the speed of light, and $\bold{r}$ the location vector of the detector
+relative to the center of the Earth. The resulting $j$'th signal $\bold{h}_j(\alpha,
+\delta, t)$ received by the detector network is then described by,
+%
 \begin{equation}\label{eq:ht2}
- \bold{h}_j(\alpha, \delta, t) = \bold{F}(\alpha, \delta, t) \times \bold{s}_q(t),
+ \bold{h}_j(\alpha, \delta, t) = \bold{F}(\alpha, \delta, t) \times
+\bold{s}_q(t+\bold{\Delta t}),
 \end{equation}
-where the time delays $\Delta t$ are absorbed into the corresponding notations and the subscript $j$ is defined in Eq.\ref{eq:cce}.
-Next, we generate independent Gaussian noise $\bold{N}_j(t) = \{\bold{n}_{1j}(t), \bold{n}_{2j}(t), ..., \bold{n}_{kj}(t)\}'$ 
-for each detector in the network using their respective power spectral densities.  
-In the above notation, the symbol $'$ indicates transpose. 
-%It is worth mentioning that although in reality, 
-%noise at \ac{GW} detectors may not be entirely Gaussian and contaminated with glitches,
-%the application of \ac{CNN} is actually not limited to time series where the noise is Gaussian.
-%Although  we will focus on Gaussian noise in this work, 
-%a \ac{CNN} can in fact be trained to identify the presence of a glitch in the data \cite{mukund2017transient, zevin2017gravity, george2017deep, gabbard2018matching}.
-The duration of the generated noise is $1.6$ times longer than $ \bold{h}_j(\alpha, \delta, t)$. 
-A random number $x$ will then be generated determining where in the generated noise the signal will be placed, as given by,
+%
+where the time delays $\Delta t$ are absorbed into the corresponding notations
+and the subscript $j$ is defined in Eq.\ref{eq:cce}~\cm{I changed the equation
+to be more explicit so you don't have to say this previous sentence.}.
+
+%
+% adding noise
+%
+Next, we generate independent Gaussian noise $\bold{N}_j(t) =
+\{\bold{n}_{1j}(t), \bold{n}_{2j}(t), ..., \bold{n}_{kj}(t)\}'$ for each
+detector in the network using their respective power spectral
+densities~\cm{give references and name the detector epoch, e.g., advanced
+design, O2, 3rd gen, etc..}. In the above notation, the symbol $'$ indicates
+transpose~\cm{why is the noise transpose and not the signal? Maybe I'll find
+out as I keep reading.}. 
+%It is worth mentioning that although in reality, noise at \ac{GW} detectors
+%may not be entirely Gaussian and contaminated with glitches, the application
+%of \ac{CNN} is actually not limited to time series where the noise is
+%Gaussian.  Although  we will focus on Gaussian noise in this work, a \ac{CNN}
+%can in fact be trained to identify the presence of a glitch in the data
+%\cite{mukund2017transient, zevin2017gravity, george2017deep,
+%gabbard2018matching}.
+The duration of the generated noise is $1.6$ times longer than
+$\bold{h}_j(\alpha, \delta, t)$~\cm{Don't start off explanations like this. It
+makes the reader think that you are simply declaring something as fact without
+explaining it}. A random number $x$~\cm{what kind of random number? I assume
+uniform but between what limits?} will then be generated determining where in
+the generated noise the signal will be placed, as given by,
+%
 \begin{equation}
@@
 \end{equation}
-This is to avoid the possibility that the \ac{CNN} learns human artefact instead of common features of the waveforms by having the signals always starting at the same place.
-For each time series of the background noise class, independently simulated Gaussian background noise of the same duration as that of the other classes 
-are generated for each detectors in the network.
-This means a data sample for this class is defined as,
+%
+~\cm{please define $\tau$.} This is to avoid the possibility that the \ac{CNN}
+learns the human artefact instead of common features of the waveforms by having
+the signals always starting at the same place.~\cm{well kind of. The reason you
+randomise is that the start time is an unknown parameter so you simply want the
+network to learn to generalise to deal with that kind of variation. Fixing the
+start time at the stame value each time is indeed a human feature but so is
+fixing the distance and all the other things that you fix.} For each
+time-series of the background noise class, independently simulated Gaussian
+background noise~\cm{you need to make it clear that you are also generating
+this noise from the detector PSDs. You could also just say that the background
+noise class is produced identically but with a zero amplitude signal.} of the
+same duration as that of the other classes are generated for each detector in
+the network. This means a data sample for this class is defined as,
+%
 \begin{equation}\label{eq:noise}
@@
 
-Since training a \ac{CNN} of a given structure to its maximum capacity requires many data samples, we augment our data set by iterating over $\bold{S}(t)$ until 
-for each waveform in $\bold{S}(t)$, we have $31$ data samples $\bold{d}$ generated using the procedure described above.
-This step is essential for the \ac{CNN} to learn the features of the waveforms and to identify them effectively under different noise scenarios.
-After that, we generate independent noise realisations for the background noise class.
-The entire data set $\bold{D}$ defined below, has roughly $l = 1.8 \times 10^{5}$ data samples, where each class has approximately $6\times10^{4}$ data samples.
+%
+% data augmentation
+%
+As a general rule, the performance of a \ac{CNN} can always be enhanced by
+increasing the volume of training data. Therefore we augment our data set by
+iterating over $\bold{S}(t)$ until for each waveform in $\bold{S}(t)$, we have
+$31$ data samples $\bold{d}$ generated using the procedure described above.
+This step is essential for the \ac{CNN} to learn the features of the waveforms
+and to identify them effectively under different noise scenarios and starting
+times.  After that, we generate independent noise realisations for the
+background noise class. The entire data set $\bold{D}$ defined below, has
+roughly $l = 1.8 \times 10^{5}$ data samples, where each of the 3 classes
+contains approximately $6\times10^{4}$ data samples.
+%
 \begin{equation}\label{eq:finaldata}
@@
 \end{equation}
-In the above equation, the subscript $o$ is the sum of the data samples in which there is a \ac{GW} signal in the time series. 
-The final step is to whiten $\bold{D}$ using the power spectral densities.
-In Figure \ref{fig:sample}, a representative example  of time series for one detector is shown. 
+%
+In the above equation, the subscript $o$ is the sum of the data samples in
+which there is a \ac{GW} signal in the time series.~\cm{this notation is very
+confusing and not really required. Why do you have to stack the waveforms up
+like this? Having to define things like $o$ and $l$ seems messy.} The final
+step is to whiten $\bold{D}$ using the power spectral densities~\cm{If you are
+going to spend effort explaining how you rescale distances (a very simple
+procedure) then you should definitley describe how you whiten the data}.
+
+%
+% the general training procedure
+%
+In Fig.~\ref{fig:sample}, we show a representative example of a pre-processed
+input time-series for a single detector. A data sample consists of such a
+time-series containing a signal from the same source or simply background noise
+from all the detectors in the network. The data samples are then split into 3
+groups, with $1\times10^{4}$ samples being randomly selected for validation,
+$10\%$ of the remainder for testing and $90\%$ for training. When the training
+is finished for a dataset generated at a given distance, the above described
+procedure will be repeated for another distance until the training for all
+distances have been carried out for a network~\cm{You need to make it clear
+that you are training different networks (with the same architecture) for each
+distance and not iterativley training the same single network.}. The entire
+procedure is then repeated for another network~\cm{the word network is being
+used to describe the CNN and the IFOs, it might be a bit confusing} of \ac{GW}
+detectors. As mentioned previously~\cm{when was it mentioned previoulsy? give a
+ref to the section.}, the \ac{CNN} will be trained for the two networks of
+\ac{GW} detectors presented in Table~\ref{table:network}. For the remaining of
+the paper, we will use their acronyms to refer to the networks~\cm{what are
+these acronymns, state them here.}.
+
+%
+% plot of representative data sample
+%
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{datasample.png}
-\caption{Representative example of the simulated time series used to train/validate/test the \ac{CNN}.
-The blue shows a whitened time series with a signal buried in Gaussian noise of unit variance.
-The red shows the same signal free of noise and whitened. 
-\label{fig:sample}}
+\caption{A representative example of the simulated time-series used to
+train/validate/test the \ac{CNN}. The blue shows a whitened time-series with a
+signal added to Gaussian noise of unit variance~\cm{if you've whitened it then
+of course the noise is zero mean and unit variance - that's the definition so
+no need to say it twice.}. The red curve shows the same whitened signal free of
+noise.~\cm{what waveform is this and what is it's SNR? Please state this in the
+caption. Is this a representative SNR that you can detect? If not then why show
+it.}\label{fig:sample}} 
 \end{figure}
-A data sample consists of such time series of the same signal or background noise from all the detectors in the network.
-The data samples are then split, with $1\times10^{4}$ samples being randomly taken for validation, $10\%$ of the rest for testing and $90\%$ for training.
-When the training is finished for a distance, 
-the above described procedure will be repeated for another distance until the training
-for all distances have been carried out for a network.
-The entire procedure is then repeated for another network of \ac{GW} detectors.
-As mentioned previously, the \ac{CNN} will be trained for two networks of \ac{GW} detectors.
-We present the networks in Table \ref{table:network}. For the remaining of the paper, we will use their acronyms to refer to the networks.
+
 \begin{table}[]
@@
 \item The networks of detectors used in this work.\\
-* H refers to the detector in Hanford and L the detector in Livingston.}
+* H refers to the detector in Hanford and L the detector in Livingston.~\cm{you
+* have enough space to simply use Hanford and Livingston in the table itslef.
+* You could also have a column for references to the detector papers.}}
 \end{tablenotes}

### 2019-12-11 main.tex
Completed my comments

@@
 \section{Result and discussion}\label{sec:result}
-After the \ac{CNN} is trained, we can estimate its performance using the testing samples.
-The results are presented in this section.
-One of the most used and convenient ways to determine the classifying performance of a model is to plot the \ac{ROC} curve.
-A \ac{ROC} shows the performance of a classifying model by showing the \ac{TAP} at a given \ac{FAP}. 
-Since \ac{ROC} is usually plotted for model distinguishing two classes, 
-for a multi-class classification problem, 
-a \ac{ROC} for a class should be viewed as the class versus the others.
-This means in this context, \ac{FAP} means the fraction of samples from other 
-classes misidentified as a sample from the class the \ac{ROC} is associated with.
-\ac{TAP} is identical to that of two-class classification problem and indicates the fraction of samples correctly identified.
-For a given \ac{FAP}, a model with a higher \ac{TAP} is considered more capable than a model with a lower \ac{TAP}.
-In Figure \ref{fig:ROClog}, we show the \acp{ROC} for both the mechanisms and \ac{GW} detector networks tested in this work. 
-For simplicity, we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
+%
+% Introduction to the ROC results
+%
+After the \ac{CNN} is trained, we can estimate its performance using the
+testing samples~\cm{what about the validation samples? These haven't been
+motivated yet.} and the results of which are presented in this section. One of
+the most commonly used and convenient ways to determine the classification
+performance of a \ac{CNN} or equivelent signal detection algorithm is to plot
+the \ac{ROC} curve. A \ac{ROC} shows the performance of a classifying model by
+defining the \ac{TAP} as a function of the \ac{FAP}. Since \ac{ROC} curves are
+usually plotted for models distinguishing between two classes, for a
+multi-class classification problem, a \ac{ROC} for a class should be viewed as
+the class versus the others. This means in this context, \ac{FAP} means the
+fraction of samples from other classes misidentified as a sample from the class
+the \ac{ROC} is associated with. The \ac{TAP} is identical to that of a
+two-class classification problem and indicates the fraction of samples
+correctly identified.  For a given \ac{FAP}, a model with a higher \ac{TAP} is
+considered more capable than a model with a lower \ac{TAP}~\cm{it appears to me
+that you haven't actually defined what your classification statistic is. Can
+you make sure that the reader understands that how you go from the output of
+the final sigmoid layer to making ROC curves. You have to define a detction
+statistic.}.
+
+%
+% describe ROC curve plots (Fig 5)
+%
+In Fig.~\ref{fig:ROClog}, we show the \acp{ROC} for both of the \ac{CCSN}
+mechanisms and \ac{GW} detector networks tested in this work. For simplicity,
+we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
+For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any
+given \acp{FAP} for magnetorotational than neutrino-driven signals.  That is
+not surprising as the intrinsic amplitudes for magnetorotational signals are
+higher than those of neutrino-driven signals~\cm{maybe a bit more description?
+Maybe give some detection probabilities at standard FAP values in the text?}.
+
 \begin{figure*}
      \begin{center}
-%
-        \subfigure[]{%
-            \label{fig:ROClog1}%
+        \subfigure[]{
+            \label{fig:ROClog1}
             \includegraphics[width=0.45\textwidth]{ROC_curves_neutrino.png}%
         }\quad
-        \subfigure[]{%
+        \subfigure[]{
             \label{fig:ROClog2}
             \includegraphics[width=0.45\textwidth]{ROC_curves_mag.png}%
-        }%
-%
+        }
     \end{center}
-    \caption{ROC curves showing the classification performance of the \ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three distances, $20$, $60$, and $100$kpc.
-The left panel shows the results for the neutrino-driven mechanism, while the panel on the right shows those for the magnetorotational mechanism.
-In both panels, the solid lines are for the network H+L+VK, while the dashed lines are for HLVK.
-\label{fig:ROClog}}%
+    \caption{\ac{ROC} curves showing the classification performance of the
+\ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three
+distances, $20$, $60$, and $100$kpc. The left panel shows the results for the
+neutrino-driven mechanism, while the panel on the right shows those for the
+magnetorotational mechanism. In both panels, the solid lines are for the
+network H+L+VK, while the dashed lines are for HLVK.~\cm{please make these
+plots square with equal length sides. Also add a diagonal line to indicate the
+worst performance bound. Also make the y-axis scales the same for both plots or
+at least highlight the fact that they are different in the text since it is
+initially misleading. The legends don't need to have both solid and dashed
+lines. Also add sub-labels indicateing that the left is magneto and the right
+is neutrino.}\label{fig:ROClog}} 
 \end{figure*}
-For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any given \acp{FAP} 
-for magnetorotational than neutrino-driven signals.
-That is not surprising as the amplitudes for magnetorotational signals are higher than that of neutrino-driven signals.
-
-We can also show the classification efficiency of the \ac{CNN}  as a function of distance.
-This is done by fixing the \ac{FAP} and plotting the \ac{TAP}. 
-The results for three chosen \acp{FAP} are shown in Figure \ref{fig:eff}.
+
+%
+% discuss the accuracy as a function of distance (Fig 6)
+%
+We also show the classification efficiency of the \ac{CNN}  as a function of
+distance.  This is done by fixing the \ac{FAP} and plotting the \ac{TAP}.  The
+results for three chosen \acp{FAP} values are shown in Fig.~\ref{fig:eff}.  In
+this figure, a similar trend is seen that magnetorotational signals are easier
+for the \ac{CNN} to identify than neutrino-driven signals at a given distance.
+For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
+of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the
+networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
+$0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at
+the same distance for the two networks respectively.  For sources that are
+located at a slightly further distance of $60$ kpc, both networks achieve a
+\ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$. Such a range
+includes distances associated with the Large and Small Magellanic Clouds and
+covers the satellite galaxies imbetween~\cite{karachentsev2004catalog,
+belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are close to or
+larger than $60\%$ for H+L+VK for all chosen \acp{FAP} values, and is $73\%$ if
+the \ac{FAP} is $0.1$. Even for sources at $150$ and $200$ kpc, the \acp{TAP}
+are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with
+such a \ac{GW} network, it is possible to detect magnetorotational \ac{CCSN}
+signals out to such a distance. On the other hand, it is more difficult for the
+\ac{CNN} to detect and classify the neutrino-driven signals, due to their
+weaker amplitudes. Nonetheless, for sources at $10$ kpc, the \ac{CNN} achieves
+a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the
+\ac{FAP} is $0.1$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
+signal it is possible to detect and classify it with either of these \ac{GW}
+detcetor networks.
+
+%
+% the TAP as a function of distance
+%
 \begin{figure*}
      \begin{center}
-%
-        \subfigure[]{%
-            \label{fig:eff1}%
-            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}%
+        \subfigure[]{
+            \label{fig:eff1}
+            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}
         }\quad
-        \subfigure[]{%
+        \subfigure[]{
             \label{fig:eff2}
-            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}%
-        }%
-%
+            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}
+        }
     \end{center}
-    \caption{Efficiency curves showing the classification ability of the \ac{CNN} as a function of distance for both mechanisms and networks.
-The left panel shows the results for the neutrino-driven mechanism, while the right shows those for the magnetorotational mechanism. 
-In both panels, the solid lines show the results for the network H+L+VK, and the dashed lines for HLVK.
-Three \acp{FAP} are chosen, i.e.: blue for \ac{FAP} $=0.1$, green for \ac{FAP} $=0.01$, red for \ac{FAP} $=0.001$.
-\label{fig:eff}}%
+    \caption{Efficiency curves showing the classification ability of the
+\ac{CNN} as a function of distance for both mechanisms and networks.  The left
+panel shows the results for the neutrino-driven mechanism, while the right
+shows those for the magnetorotational mechanism. In both panels, the solid
+lines show the results for the network H+L+VK, and the dashed lines for HLVK.
+Three \acp{FAP} values are chosen, blue for \ac{FAP} $=0.1$, green for \ac{FAP}
+$=0.01$, red for \ac{FAP} $=0.001$.\label{fig:eff}}
 \end{figure*}
-In this figure, a similar trend is seen that magnetorotational signals are easier for the \ac{CNN} to identify than neutrino-driven signals at any distance. 
-For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP} of $0.1$, 
-the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the networks H+L+VK and HLVK respectively.
-At more restrict \acp{FAP} such as $0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at the same distance for the two networks respectively.
-For sources that are located at a slightly further distance of $60$ kpc, both networks achieve a \ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$.  
-Such a range is well into the Large and Small Magellanic Clouds and covers the satellite galaxies in between\cite{karachentsev2004catalog, belokurov2007cats}.
-For sources at $100$ kpc, the \acp{TAP} are close to or larger than $60\%$ for H+L+VK for all chosen \acp{FAP}, and is $73\%$ if the \ac{FAP} is $0.1$.  
-Even for sources at $150$ and $200$ kpc, the \acp{TAP} are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with such a \ac{GW} network,
-it is possible to detect magnetorotational \ac{CCSN} signals out to such a distance.
-On the other hand, it is more difficult for the \ac{CNN} to detect and classify the neutrino-driven signals, due to their weaker amplitudes.
-Nonetheless, for sources at $10$ kpc,
-the \ac{CNN} achieves a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the \ac{FAP} is $0.1$.
-This means that the \ac{GW} from a Galactic \ac{CCSN} signal is possible to be detected and classified with either of these networks.
+
+%
+% the TAP vs distance plot for fixed threshold
+%
 \begin{figure*}
      \begin{center}
-%
-        \subfigure[]{%
-            \label{fig:ROCfixed1}%
-            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}%
+        \subfigure[]{
+            \label{fig:ROCfixed1}
+            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}
         }\quad
-        \subfigure[]{%
+        \subfigure[]{
             \label{fig:ROCfixed2}
-            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}%
-        }%
-%
+            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}
+        }
     \end{center}
-    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data with a fixed decision threshold(0.5), and their corresponding \acp{FAP}.
-    The left panel shows the results for the neutrino-driven mechanism, and the right shows that for the magnetorotational mechanism.
-    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the dashed lines show those for HLVK.  
-\label{fig:ROCfixed}}%
+    \caption{Efficiency curves showing the ability of the \ac{CNN} in
+distinguishing input data with a fixed decision threshold $(0.5)$~\cm{what is
+this? Is it defined in the text?}, and their corresponding \acp{FAP}~\cm{and
+TAP?}. The left panel shows the results for the neutrino-driven mechanism, and
+the right shows that for the magnetorotational mechanism. In both panels, the
+solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the
+dashed lines show those for HLVK.\label{fig:ROCfixed}}
 \end{figure*}
 
-In practice, since the output of a \ac{CNN} is probabilities indicating how likely the input belongs to each of the classes, 
-it may be desired to set a threshold on which the decision whether the input belong to a class is made.
-For example, an input will be classified into a class if the corresponding probability is larger than the pre-selected threshold.
-In such a scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the threshold.
-We show such a result in Figure \ref{fig:ROCfixed}, where we employed a threshold of $0.5$. 
-For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. 
-If the distance is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.
-For the largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are $43\%$ and $29\%$ respectively.
-For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and $80$ kpc respectively.
+In practice, since the output of a \ac{CNN} is probabilities indicating how
+likely the input belongs to each of the classes, it may be desired to set a
+threshold on which the decision whether the input belong to a class is made.
+For example, an input will be assigned into a certain class if the
+corresponding probability is larger than the pre-selected threshold. In such a
+scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the
+threshold. We show such a result in Fig.~\ref{fig:ROCfixed}, where we employed
+a threshold of $0.5$~\cm{I'm a bit confused. You have 3 classes so how exactly
+are you doing this analysis? You mentioned before that you are treating one
+class vs the remainder but when you talk about magneto does that mean that the
+other model is noise AND neutrino. That would be strange.}. For H+L+VK and
+magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. If the distance
+is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.  For the
+largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are
+$43\%$ and $29\%$ respectively~\cm{these numbers don't seem to match the
+plot.}. For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and
+$80$ kpc respectively.
 %The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
-Throughout the distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for both networks.
-For neutrino-driven signals, it is shown that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it is $55\%$ at $10$ kpc for HLVK.
-Both of the networks have \acp{FAP} close to or less than $0.2$.
-It should be noted that the results presented here are averaged over all the data samples in the testing samples.
-The performance on any individual waveform may vary depending on the morphology and the amplitudes of the waveform.
+For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for
+both networks regarding magnetorotational waveforms. For neutrino-driven
+signals, we show that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it
+is $55\%$ at $10$ kpc for HLVK.  Both of the networks have \acp{FAP} close to
+or less than $0.2$. It should be noted that the results presented here are
+averaged over all the data samples in the testing samples. The performance on
+any individual waveform may vary depending on the morphology and the amplitudes
+of the waveform.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Waveforms Excluded from Training}\label{sec:unseen}
-The above section proves that using a \ac{CNN}, it is possible to detect and classify \ac{CCSN} waveforms 
-if the waveforms have been used to train the \ac{CNN}. 
-However, in reality, it is likely that the \acp{GW} from a \ac{CCSN} may only be partially similar to the simulated waveforms, 
-while having some other features that are different or even unexpected. 
-A \ac{CNN} that is only capable of recognising waveforms with which it is familiar may prove to be not entirely applicable.
-Therefore, we apply our trained \ac{CNN} to waveforms from other studies that were not used during the training.
-Similar to what was done in \cite{roma2019astrophysics}, 
-we take the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from \cite{scheidegger2010influence} as the test waveforms for the magnetorotational mechanism.
-The test waveforms for the neutrino-driven mechanisms are $\text{s}20$ from \cite{andresen2017gravitational} and $\text{SFHx}$ from \cite{kuroda2016new}.
-The waveforms are shown in Figure \ref{fig:Extratestwaveform}.
-The test waveforms in this section should not be confused with the testing samples in section \ref{sec:result}, 
-which are randomly drawn from the same distribution as the training samples.
+%
+% introduce the issue of test samples from different families
+%
+The previous section proves that using a \ac{CNN}, it is possible to detect and
+classify \ac{CCSN} waveforms if appropriate waveforms have been used to train
+the \ac{CNN}. However, in reality, it is likely that the \acp{GW} from a
+\ac{CCSN} may only be partially similar to the simulated waveforms, while
+having some other features that are different or even unexpected. A \ac{CNN}
+that is only capable of recognising waveforms with which it is familiar may
+prove to be not be entirely applicable. Therefore, we apply our trained
+\ac{CNN} to waveforms from other studies that were not used during the
+training. Similar to the procedure used in~\cite{roma2019astrophysics}, we take
+the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
+from~\cite{scheidegger2010influence} as the test waveforms for the
+magnetorotational mechanism. The test waveforms for the neutrino-driven
+mechanisms are $\text{s}20$ from~\cite{andresen2017gravitational} and
+$\text{SFHx}$ from~\cite{kuroda2016new}. Examples of these waveforms are shown
+in Fig.~\ref{fig:Extratestwaveform}. The test waveforms in this section should
+not be confused with the testing samples in Sec.~\ref{sec:result}, which are
+randomly drawn from the same distribution as the training samples.
+
+%
+% plots of extra test waveforms
+%
 \begin{figure}
      \begin{center}
-%
-        \subfigure[]{%
-            \label{fig:ex_waveform_neu}%
-            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}%
+        \subfigure[]{
+            \label{fig:ex_waveform_neu}
+            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}
         }\quad
-        \subfigure[]{%
+        \subfigure[]{
             \label{fig:ex_waveform_mag}
-            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}%
-        }%
-%
+            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}
+        }
     \end{center}
-    \caption{The waveforms excluded from the training session of the \ac{CNN} and used as an extra test for the performance of the \ac{CNN}.
-    From the top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$(neutrino-driven mechanism), 
-    $\text{R3E1AC}$ and $\text{R4E1FC\_L}$(magnetorotational mechanism), respectively. 
-    The time in the x-axis is not related to core bounce.
-\label{fig:Extratestwaveform}}%
+    \caption{The waveforms excluded from the training session of the \ac{CNN}
+and used as an extra test for the performance of the trained \ac{CNN}. From the
+top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$
+(neutrino-driven mechanism), $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
+(magnetorotational mechanism), respectively. The time in the x-axis is not
+related to core bounce~\cm{again, why state this (same comment as for Fig.
+2}.\label{fig:Extratestwaveform}} 
 \end{figure}
+
+%
+% 
+%
 \begin{figure}
      \begin{center}
-%
-        \subfigure[]{%
-            \label{fig:extra_waveform_test_neu}%
-            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}%
+        \subfigure[]{
+            \label{fig:extra_waveform_test_neu}
+            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}
         }\quad
-        \subfigure[]{%
+        \subfigure[]{
             \label{fig:extra_waveform_test_mag}
-            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}%
-        }%
-%
+            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}
+        }
     \end{center}
-    \caption{Efficiency curves showing the ability of the \ac{CNN} in distinguishing input data.
-    The upper panel shows the results for the the waveforms $\text{SFHx}$ and $\text{s}20$ (neutrino-driven mechanism), 
-    and the lower panel shows that for the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ (the magnetorotational mechanism).
-    In both panels, the solid lines show the \acp{TAP} and \acp{FAP} for H+L+VK, and the dashed lines show those for HLVK.  
+    \caption{Efficiency curves showing the ability of the \ac{CNN} in
+distinguishing input data.  The upper panel shows the results for the the
+waveforms $\text{SFHx}$ and $\text{s}20$ (neutrino-driven mechanism), and the
+lower panel shows that for the waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
+(the magnetorotational mechanism).  In both panels, the solid lines show the
+\acp{TAP} and \acp{FAP} for H+L+VK, and the dashed lines show those for HLVK.
 The waveforms have not been used for the training of the \ac{CNN}.
-\label{fig:Extratest}}%
+\label{fig:Extratest}}
 \end{figure}
-Using the procedure described in section \ref{sec:spwf}, we generate $1200$ injections for each distance and each class has around 400 injections.
-The performance of the \ac{CNN} on the test waveforms are shown in Figure \ref{fig:Extratest}.
-For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$ with H+L+VK and $59\%$ with HLVK respectively.
-At $60$kpc, the \acp{TAP} drop slightly to $83\%$ and $52\%$ respectively.
-This indicates that with the \ac{CNN}, it is possible to detect these waveforms from sources that are well into the Large and Small Magellanic Clouds.
-For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$. 
-The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably higher than that for the neutrino-driven mechanism in Figure \ref{fig:eff} for the same distance.
-This is because as mentioned before, the detection and classification efficiency in Figure \ref{fig:eff} are the results averaged over the testing samples.
-It is possible that individual waveforms may be easier for the \ac{CNN} to detect. The results indicate that the \ac{CNN} has generalised the features of the explosion mechanisms.
+
+%
+% the new test waveofmr procedure
+%
+Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1200$
+injections~\cm{injections is jargon. Use the same terminolgy as used in the
+rest of the paper} for each distance and therefore each class has $\sim 400$
+injections. The performance of the \ac{CNN} on the test waveforms is shown in
+Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
+at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$
+with H+L+VK and $59\%$ with HLVK respectively. At $60$kpc, the \acp{TAP} drops
+slightly to $83\%$ and $52\%$ respectively. This indicates that with the
+\ac{CNN}, it is possible to detect these waveforms from sources that are at
+distances consistent with the Large and Small Magellanic Clouds. For waveforms
+$\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two
+networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$.  The
+efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
+higher than that for the neutrino-driven mechanism in Fig.~\ref{fig:eff} for
+the same distance. This is because as mentioned before, the detection and
+classification efficiency in Fig.~\ref{fig:eff} are the results averaged over
+the testing samples. It is possible that individual waveforms may be easier for
+the \ac{CNN} to detect and the results here also indicate that the \ac{CNN} has
+generalised the features of the explosion mechanisms.~\cm{this last statement
+is very vague and needs clarification. What are features? and what does
+generalisation mean in this context?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}\label{sec:conclusion}
-We have demonstrated a \ac{CNN} can be applied for the purpose of distinguishing \ac{GW} detector time series 
-among pure background noise and \ac{CCSN} explosion mechanisms. 
-We trained the \ac{CNN} using $1.8\times10^{5}$ samples of simulated time series for each distance in a number of distances from $10$kpc to $200$kpc.
-The data samples for each classes consisted of approximately $4\times10^5$ samples.
-
-We have shown that with a network of HLVK, when the \ac{FAP} was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
-for magnetorotational signals from sources at $60$ kpc. 
-Using a network of H+L+VK, we showed that the \ac{TAP} could be even more promising at $91\%$. Both the Large and Small Magellanic Clouds are within this distance.
-If the distance is extended to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ 
-respectively are still achievable for H+L+VK, indicating the possibility of detections within such distances.
-
-For the neutrino-driven mechanism, the weaker amplitudes of the waveforms result in lower \acp{TAP} at the same distances.
-For sources at $10$kpc, the trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and $76\%$ for HLVK and H+L+VK respectively.
-This indicates a Galactic \ac{CCSN} event is likely to be detectable.
-
-We used four waveforms that were not used for the training of the \ac{CNN} to test the performance of the \ac{CNN} in a more realistic situation.
-We found that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at $60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
-For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two networks respectively.
-The results prove the possibility of using \ac{CNN} for the detection and classification of \ac{CCSN} \ac{GW} signals.
-\\
+%
+% overall main message
+%
+We have demonstrated that a \ac{CNN} can be applied for the purpose of
+distinguishing \ac{GW} detector time-series among pure background noise and
+\ac{CCSN} explosion mechanisms. We have trained the \ac{CNN} using
+$1.8\times10^{5}$ samples of simulated time series for each distance at a
+number of distances from $10$kpc to $200$kpc. The data samples for each
+class consisted of approximately $4\times10^5$ samples.
+
+%
+% Primary magneto results
+%
+We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
+was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
+for magnetorotational signals from sources at $60$ kpc. Using a network of
+H+L+VK, we showed that the \ac{TAP} is imcreased to $91\%$.  Both the Large and
+Small Magellanic Clouds are within this distance. If the distance is extended
+to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ respectively are still
+achievable for H+L+VK, indicating the small possibility of detections within
+such distances.
+
+%
+% not so good neutrino results
+%
+For the neutrino-driven mechanism, the weaker amplitudes of the waveforms
+result in lower \acp{TAP} at the same distances.  For sources at $10$kpc, the
+trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and
+$76\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
+event would likely be detectable.
+
+%
+% statement about out of treaining data extra test samples
+%
+We used four waveforms that were not used for the training of the \ac{CNN} to
+test the performance of the \ac{CNN} in a more realistic situation. We found
+that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at
+$60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
+For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and
+$70\%$ for the two networks respectively. The results prove the possibility of
+using a \ac{CNN} as a tool for the detection and classification of \ac{CCSN}
+\ac{GW} signals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{ACKNOWLEDGEMENTS}
-I.S.H. and C.M. are supported by
-the Science and Technology Research Council (grant No.
-ST/L000946/1) and the European Cooperation in
-Science and Technology (COST) action CA17137. 
+%
+%
+%
+I.S.H. and C.M. are supported by the Science and Technology Research Council
+(grant No.~ST/L000946/1) and the European Cooperation in Science and
+Technology (COST) action CA17137.
+
 \bibliography{main}

### 2020-01-08 main.tex
comments incoporated version

@@
 \usepackage{xcolor}
-\usepackage{hyperref}
+%\usepackage[backref,breaklinks,colorlinks,citecolor=blue, hyperfootnotes=false]{hyperref}
 \usepackage{latexsym}
-\usepackage{url}
+%\usepackage{url}
 \usepackage{multirow}
@@
 %\usepackage[numbers,sort]{natbib}
-\bibliographystyle{unsrt3}
+%\bibliographystyle{unsrt3}
 %\usepackage{subcaption}
@@
 
-\author{Authors$^{12}$\cm{fix}}
+\author{Man Leong Chan$^{1}$, Ik Siong Heng$^{2}$ \& Chris Messenger$^{2}$ }
 \affiliation{
@@
 convolutional neural network with waveforms not used for training, we show that
-the true alarm probabilities are $52\%$ and $83\%$ at $60$kpc for waveforms
+the true alarm probabilities are $52\%$ and $83\%$ at $60$ kpc for waveforms
 $\text{R3E1AC}$ and $\text{R4E1FC\_L}$.  For waveforms $\text{s}20$ and
 $\text{SFHx}$ at $10$ kpc, the true alarm probabilities are $70\%$ and $93\%$
-respectively. All at false alarm probability equal to $0.1$\cm{why is this nopt
-also written as a percentage? Should it be 10\%?}.  \end{abstract}
+respectively. All at false alarm probability equal to $10\%$. 
+\end{abstract}
 
@@
 interferometers~\cite{aso2013interferometer, gossan2016observing,
-abbott2016first}. It is currently not entirely clear to astronomers how such
+abbott2016first, abbott2019optically}. It is currently not entirely clear to astronomers how such
 massive stars become supernovae. The basic theory of the explosion, confirmed
@@
 %
-There exist two most popular theories~\cm{theories for what?}, the
-neutrino-driven mechanism~\cite{bethe1985revival, bethe1990supernova} and the
+There exist two most popular theories for how the shock is revived and a star becomes supernova, 
+the neutrino-driven mechanism~\cite{bethe1985revival, bethe1990supernova} and the
 magnetorotational mechanism~\cite{janka2012explosion, kotake2012core,
-mezzacappa2014two}. For supernova progenitors with core rotation too slow to
+mezzacappa2014two} (also see \cite{obergaulinger2006axisymmetric, obergaulinger2006axisymmetric2} for studies bridging these two theories). 
+For supernova progenitors with core rotation too slow to
 affect the dynamics~\cite{takiwaki2016three, summa2018rotation}, the
@@
 of the observed \acp{CCSN} can be explained by the neutrino
-mechanism~\cite{bruenn2016development}~\cm{why?}. The neutrino
+mechanism~\cite{bruenn2016development}. The neutrino
 mechanism~\cite{bethe1985revival, janka2007theory} suggests that approximately
-$5-10\%$ of the outgoing neutrino luminosity is stored below the shock, which
+$5\%$ of the outgoing neutrino luminosity is stored below the shock, which
 causes turbulence to occur and thermal pressure to increase. The stalled shock
@@
 standing accretion shock instability~\cite{blondin2003stability}. On the other
-hand, the magnetorotational mechanism requires rapid core spin and a strong
+hand, the magnetorotational mechanism may require rapid core spin and a strong
 magnetic field~\cite{leblanc1970numerical, burrows2007simulations,
 takiwaki2009special,
-moiseenko2006magnetorotational,mosta2014magnetorotational}. Together, they may
-produce an outflow that may cause the most energetic \acp{CCSN}
-observed~\cm{are you referring to a real observed CCSN, if so you should
-provide a reference.}. The magnetorotational mechanism may \cm{also?} be able
+moiseenko2006magnetorotational,mosta2014magnetorotational} 
+(this may not be absolutely the case, see e.g. \cite{obergaulinger2019magnetorotational}). Together, they may
+produce an outflow that may cause some of the most energetic \acp{CCSN}
+observed and may be able
 to explain the extreme hypernovae and the observed long gamma-ray
-bursts\cite{woosley2006progenitor, yoon2005evolution, de2013rotation}.
+bursts~\cite{woosley2006progenitor, yoon2005evolution, de2013rotation, obergaulinger2017protomagnetar}.
 
@@
 %could reach us.  However, 
-As \acp{GW} are emitted\cm{generated?} in the central core of a \ac{CCSN}, they
+As \acp{GW} are generated in the central core of a \ac{CCSN}, they
 are likely to carry direct information of the \ac{CCSN} and therefore provide a
@@
 \ac{CBC} events the established method for searching for signals is
-matched-filtering~\cm{give ref for pycbc and gstlal}. However, since the
+matched-filtering~\cite{usman2016pycbc, cannon2012toward}. However, since the
 emission process of the \acp{GW} from \acp{CCSN} is affected by turbulence in
-the post-bounce and is \cm{expected to be?} stochastic in nature,  the signal
+the post-bounce and is expected to be stochastic in nature,  the signal
 evolution cannot be predicted robustly~\cite{ott2009gravitational,
-kotake2013multiple, kotake2009stochastic}.  This in turn prevents
+kotake2013multiple, kotake2009stochastic, aloy2019neutron}.  This in turn prevents
 matched-filtering from being applied to \acp{CCSN}.
@@
 suvorova2019reconstructing}. This method creates a set of component basis
-vectors from a \cm{larger?} set of \ac{CCSN} waveforms belonging to a
+vectors from a larger set of \ac{CCSN} waveforms belonging to a
 particular mechanism where the basis vectors represent the common features of
 those waveforms.  There have been other approaches developed in the literature
-such as Bayesian inference~\cite{rover2009bayesian}, Bayesian model
-selection~\cite{logue2012inferring} , multivariate regression
+such as Bayesian inference~\cite{rover2009bayesian, cannon2012toward}, Bayesian model
+selection~\cite{logue2012inferring}, multivariate regression
 modelling~\cite{engels2014multivariate}, maximum
 entropy~\cite{summerscales2008maximum}, maximum
-likelihood~\cite{gursel1989near} and Tikhonov regularization
+likelihood~\cite{klimenko2016method} and Tikhonov regularization
 scheme~\cite{rakhmanov2006rank, hayama2007coherent}.
@@
 (glitches)~\cite{mukund2017transient, zevin2017gravity, george2017deep} and the
-detection of astrophysical signals~\cite{george2018deep, gabbard2018matching,
-astone2018new} and their parameter estimation~\cm{add ref to Hunters latest
-paper}. A \ac{CNN} is a deep learning algorithm that has the advantage of
-capturing spatial and temporal features of the input data~\cm{this doesn't
-really mean anything. Spatial refers to features in certain locations in images
-and temporal refers to locations in a time series of in the time axis of a
-spectrogram image}. Another advantage of the use of a \ac{CNN} in the detection
+detection of astrophysical signals~\cite{george2018deep, gabbard2018matching, astone2018new},
+and their parameter estimation~\cite{2019arXiv190906296G}.
+An advantage of the use of a \ac{CNN} in the detection
 of a \ac{GW} signal is that a \ac{CNN} is relatively computationally cheap
@@
 \acp{GW} from \acp{CCSN} and to the classification of their explosion
-mechanisms.  To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a
-number of studies and simlate sources at a range of distances from $10$ to
+mechanisms. 
+To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a
+number of studies and simulate sources at a range of distances from $10$ to
 $200$ kpc for two networks of four \ac{GW} detectors. The first network
@@
 detectors of \ac{aLIGO} with a modest set of planned upgrade version of them -
-LIGO A+ in Hanford and Livingston~\cite{miller2015prospects, LIGOW}. We then
-apply the \ac{CNN} to waveforms excluded from the training set to show that the
-\ac{CNN} is not only able to identify the waveforms it familiarised itself with
-during training, but also new waveforms~\cm{this is a strange statement. The
-ability of the CNN to work on the training data is completely outweighed by its
-perfromance on the independent testing set. The testing set perfroamnce is all
-that you should mention here.}.
+LIGO A+ in Hanford and Livingston~\cite{miller2015prospects, LIGOW}. All detectors 
+are at their design sensitivities. We then
+apply the \ac{CNN} to waveforms excluded from the training set to show 
+the performance on an independent testing set.
+Similar to~\cite{astone2018new}, 
+we use machine learning techniques for the search of \acp{GW} from \acp{CCSN}.
+However, the \ac{CNN} developed in ~\cite{astone2018new} takes time-frequency images of \ac{GW} detector 
+data from the coherent WaveBurst pipeline~\cite{klimenko2005constraint} as input, 
+while we aim to develop a \ac{CNN} that works independently and takes time series data from \ac{GW} detectors as input.
 
@@
 %
-A \ac{CNN} is a computational processing system that is composed of
-interconnected layers of computational nodes~\cite{o2015introduction}. The
-nodes are known as neurons and the outputs of which are processed with an
-activation function. The activation function performs an elementwise nonlinear
-operation to the output of the layer. In a standard \ac{CNN}, there are
-commonly three types of layers: convolutional layers, max-pooling layers, and
+A \ac{CNN} is a computational processing system that takes in data and 
+is able to classify the input data as one of the N types it has learnt through training.
+A \ac{CNN} is composed of interconnected layers of computational nodes~\cite{o2015introduction}. 
+The nodes are known as neurons and the outputs of which are processed with an
+activation function. The activation function performs an elementwise non-linear
+operation to the output of the layer. 
+There are commonly three types of layers: convolutional layers, max-pooling layers, and
 fully connected layers~\cite{o2015introduction}. Convolutional layers perform
@@
 \ac{CNN}.  Fully connected layers are layers that connect every neuron in its
-layer to every neuron of its immediate previous and next layer. In the case of
-detection and classification, the output layer is also a fully connected layer
-with a softmax activation function with output used to represent the class
-scores or probabilities.~\cm{even after editing, this isn't the clearest
-description of a CNN. You are lacking an initial statement that says what a CNN
-does - it takes in data and is able to classify it as one of the N types it has
-learnt through training.}
-
-%
-% decribe the structure of the CNN
-%
+layer to every neuron of its immediate previous and next layer.
+
 When multiple layers of these three types are stacked and connected one after
 the other, a \ac{CNN} has been formed, where the output of each layer is the
-input of the next layer. How these layers are connected in a \ac{CNN}, the
+input of the next layer. 
+%
+% decribe the structure of the CNN
+%
+How these layers are connected in a \ac{CNN}, the
 numbers of layers, their type, the number of neurons, the convolutional filter
 size, max-pooling size, and the activation functions used, describes the
-architecture of the \ac{CNN} (also known as hyper-parameters). The first layer
-in a \ac{CNN}, also known as the input layer, is often a convolutional layer,
-while the last layer or the output layer is often a fully connected layer with
-an associated loss function~\cm{the loss isn't really associated with the
-output layer. It is associated withe whole network.}. The architecture of the
-remainder of the \ac{CNN} should depend on the specific task that it is being
+architecture of the \ac{CNN} (also known as hyper-parameters).  
+In a standard \ac{CNN}, 
+the first layer, also known as the input layer and often a convolutional layer, 
+takes in raw values of the input (or time series from \ac{GW} detectors in our case, this will be explained more in section \ref{sec:spwf}).
+The output layer is usually a fully connected layer
+with a softmax activation function with output used to represent the class
+scores or probabilities in the case of detection and classification.
+For a \ac{CNN} designed to classify its input into different classes, 
+the output layer computes the probabilities of the inferred classes.
+The architecture of the remainder of the \ac{CNN} should depend on the specific task that it is being
 trained to solve. An over-complicated model with too many trainable parameters
-makes it easier to result in over-fitting (a procedure where the network
+makes it easier to result in over-fitting, where the network
 essentially memorises the training data but is unable to generalise to new
-data). Alternatively, an overly simple architecture will struggle to capture
+data. Alternatively, an overly simple architecture will struggle to capture
 the features inherent to the input and not perform well in classification.
 Automated schemes do exist for finding the optimal combination of
-hyperparameters but in general (and in our case) the final architecture is
-often obtained through rough trial and error, followed by fine tunning.
+hyperparameters but in general and in our case the final architecture is
+often obtained through rough trial and error, followed by fine tuning.
 
@@
 using an algorithm called back-propagation~\cite{lecun1988theoretical}. The
-output of the \ac{CNN} is used as an input to the loss-function~\cm{you need to
-define what the loss function is supposed to do and how by minimising it you
-make the network produce the right result. It isn't clear here.} and
-back-propagation then computes the gradient of the loss-function with respect
-to the traininable weights and biases within the network. A gradient descent
-algorithm is then used to adjust the values of the weights and biases of the
-neurons in each layer in order to iteratively minimise the loss-function.  When
-the loss function is minimised and training is therefore complete, the \ac{CNN}
+outputs of the \ac{CNN} (the probabilities of the inferred classes in our case) are used as an input to the loss-function that is associated with the entire network.  
+The value of the loss function is used to evaluate how well the algorithm models the input data of the \ac{CNN}.
+After a subset of training data is fed through the \ac{CNN}, the back-propagation algorithm 
+then computes the gradient of the loss-function with respect
+to the trainable weights and biases within the network. 
+The size of the subset of the training data is referred to as batch.
+A gradient descent algorithm is then used to adjust the values of the weights and biases of the
+neurons in each layer in order to iteratively minimise the loss-function.  
+When the loss function is minimised and training is therefore complete, the \ac{CNN}
 will be able to take in input in the form of new data and its output will best
 represent the probability of that data belonging to each of the trained
-classes. A well performing network will give high output probabilities to the
+classes. 
+A well performing network will give high output probabilities to the
 correct class in most cases. The process of achieving the minimisation of the
 loss function during the training stage is the process whereby the machine is
-"learning"..
-
+\textquotedblleft learning\textquotedblright.
 %
@@
 In this work, we employ a \ac{CNN} of $8$ convolutional layers, $3$ max-pooling
-layers, and $3$ fully connected layers. The exact architecture of the \ac{CNN}
+layers, and $3$ fully connected layers. We also use a technique, known as drop-out, for addressing over-fitting~\cite{srivastava2014dropout}. 
+This terms refers to the way this technique works - 
+by removing units of random choices temporarily in the hidden layers and their associated connections in the \ac{CNN}.
+The exact architecture of the \ac{CNN}
 is shown in Table~\ref{table:architecture} and illustrated in
 Fig.~\ref{fig:CNN}. 
-
 %
@@
 layer respectively. The numbers in the bracket for the fully-connected layers
-are the number used for drop-out~\cm{You haven't discussed drop-out yet. You
-should mention it earlier when you introduce CNNs}.}
+are the number used for drop-out.}
 \end{tablenotes}
@@
 \end{table}
-
 \begin{figure*}
@@
 the first convolutional layer has $11$ filters, each of which is $1$ by $32$ in
-size~\cm{this is the only place that you describe the timeseries being the
-input and what the network does in a single sentence. This text should appear
-in the main bodty of the paper}.~\cm{Also, because I'm very picky about plots
-and images - even though I made the image full page width, the timeseries plots
-are TOO small and the axes are insanely small to read. You seem to have
-strecthed curly bracket symbols to the point that they look super-wierd.}
+size.
 \label{fig:CNN}}
 \end{figure*}
-
 %
@@
 %
+
 The problem we are trying to solve is a problem of multi-class
@@
 %
-where $C$ is the number of the classes and $M$ is the number of the training
-samples~\cm{the loss is computed over batches so here $M$ should be the batch
-size. However, you haven't introduced batches yet, which you need to do when
-you're discussing training}. For the $j^{\text{th}}$ sample and the $i^{th}$
-class, $y_{ij}$ is the correponding class value. It is equal to $1$ for the
+where $C$ is the number of the classes and $M$ is the number of the batch.
+For the $j^{\text{th}}$ sample and the $i^{\text{th}}$ class, $y_{ij}$ is the corresponding class value. It is equal to $1$ for the
 true class and $0$ otherwise.  Similarly, $\hat{y}_{ij}$ is the predicted
-probability from the \ac{CNN} for the $i^{th}$ class and the $j^{\text{th}}$
+probability from the \ac{CNN} for the $i^{\text{th}}$ class and the $j^{\text{th}}$
 sample.
@@
 of these three classes. The training data is used for tuning the weights of
-the neurons in the layers in the \ac{CNN}, while validating data is to verify
-that the \ac{CNN} is learning the features inherent to the data and testing
-data is to test the performance of the trained \ac{CNN}.
+the neurons in the layers in the \ac{CNN}. Validating data is usually applied during training 
+to verify that the \ac{CNN} is learning the features inherent to the data and
+to prevent the \ac{CNN} from over-fitting the training data.
+For a \ac{CNN} that is not over-fitting, the value of the loss function will be close between the validation data and training data.
+Testing data is to test the performance of the trained \ac{CNN} and applied after training has completed.
 
@@
 signals are taken from~\cite{abdikamalov2014measuring,
-dimmelmeier2008gravitational, richers2017equation}. The simulations
+dimmelmeier2008gravitational, richers2017equation}\footnote{\href{https://stellarcollapse.org/ccdiffrot}
+{https://stellarcollapse.org/ccdiffrot}}$^{,}$\footnote{\href{https://zenodo.org/record/201145}{https://zenodo.org/record/201145}}. 
+The simulations
 in~\cite{abdikamalov2014measuring} were focused on the dependence of the
-waveforms on the angular momentum distribution of the progenitors and proivide
+waveforms on the angular momentum distribution of the progenitors and provide
 us with 92 waveforms. In~\cite{dimmelmeier2008gravitational}, 136 waveforms are
@@
 parameter space of $18$ different equations of state and $98$ rotation profiles
-for a progenitor of $12M_{\odot}$ providing a total of $1824$ waveforms. All
+for a progenitor of $12\text{M}_\odot$ providing a total of $1824$ waveforms. All
 the simulations from the studies were based on 2D simulations of supernovae.
+It needs to be pointed out that as the authors in these studies
+were interested in the early stage of post-core bounce, and/or the effects of the equation of states on the \acp{GW} generated at core bounce,
+the simulations were only run for a short amount of time after core bounce. 
+For example, the simulations in~\cite{richers2017equation} were only run for $50$ ms, and only approximately up to $10$ ms after core bounce were used.
 
@@
 yakunin2017gravitational, ott2009gravitational, murphy2009model,
-ott2013general}. The simulations in~\cite{10.1093mnrasstz990,
+ott2013general}\footnote{\href{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/data/Andresen2019/}
+{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/
+data/Andresen2019/ }}$^{,}$\footnote{\href{ https://www.astro.princeton.edu/~burrows/gw.3d/  }
+{ https://www.astro.princeton.edu/~burrows/gw.3d/  }}. The simulations in~\cite{10.1093mnrasstz990,
 kuroda2017correlated, muller2012parametrized, powell2019gravitational,
-radice2019characterizing, yakunin2017gravitational} were from 3D modelling of
+radice2019characterizing, yakunin2017gravitational, ott2013general} were from 3D modelling of
 the supernovae while the simulations in~\cite{yakunin2015gravitational,
-ott2009gravitational, murphy2009model, ott2013general} were 2D. These
+ott2009gravitational, murphy2009model} were 2D. These
 simulations cover a wide range of progenitor masses from $9\text{M}_\odot$ to
 $60\text{M}_\odot$ and the specific progenitor masses of the simulations are
-shown in Table~\ref{table:waveforms}. Examples of the simulated waveforms for
+shown in Table~\ref{table:waveforms}. Examples of the waveforms for
 both mechanisms are shown in Figs.~\ref{fig:magwaveforms} and
@@
 \hline                         
-Abdikamalov\cite{abdikamalov2014measuring} & M   & 12.0                          & 92   \\
-Dimmelmeier\cite{dimmelmeier2008gravitational} & M   & 11.2,15.0,20.0,40.0        & 136  \\
-Richers\cite{richers2017equation}     & M   & 12.0                          & 1824 \\
-Andresen\cite{10.1093mnrasstz990}    & N   & 15.0                          & 6    \\
-Kuroda\cite{kuroda2017correlated}      & N   & 11.2,15.0                    & 2    \\
-Muller\cite{muller2012parametrized}      & N   & 15.0,20.0                    & 6    \\
-Murphy\cite{murphy2009model}      & N   & 12.0,15.0,20.0,40.0        & 16   \\
-Ott$_1$\cite{ott2009gravitational}       & N   & 15.0                          & 2    \\
-Ott$_2$\cite{ott2013general}       & N   & 27.0                          & 8    \\
-Powell\cite{powell2019gravitational}      & N   & 3.5,18.0                      & 2    \\
-Radice\cite{radice2019characterizing}      & N   & 9,10,11,12,13,19,25,60 & 8    \\
-Yakunin$_1$\cite{yakunin2015gravitational}   & N   & 12,15,20,25                & 4    \\
-Yakunin$_2$\cite{yakunin2017gravitational}   & N   & 15                            & 1   \\
+Abdikamalov~\cite{abdikamalov2014measuring} & M   & 12.0                          & 92   \\
+Dimmelmeier~\cite{dimmelmeier2008gravitational} & M   & 11.2,15.0,20.0,40.0        & 136  \\
+Richers~\cite{richers2017equation}     & M   & 12.0                          & 1824 \\
+Andresen~\cite{10.1093mnrasstz990}    & N   & 15.0                          & 6    \\
+Kuroda~\cite{kuroda2017correlated}      & N   & 11.2,15.0                    & 2    \\
+Muller~\cite{muller2012parametrized}      & N   & 15.0,20.0                    & 6    \\
+Murphy~\cite{murphy2009model}      & N   & 12.0,15.0,20.0,40.0        & 16   \\
+Ott$_1$~\cite{ott2009gravitational}       & N   & 15.0                          & 2    \\
+Ott$_2$~\cite{ott2013general}       & N   & 27.0                          & 8    \\
+Powell~\cite{powell2019gravitational}      & N   & $3.5^{*}$,18.0                      & 2    \\
+Radice~\cite{radice2019characterizing}      & N   & 9,10,11,12,13,19,25,60 & 8    \\
+Yakunin$_1$~\cite{yakunin2015gravitational}   & N   & 12,15,20,25                & 4    \\
+Yakunin$_2$~\cite{yakunin2017gravitational}   & N   & 15                            & 1   \\
 \hline
@@
 magnetorotational mechanism and N for the neutrino-driven mechanism.  Mass
-refers the mass, in units of solar mass, of the progenitors in the simulations.
-No. means the number of waveforms available from the study.} 
+refers to the mass, in units of solar mass, of the progenitors in the simulations.
+No. means the number of waveforms available from the study.
+All masses are the masses of the stars at
+zeros age unless indicated otherwise.\\
+$^*$ Mass of a star in a binary system with an initial helium mass of $3.5\text{M}_\odot$} 
 \end{tablenotes}
@@
 %
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{mag_waveforms.png}
-\caption{Examples of simulated waveforms for which the explosion is modeled by
-the magnetorotational mechanism. The top panel shows a waveform
+\begin{figure*}
+     \begin{center}
+        \subfigure[]{
+            \label{fig:magsample1}
+            \includegraphics[width=0.315\textwidth]{abd_wave.png}%
+        }\quad
+        \subfigure[]{
+            \label{fig:magsample2}
+            \includegraphics[width=0.315\textwidth]{Dim_wave.png}%
+        }\quad
+        \subfigure[]{
+            \label{fig:magsample3}
+            \includegraphics[width=0.315\textwidth]{richer_wave.png}%
+        }
+    \end{center}
+    \caption{Examples of simulated waveforms for which the explosion is modelled by
+the magnetorotational mechanism. The left panel shows a waveform
 from~\cite{abdikamalov2014measuring}. The progenitor is $12\text{M}_\odot$ with
-differential rotation parameter $A=300\text{km}$. The initial angular velocity
-at the core $\Omega_c$ is $8.5\text{rads/s}$. The middle panel shows a waveform
+differential rotation parameter $A=10^4~\text{km}$. The initial angular velocity
+at the core $\Omega_c$ is $5.0~\text{rads/s}$. The middle panel shows a waveform
 from~\cite{dimmelmeier2008gravitational}. The simulation corresponds to a
-progenitor of $15\text{M}_\odot$ with $A=50$km and $\Omega_c =
-1.91\text{rads/s}$.  The lower panel shows a waveform
+progenitor of $15\text{M}_\odot$ with $A=10^5$ km and $\Omega_c =
+4.56~\text{rads/s}$.  The right panel shows a waveform
 from~\cite{richers2017equation} where the progenitor is $12\text{M}_\odot$, $A$
-and $\Omega_c$ are $10000$km and $0.5\text{rad/s}$ respectively. In all panels,
+and $\Omega_c$ are $10^4$ km and $3.0~\text{rad/s}$ respectively. In all panels,
 only the $h_{+}$ polarisations are shown because the simulations are
 axis-symmetric or 2D, and therefore described by only one polarisation.  The
-sources are assumed to be at a distance of $10$ kpc. The time is not related to
-the time at core bounce~\cm{then what is the time in reference to? Also, these
-plots are too small and squashed. The text is certainly too small to be
-readable and they should all have equal y and x-axis scales for comparison.}.
-\label{fig:magwaveforms}} 
-\end{figure}
-
+sources are assumed to be at a distance of $10$ kpc. The x-axes show the time after 
+core bounce.\label{fig:magwaveforms}} 
+\end{figure*}
 %
@@
 %
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{neu_waveforms.png}
+\begin{figure*}
+     \begin{center}
+        \subfigure[]{
+            \label{fig:neusample1}
+            \includegraphics[width=0.315\textwidth]{and_wave.png}%
+        }\quad
+        \subfigure[]{
+            \label{fig:neusample2}
+            \includegraphics[width=0.315\textwidth]{Radice_wave.png}%
+        }\quad
+        \subfigure[]{
+            \label{fig:neusample3}
+            \includegraphics[width=0.315\textwidth]{Yak_wave.png}%
+        }
+    \end{center}
     \caption{Examples of simulated waveforms for which the explosion mechanism is
-modeled by the neutrino-driven mechanism. From the top to the bottom, the
-panels show waveforms from~\cite{10.1093mnrasstz990, murphy2009model,
-radice2019characterizing}, with progenitors of masses equal to
+modelled by the neutrino-driven mechanism. From the left to the right, the
+panels show waveforms from~\cite{10.1093mnrasstz990, 
+radice2019characterizing, yakunin2017gravitational}, with progenitors of masses equal to
 $15\text{M}_\odot$, $15\text{M}_\odot$ and $60\text{M}_\odot$ respectively.
-The sources are assumed to be at $10$ kpc from earth. The time is not related
-to the time at core bounce.~\cm{then what is the time in reference to? Also, these
-plots are too small and squashed. The text is certainly too small to be
-readable and they should all have equal y and x-axis scales for comparison. Why
-does the x-axis extend to longer than the longest waveform?}
+The sources are assumed to be at $10$ kpc from earth. The x-axes show the time after core bounce.
 \label{fig:neuwaveforms}} 
-\end{figure}
-
+\end{figure*}
 %
@@
 then ensure that the sampling rate are identical for all the waveforms by down
-sampling them to a pre-selected sampling rate (e.g., $4096$Hz~\cm{e.g. means
-for example, is this an example rate or is it THE rate?}). The longest duration
+sampling them to a pre-selected sampling rate of $4096$Hz. The longest duration
 $\tau$ among the waveforms is then identified and each of the remaining
@@
 To balance the difference in the number of waveforms between the two mechanisms
-in the final data set~\cm{what is the final dataset? Is it the training,
-validation or test, or all of them? Please be clearer}, $36$ copies of each neutrino-driven waveform are
-made~\cm{please explain this in more detail, why is this done and how is this
-done. Surely they are not simply exact copies? Does each copy get a different
-noise realisation or different arrival time? This leaves many questions. Do
-you simply make the number of magneto and neutrino wavelforms equal? What about
-the sub categories? Do you still have 8 times as many Ott2 waveforms as
-Yakunin2? If so, why?}. After this procedure, the
-simulated waveforms are then $\bold{S}(t) = \{\bold{s}_{1}(t), \bold{s}_{2}(t),
+in the training, validation and testing data set, $36$ exact copies of each neutrino-driven waveform are
+made. This will make the ratio of the waveforms modelled by the two mechanisms close to 1, 
+while does not change the ratio of the waveforms from different studies modelled by the neutrino-driven mechanism. 
+This means each waveform in the neutrino-driven mechanism will have equal representations in the data set,
+and waveforms from different mechanisms will have equal representation.
+After this procedure, the simulated waveforms are then $\bold{S}(t) = \{\bold{s}_{1}(t), \bold{s}_{2}(t),
 ..., \bold{s}_{m}(t)\}$, where $m$ is the number of the waveforms and
@@
 where $h_q^+(t)$ and $h_q^\times(t)$ are the two polarisations of the waveform
-and $t$ is the time. As mentioned, some of the waveforms used in the work are
+and $t$ is the time. In this work, we assume a 
+fixed GPS time when generating the training/validation/testing data. 
+At this GPS time, the value of $t$ is zero.
+As mentioned, some of the waveforms used in the work are
 generated with the simulations being axisymmetric, in which case the waveforms
 are entirely described by one polarisation $h_q^+(t)$. The corresponding
-$h_q^\times(t)$ for these waveforms are defined as a vector of zeros.~\cm{This
-slightly worries me that classification between models may be artifically
-enhanced by forcing the cross polarisation to be zero. The network might be
-able to easily use this to distinguich between classes when in reality
-waveforms will not show this property. A referee may have the sam concern.}
-
+$h_q^\times(t)$ for these waveforms are defined as a vector of zeros. 
 %
@@
 $40$, $50$, $60$, $80$, $100$, $150$ and $200$ kpc. If for a training
-procedure, the default distance $d_\text{L}$ of a waveform is not $10$ kpc, the
-following relationship is employed to scale the amplitudes of the waveforms,
-
-\begin{equation}\label{eq:sap} 
-\bold{s}^{d_\text{L}}_q(t) =
-\frac{10\text{kpc}\times\bold{s}_q(t)}{d_\text{L}}, 
-\end{equation} 
-%
-where $\bold{s}^{d_\text{L}}_q(t)$ is the waveform for the source at $d_\text{L}$
-from earth.~\cm{this equation and preceeding text is kind of obvious and could
-be said in far less words. You just simply rescale the amplitude by the
-distance since the amplitude is inversely proportional to the distance.}
+procedure, the default distance $d_\text{L}$ of a waveform is not $10$ kpc, the amplitude are rescaled 
+by the distance since the amplitude is inversely proportional to the distance.
 
@@
 \delta)$ in the sky is selected from a uniform distribution on $\alpha$ and a
-uniform distribution on $\sin\delta$. The corresponding antenna patterns
-$\bold{F}(\alpha, \delta, t)$, given by the following equation~\cm{the
-following equation doesn't give you the antenna patterns. It just lists them as
-an array. Do you really need this array format to explain the waveforms? Does
-it help you?},
+uniform distribution on $\sin\delta$. 
+%
+% the time delays
+%
+The relative delays in the arrival times of the signals at each
+detector are a function of the sky location and are also computed and applied
+to the selected waveform. The delay in arrival time between a detector and the
+centre of the earth is given by,
+%
+\begin{equation}\label{eq:tdetector}
+\Delta t = \frac{\bold{n}(\alpha,\delta) \cdot \bold{r}}{c},
+\end{equation}
+%
+where $\bold{n}(\alpha,\delta)$ is the propagation direction of the \ac{GW},
+$c$ is the speed of light, and $\bold{r}$ the location vector of the detector
+relative to the centre of the Earth. The resulting $j^{\text{th}}$ signal $\bold{h}_j(\alpha,
+\delta, t)$ received by the detector network is then described by,
+%
+\begin{equation}\label{eq:ht2}
+ \bold{h}_j(\alpha, \delta, t) = \bold{F}(\alpha, \delta, t) \times
+\bold{s}_q(t+\bold{\Delta t}),
+\end{equation}
+%
+where $\bold{F}(\alpha, \delta, t)$ is a matrix of which the elements are the antenna patterns of each detector in the network,
 %
@@
 %
-is computed, where $f^+(\alpha, \delta, t)$ and $f^{\times}(\alpha, \delta, t)$
+$f^+(\alpha, \delta, t)$ and $f^{\times}(\alpha, \delta, t)$
 are the antenna pattern functions for the two polarizations and $k$ is the
-number of detectors as defined above~\cm{How do you select $t$ and what does it
-represent?}.
-
-%
-% the time delays
-%
-The relative delays in the arrival times of the signals at each
-detector are a function of the sky location and are also computed and applied
-to the selected waveform. The delay in arrival time between a detector and the
-center of the earth is given by,
-%
-\begin{equation}\label{eq:tdetector}
-\Delta t = \frac{\bold{n}(\alpha,\delta) \cdot \bold{r}}{c},
-\end{equation}
-%
-where $\bold{n}(\alpha,\delta)$ is the propagation direction of the \ac{GW},
-$c$ is the speed of light, and $\bold{r}$ the location vector of the detector
-relative to the center of the Earth. The resulting $j$'th signal $\bold{h}_j(\alpha,
-\delta, t)$ received by the detector network is then described by,
-%
-\begin{equation}\label{eq:ht2}
- \bold{h}_j(\alpha, \delta, t) = \bold{F}(\alpha, \delta, t) \times
-\bold{s}_q(t+\bold{\Delta t}),
-\end{equation}
-%
-where the time delays $\Delta t$ are absorbed into the corresponding notations
-and the subscript $j$ is defined in Eq.\ref{eq:cce}~\cm{I changed the equation
-to be more explicit so you don't have to say this previous sentence.}.
-
+number of detectors as defined above. 
 %
@@
 %
-Next, we generate independent Gaussian noise $\bold{N}_j(t) =
-\{\bold{n}_{1j}(t), \bold{n}_{2j}(t), ..., \bold{n}_{kj}(t)\}'$ for each
+Next, we generate independent Gaussian noise $\bold{N}_j(T) =
+\{\bold{n}_{1j}(T), \bold{n}_{2j}(T), ..., \bold{n}_{kj}(T)\}'$ for each
 detector in the network using their respective power spectral
-densities~\cm{give references and name the detector epoch, e.g., advanced
-design, O2, 3rd gen, etc..}. In the above notation, the symbol $'$ indicates
-transpose~\cm{why is the noise transpose and not the signal? Maybe I'll find
-out as I keep reading.}. 
+densities. In the expression, $T$ is the time for the generated noise and should not be confused with the lower case $t$, 
+which is the time for the waveforms.
 %It is worth mentioning that although in reality, noise at \ac{GW} detectors
@@
 %gabbard2018matching}.
-The duration of the generated noise is $1.6$ times longer than
-$\bold{h}_j(\alpha, \delta, t)$~\cm{Don't start off explanations like this. It
-makes the reader think that you are simply declaring something as fact without
-explaining it}. A random number $x$~\cm{what kind of random number? I assume
-uniform but between what limits?} will then be generated determining where in
+To make the simulated data as realistic as possible, 
+we allow the start time of the signal in a data sample to vary.
+To do this,  the duration of the generated noise $T_{\text{max}}$ is $1.6$ times longer than
+that of $\bold{h}_j(\alpha, \delta, t)$. A random number $p$ drawn from 
+a uniform distribution on the range of $[0, P)$ 
+will then be generated, where
+$P = T_{\text{max}}\times 18\% $  and $p$ 
+determines where in
 the generated noise the signal will be placed, as given by,
@@
 \begin{equation}
-\bold{d}_j(\alpha, \delta, t, x)=
+\bold{d}_j(\alpha, \delta, T, p)=
+\\
 \begin{cases}
-\bold{N}_j(t)~~~~~~~~~~~~~~~~~t < x; \\
-\bold{N}_j(t) + \bold{h}_j(\alpha, \delta, t)~x \leq t \leq \tau + x; \\
-\bold{N}_j(t)~~~~~~~~~~~~~~~~~t > \tau + x. \\
+\bold{N}_j(T)~~~~~~~~~~~~~~~~~T < T_{\text{max}} p; \\
+\bold{N}_j(T) + \bold{h}_j(\alpha, \delta, t)~ T_{\text{max}} p \leq T \leq \tau + T_{\text{max}} p; \\
+\bold{N}_j(T)~~~~~~~~~~~~~~~~~T > \tau + T_{\text{max}} p, \\
 \end{cases}
@@
 %
-~\cm{please define $\tau$.} This is to avoid the possibility that the \ac{CNN}
+where $\tau$ is defined in section \ref{sec:spwf}. 
+This will avoid the possibility that the \ac{CNN}
 learns the human artefact instead of common features of the waveforms by having
-the signals always starting at the same place.~\cm{well kind of. The reason you
-randomise is that the start time is an unknown parameter so you simply want the
-network to learn to generalise to deal with that kind of variation. Fixing the
-start time at the stame value each time is indeed a human feature but so is
-fixing the distance and all the other things that you fix.} For each
-time-series of the background noise class, independently simulated Gaussian
-background noise~\cm{you need to make it clear that you are also generating
-this noise from the detector PSDs. You could also just say that the background
-noise class is produced identically but with a zero amplitude signal.} of the
-same duration as that of the other classes are generated for each detector in
-the network. This means a data sample for this class is defined as,
+the signals always starting at the same place.
+For each time-series of the background noise class, independently simulated Gaussian
+background noise  of the
+same duration as that of the other classes are generated using the same power spectrum density 
+for each detector in the network. This means a data sample for this class is defined as,
 %
 \begin{equation}\label{eq:noise}
- \bold{d}_j(t) = \bold{N}_j(t).
+ \bold{d}_j(T) = \bold{N}_j(T).
 \end{equation}
@@
 times.  After that, we generate independent noise realisations for the
-background noise class. The entire data set $\bold{D}$ defined below, has
+background noise class. The entire data set $\bold{D}$ has
 roughly $l = 1.8 \times 10^{5}$ data samples, where each of the 3 classes
@@
 %
-\begin{equation}\label{eq:finaldata}
-\bold{D}(\boldsymbol{\alpha}, \boldsymbol{\delta}, \boldsymbol{\delta_t}, \bold{t}, \bold{x}) =  \left(\begin{array}{c}
-\bold{d}_1(\alpha, \delta, \delta_t, t, x) \\
-\vdots \\
-\bold{d}_o(\alpha, \delta, \delta_t, t, x) \\
-\vdots \\
-\bold{d}_l(t) \\
-\end{array}\right).
-\end{equation}
-%
-In the above equation, the subscript $o$ is the sum of the data samples in
-which there is a \ac{GW} signal in the time series.~\cm{this notation is very
-confusing and not really required. Why do you have to stack the waveforms up
-like this? Having to define things like $o$ and $l$ seems messy.} The final
-step is to whiten $\bold{D}$ using the power spectral densities~\cm{If you are
-going to spend effort explaining how you rescale distances (a very simple
-procedure) then you should definitley describe how you whiten the data}.
-
+%\begin{equation}\label{eq:finaldata}
+%\bold{D}(\boldsymbol{\alpha}, \boldsymbol{\delta}, \boldsymbol{\delta_t}, \bold{t}, \bold{x}) =  \left(\begin{array}{c}
+%\bold{d}_1(\alpha, \delta, \delta_t, t, x) \\
+%\vdots \\
+%\bold{d}_o(\alpha, \delta, \delta_t, t, x) \\
+%\vdots \\
+%\bold{d}_l(t) \\
+%\end{array}\right).
+%\end{equation}
+%
+%In the above equation, the subscript $o$ is the sum of the data samples in
+%which there is a \ac{GW} signal in the time series.~\cm{this notation is very
+%confusing and not really required. Why do you have to stack the waveforms up
+%like this? Having to define things like $o$ and $l$ seems messy.} The final
+%step is to whiten $\bold{D}$ using the power spectral densities. 
 %
@@
 is finished for a dataset generated at a given distance, the above described
-procedure will be repeated for another distance until the training for all
-distances have been carried out for a network~\cm{You need to make it clear
-that you are training different networks (with the same architecture) for each
-distance and not iterativley training the same single network.}. The entire
-procedure is then repeated for another network~\cm{the word network is being
-used to describe the CNN and the IFOs, it might be a bit confusing} of \ac{GW}
-detectors. As mentioned previously~\cm{when was it mentioned previoulsy? give a
-ref to the section.}, the \ac{CNN} will be trained for the two networks of
+procedure will be repeated for another distance with a different \ac{CNN} of 
+the same architecture until the training for all
+distances have been carried out for a \ac{GW} detector network. The entire
+procedure is then repeated for another \ac{GW} detector network. 
+As mentioned in the introduction, the \ac{CNN} will be trained for the two networks of
 \ac{GW} detectors presented in Table~\ref{table:network}. For the remaining of
-the paper, we will use their acronyms to refer to the networks~\cm{what are
-these acronymns, state them here.}.
+the paper, we will use their acronyms to refer to the networks, i.e., HLVK and H+L+VK.
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{datasample.png}
+\includegraphics[width=0.475\textwidth]{datasample.png}
 \caption{A representative example of the simulated time-series used to
 train/validate/test the \ac{CNN}. The blue shows a whitened time-series with a
-signal added to Gaussian noise of unit variance~\cm{if you've whitened it then
-of course the noise is zero mean and unit variance - that's the definition so
-no need to say it twice.}. The red curve shows the same whitened signal free of
-noise.~\cm{what waveform is this and what is it's SNR? Please state this in the
-caption. Is this a representative SNR that you can detect? If not then why show
-it.}\label{fig:sample}} 
+signal added to Gaussian noise generated using the power spectral density of \ac{aLIGO}. 
+The red curve shows the same whitened signal free of
+noise. The original waveform is shown in Fig. \ref{fig:neusample1}.
+The source is at a distance of $10$ kpc from earth.
+\label{fig:sample}} 
 \end{figure}
@@
 \label{table:network}
-\begin{tabular}{ccc}
+\begin{tabular}{lll}
 \toprule
-Network            & Detectors                & Acronym                 \\
+Network            & \multicolumn{1}{c}{Detector}                & Acronym                 \\
 \hline
-\multirow{4}{*}{1} & \ac{aLIGO} H*    & \multirow{4}{*}{HLVK}   \\
-                   & \ac{aLIGO} L* &                         \\
-                   & \ac{AdVirgo}           &                         \\
-                   & KAGRA                    &                         \\
+\multirow{4}{*}{1} & \ac{aLIGO} Hanford~\cite{aasi2015advanced}    & \multirow{4}{*}{HLVK}   \\
+                   & \ac{aLIGO} Livingston &                         \\
+                   & \ac{AdVirgo}~\cite{acernese2014advanced}           &                         \\
+                   & KAGRA~\cite{aso2013interferometer}                    &                         \\
                    \hline
-\multirow{4}{*}{2} & LIGO A+ H          & \multirow{4}{*}{H+L+VK} \\
-                   & LIGO A+ L       &                         \\
+\multirow{4}{*}{2} & LIGO A+ Hanford~\cite{miller2015prospects, LIGOW}          & \multirow{4}{*}{H+L+VK} \\
+                   & LIGO A+ Livingston       &                         \\
                    & \ac{AdVirgo}           &                         \\
@@
 \normalfont{
-\item The networks of detectors used in this work.\\
-* H refers to the detector in Hanford and L the detector in Livingston.~\cm{you
-* have enough space to simply use Hanford and Livingston in the table itslef.
-* You could also have a column for references to the detector papers.}}
+\item The networks of detectors used in this work.}
 \end{tablenotes}
@@
 After the \ac{CNN} is trained, we can estimate its performance using the
-testing samples~\cm{what about the validation samples? These haven't been
-motivated yet.} and the results of which are presented in this section. One of
-the most commonly used and convenient ways to determine the classification
-performance of a \ac{CNN} or equivelent signal detection algorithm is to plot
-the \ac{ROC} curve. A \ac{ROC} shows the performance of a classifying model by
+testing samples and the results of which are presented in this section. 
+By applying the trained network to the testing samples, 
+the \ac{CNN} will output values of statistics to each of the testing samples. 
+Since we have knowledge of the true class associated with the testing samples,
+it is possible to construct the \ac{ROC} curves.
+The \ac{ROC} curve is one of the most commonly used and convenient ways to 
+determine the classification performance of a \ac{CNN} or equivalent signal detection 
+algorithm. A \ac{ROC} shows the performance of a classifying model by
 defining the \ac{TAP} as a function of the \ac{FAP}. Since \ac{ROC} curves are
@@
 correctly identified.  For a given \ac{FAP}, a model with a higher \ac{TAP} is
-considered more capable than a model with a lower \ac{TAP}~\cm{it appears to me
-that you haven't actually defined what your classification statistic is. Can
-you make sure that the reader understands that how you go from the output of
-the final sigmoid layer to making ROC curves. You have to define a detction
-statistic.}.
+considered more capable than a model with a lower \ac{TAP}.
 
@@
 not surprising as the intrinsic amplitudes for magnetorotational signals are
-higher than those of neutrino-driven signals~\cm{maybe a bit more description?
-Maybe give some detection probabilities at standard FAP values in the text?}.
+higher than those of neutrino-driven signals.
 
@@
             \label{fig:ROClog1}
-            \includegraphics[width=0.45\textwidth]{ROC_curves_neutrino.png}%
+            \includegraphics[width=0.475\textwidth]{ROC_curves_neutrino.png}%
         }\quad
@@
             \label{fig:ROClog2}
-            \includegraphics[width=0.45\textwidth]{ROC_curves_mag.png}%
+            \includegraphics[width=0.475\textwidth]{ROC_curves_mag.png}%
         }
@@
 \ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three
-distances, $20$, $60$, and $100$kpc. The left panel shows the results for the
+distances, $20$, $60$, and $100$ kpc. The left panel shows the results for the
 neutrino-driven mechanism, while the panel on the right shows those for the
 magnetorotational mechanism. In both panels, the solid lines are for the
-network H+L+VK, while the dashed lines are for HLVK.~\cm{please make these
-plots square with equal length sides. Also add a diagonal line to indicate the
-worst performance bound. Also make the y-axis scales the same for both plots or
-at least highlight the fact that they are different in the text since it is
-initially misleading. The legends don't need to have both solid and dashed
-lines. Also add sub-labels indicateing that the left is magneto and the right
-is neutrino.}\label{fig:ROClog}} 
+network H+L+VK, while the dashed lines are for HLVK. The black diagonal lines in both plots indicate 
+the worst scenario where a model has zero ability in distinguishing its input.
+\label{fig:ROClog}} 
 \end{figure*}
@@
 For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
-of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the
+of $10\%$, the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the
 networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
-$0.001$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at
+$0.1\%$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at
 the same distance for the two networks respectively.  For sources that are
 located at a slightly further distance of $60$ kpc, both networks achieve a
-\ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $0.1$. Such a range
+\ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $10\%$. Such a range
 includes distances associated with the Large and Small Magellanic Clouds and
-covers the satellite galaxies imbetween~\cite{karachentsev2004catalog,
+covers the satellite galaxies in between~\cite{karachentsev2004catalog,
 belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are close to or
 larger than $60\%$ for H+L+VK for all chosen \acp{FAP} values, and is $73\%$ if
-the \ac{FAP} is $0.1$. Even for sources at $150$ and $200$ kpc, the \acp{TAP}
+the \ac{FAP} is $10\%$. Even for sources at $150$ and $200$ kpc, the \acp{TAP}
 are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with
@@
 a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the
-\ac{FAP} is $0.1$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
+\ac{FAP} is $10\%$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
 signal it is possible to detect and classify it with either of these \ac{GW}
-detcetor networks.
+detector networks.
 
@@
             \label{fig:eff1}
-            \includegraphics[width=0.45\textwidth]{Neutrino_efficiency.png}
+            \includegraphics[width=0.475\textwidth]{Neutrino_efficiency.png}
         }\quad
@@
             \label{fig:eff2}
-            \includegraphics[width=0.45\textwidth]{Magnetarotational_efficiency.png}
+            \includegraphics[width=0.475\textwidth]{Magnetarotational_efficiency.png}
         }
@@
 lines show the results for the network H+L+VK, and the dashed lines for HLVK.
-Three \acp{FAP} values are chosen, blue for \ac{FAP} $=0.1$, green for \ac{FAP}
-$=0.01$, red for \ac{FAP} $=0.001$.\label{fig:eff}}
+Three \acp{FAP} values are chosen, blue for \ac{FAP} $=10\%$, green for \ac{FAP}
+$=1\%$, red for \ac{FAP} $=0.1\%$.\label{fig:eff}}
 \end{figure*}
@@
             \label{fig:ROCfixed1}
-            \includegraphics[width=0.45\textwidth]{ROC_fixed_neutrino.png}
+            \includegraphics[width=0.475\textwidth]{ROC_fixed_neutrino.png}
         }\quad
@@
             \label{fig:ROCfixed2}
-            \includegraphics[width=0.45\textwidth]{ROC_fixed_mag.png}
+            \includegraphics[width=0.475\textwidth]{ROC_fixed_mag.png}
         }
@@
     \caption{Efficiency curves showing the ability of the \ac{CNN} in
-distinguishing input data with a fixed decision threshold $(0.5)$~\cm{what is
-this? Is it defined in the text?}, and their corresponding \acp{FAP}~\cm{and
-TAP?}. The left panel shows the results for the neutrino-driven mechanism, and
+distinguishing input data with a fixed decision threshold $(50\%)$, 
+and their corresponding \acp{FAP} and \ac{TAP}. 
+The left panel shows the results for the neutrino-driven mechanism, and
 the right shows that for the magnetorotational mechanism. In both panels, the
@@
 likely the input belongs to each of the classes, it may be desired to set a
-threshold on which the decision whether the input belong to a class is made.
+threshold probability on which the decision whether the input belong to a class is made.
 For example, an input will be assigned into a certain class if the
-corresponding probability is larger than the pre-selected threshold. In such a
+corresponding probability is larger than the pre-selected threshold probability. In such a
 scenario, the \ac{FAP} and \ac{TAP} would be affected by the choice of the
 threshold. We show such a result in Fig.~\ref{fig:ROCfixed}, where we employed
-a threshold of $0.5$~\cm{I'm a bit confused. You have 3 classes so how exactly
-are you doing this analysis? You mentioned before that you are treating one
-class vs the remainder but when you talk about magneto does that mean that the
-other model is noise AND neutrino. That would be strange.}. For H+L+VK and
-magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. If the distance
+a threshold probability of $50\%$. This value is chosen because for lower values, 
+there could be more than a class with predicted probabilities from the \ac{CNN} 
+larger than the threshold, while higher values could potentially rule out inputs 
+that may otherwise be correctly identified.
+For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. If the distance
 is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.  For the
 largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are
-$43\%$ and $29\%$ respectively~\cm{these numbers don't seem to match the
-plot.}. For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and
+$43\%$ and $29\%$ respectively. 
+For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and
 $80$ kpc respectively.
 %The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
-For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.04$ for
+For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $4\%$ for
 both networks regarding magnetorotational waveforms. For neutrino-driven
@@
 is $55\%$ at $10$ kpc for HLVK.  Both of the networks have \acp{FAP} close to
-or less than $0.2$. It should be noted that the results presented here are
+or less than $20\%$. It should be noted that the results presented in this section are
 averaged over all the data samples in the testing samples. The performance on
@@
 that is only capable of recognising waveforms with which it is familiar may
-prove to be not be entirely applicable. Therefore, we apply our trained
+prove to be not entirely applicable. Therefore, we apply our trained
 \ac{CNN} to waveforms from other studies that were not used during the
@@
 mechanisms are $\text{s}20$ from~\cite{andresen2017gravitational} and
-$\text{SFHx}$ from~\cite{kuroda2016new}. Examples of these waveforms are shown
+$\text{SFHx}$ from~\cite{kuroda2016new}. These waveforms are shown
 in Fig.~\ref{fig:Extratestwaveform}. The test waveforms in this section should
@@
 %
-\begin{figure}
+\begin{figure*}
      \begin{center}
         \subfigure[]{
-            \label{fig:ex_waveform_neu}
-            \includegraphics[width=0.45\textwidth]{ex_waveform_neu.png}
+            \label{fig:ex_waveform_mag1}
+            \includegraphics[width=0.475\textwidth]{sch_waveform_R3.png}
+        }
+        \subfigure[]{
+            \label{fig:ex_waveform_mag2}
+            \includegraphics[width=0.475\textwidth]{sch_waveform_R4.png}
         }\quad
         \subfigure[]{
-            \label{fig:ex_waveform_mag}
-            \includegraphics[width=0.45\textwidth]{ex_waveform_mag.png}
+            \label{fig:ex_waveform_neu1}
+            \includegraphics[width=0.475\textwidth]{Kuroda_2016.png}
+        }
+        \subfigure[]{
+            \label{fig:ex_waveform_neu2}
+            \includegraphics[width=0.475\textwidth]{Andresen_2016.png}
         }
@@
     \caption{The waveforms excluded from the training session of the \ac{CNN}
-and used as an extra test for the performance of the trained \ac{CNN}. From the
-top to the bottom, the waveforms shown are $\text{SFHx}$, $\text{s}20$
-(neutrino-driven mechanism), $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
-(magnetorotational mechanism), respectively. The time in the x-axis is not
-related to core bounce~\cm{again, why state this (same comment as for Fig.
-2}.\label{fig:Extratestwaveform}} 
-\end{figure}
-
+and used as an extra test for the performance of the trained \ac{CNN}. The top 
+panels show the waveforms $\text{R3E1AC}$(left) and $\text{R4E1FC\_L}$(right), 
+modelled by the magnetorotational mechanism.
+The inset plots show the $h_{\times}$ polarisations of the waveform, which are at least one order of magnitude weaker than the 
+$h_{+}$ polarisations.
+The waveforms shown in the bottom panels are $\text{SFHx}$(left) and $\text{s}20$(right), 
+modelled by the neutrino-driven mechanism. 
+Shown in the x-axes are the time after core bounce.\label{fig:Extratestwaveform}} 
+\end{figure*}
 %
@@
             \label{fig:extra_waveform_test_neu}
-            \includegraphics[width=0.45\textwidth]{extra_neu_waveform_test.png}
+            \includegraphics[width=0.475\textwidth]{extra_neu_waveform_test.png}
         }\quad
@@
             \label{fig:extra_waveform_test_mag}
-            \includegraphics[width=0.45\textwidth]{extra_mag_waveform_test.png}
+            \includegraphics[width=0.475\textwidth]{extra_mag_waveform_test.png}
         }
@@
 Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1200$
-injections~\cm{injections is jargon. Use the same terminolgy as used in the
-rest of the paper} for each distance and therefore each class has $\sim 400$
-injections. The performance of the \ac{CNN} on the test waveforms is shown in
+samples for each distance and therefore each class has $400$
+samples. The performance of the \ac{CNN} on the test waveforms is shown in
 Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
-at $50$kpc and a \ac{FAP} of $0.1$, the \ac{CNN} achieves a \ac{TAP} of $87\%$
-with H+L+VK and $59\%$ with HLVK respectively. At $60$kpc, the \acp{TAP} drops
+at $50$ kpc and a \ac{FAP} of $10\%$, the \ac{CNN} achieves a \ac{TAP} of $87\%$
+with H+L+VK and $59\%$ with HLVK respectively. At $60$ kpc, the \acp{TAP} drops
 slightly to $83\%$ and $52\%$ respectively. This indicates that with the
@@
 $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two
-networks if the sources are at $10$kpc and the \ac{FAP} is $0.1$.  The
+networks if the sources are at $10$ kpc and the \ac{FAP} is $10\%$.  The
 efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
@@
 the testing samples. It is possible that individual waveforms may be easier for
-the \ac{CNN} to detect and the results here also indicate that the \ac{CNN} has
-generalised the features of the explosion mechanisms.~\cm{this last statement
-is very vague and needs clarification. What are features? and what does
-generalisation mean in this context?}
-
+the \ac{CNN} to detect. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $1.8\times10^{5}$ samples of simulated time series for each distance at a
-number of distances from $10$kpc to $200$kpc. The data samples for each
+number of distances from $10$ kpc to $200$ kpc. The data samples for each
 class consisted of approximately $4\times10^5$ samples.
@@
 We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
-was $0.1$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
+was $10\%$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
 for magnetorotational signals from sources at $60$ kpc. Using a network of
-H+L+VK, we showed that the \ac{TAP} is imcreased to $91\%$.  Both the Large and
+H+L+VK, we showed that the \ac{TAP} is increased to $91\%$.  Both the Large and
 Small Magellanic Clouds are within this distance. If the distance is extended
@@
 For the neutrino-driven mechanism, the weaker amplitudes of the waveforms
-result in lower \acp{TAP} at the same distances.  For sources at $10$kpc, the
-trained \ac{CNN}, with a \ac{FAP} of $0.1$, achieved a \ac{TAP} of $55\%$ and
+result in lower \acp{TAP} at the same distances.  For sources at $10$ kpc, the
+trained \ac{CNN}, with a \ac{FAP} of $10\%$, achieved a \ac{TAP} of $55\%$ and
 $76\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
@@
 that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at
-$60$kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
+$60$ kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
 For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and
-$70\%$ for the two networks respectively. The results prove the possibility of
+$70\%$ for the two networks respectively. All at \ac{FAP} of $10\%$. 
+The results prove the possibility of
 using a \ac{CNN} as a tool for the detection and classification of \ac{CCSN}
 \ac{GW} signals.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{ACKNOWLEDGEMENTS}
-%
-%
-%
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{ACKNOWLEDGEMENTS}
+We would like to thank Jade Powell and Marek Szczepanczyk for their 
+constructive comments on the paper.
 I.S.H. and C.M. are supported by the Science and Technology Research Council
@@
 \bibliography{main}
+%\input{main.bbl}
 

### 2020-03-25 main.tex
comments incoporated version
revised version of the paper

@@
 advanced VIRGO and KAGRA is likely to detect a magnetorotational core collapse
-supernovae within the Large and Small Magellanic Clouds, or a Galactic event if
-the explosion mechanism is the neutrino-driven mechanism.  By testing the
-convolutional neural network with waveforms not used for training, we show that
-the true alarm probabilities are $52\%$ and $83\%$ at $60$ kpc for waveforms
-$\text{R3E1AC}$ and $\text{R4E1FC\_L}$.  For waveforms $\text{s}20$ and
-$\text{SFHx}$ at $10$ kpc, the true alarm probabilities are $70\%$ and $93\%$
-respectively. All at false alarm probability equal to $10\%$. 
+supernovae out to the Large or even Small Magellanic Clouds. A Galactic event 
+is likely to be detectable with a network of H+L+VK if the explosion mechanism 
+is the neutrino-driven mechanism.  By testing the convolutional neural network 
+with waveforms not used for training, we show that the true alarm probabilities 
+are $50\%$ and $73\%$ at $50$ kpc for waveforms $\text{R3E1AC}$ and 
+$\text{R4E1FC\_L}$ for networks of HLVK and H+L+VK respectively.  
+For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, 
+the true alarm probabilities are $64\%$ for a network of H+L+VK. 
+All at false alarm probability equal to $1\%$. 
 \end{abstract}
@@
 %
-Since 2015 when LIGO made the first direct observation of \acp{GW} from the
-merger of a binary black hole~\cite{abbott2016observation}, there have been
+In 2015, LIGO made the first direct observation of \acp{GW} from the
+merger of a binary black hole~\cite{abbott2016observation} 
+with the detector of \ac{aLIGO}~\cite{aasi2015advanced}.
+Since then and after VIRGO joined the observations 
+with its \ac{AdVirgo} detector~\cite{abbott2016gw151226,
+abbott2017gw170608, abbott2017gw170814}, there have been
 numerous observations of \acp{GW} from similar systems in the subsequent
-observation runs of LIGO and VIRGO~\cite{abbott2016gw151226,
-abbott2017gw170608, abbott2017gw170814}. These discoveries represent a crucial
+observation runs of LIGO and VIRGO. These discoveries represent a crucial
 milestone in \ac{GW} astronomy and have opened up a new window on the universe.
@@
 near future, many more observations of \acp{GW} from similar \ac{CBC} systems
-can be expected as KAGRA starts joint observations with LIGO and
-VIRGO~\cite{aso2013interferometer, somiya2012detector, abbott2018prospects}.
+can be expected as the KAGRA interferometer starts joint observations with LIGO and
+VIRGO~\cite{aso2013interferometer, somiya2012detector, abbott2018prospects, gossan2016observing,
+abbott2016first, abbott2019optically}.
 
@@
 %with core of $10-100 \text{M}_\odot $ prior to collapse 
-\acp{CCSN} are also considered to be potential sources to the second generation
-detectors such as \ac{aLIGO}~\cite{aasi2015advanced},
-\ac{AdVirgo}~\cite{acernese2014advanced} and KAGRA
-interferometers~\cite{aso2013interferometer, gossan2016observing,
-abbott2016first, abbott2019optically}. It is currently not entirely clear to astronomers how such
+\acp{CCSN} are also considered to be potential sources to
+\ac{aLIGO}, \ac{AdVirgo} and KAGRA interferometers. 
+It is currently not entirely clear to astronomers how such
 massive stars become supernovae. The basic theory of the explosion, confirmed
@@
 will ensue and continue until the core reaches nuclear density. The nuclear
-equation of state will then stiffens by the strong nuclear force above the
+equation of state will then stiffens by the strong nuclear force as the core exceeds
 nuclear density and stops the core collapse. The inner core will bounce back
@@
 using an algorithm called back-propagation~\cite{lecun1988theoretical}. The
-outputs of the \ac{CNN} (the probabilities of the inferred classes in our case) are used as an input to the loss-function that is associated with the entire network.  
+outputs of the \ac{CNN} (the probabilities of the inferred classes in our case) 
+are used as an input to the loss-function that is associated with the entire network.  
 The value of the loss function is used to evaluate how well the algorithm models the input data of the \ac{CNN}.
@@
 \item The architecture of the \ac{CNN} used in this work for the purpose of
-distinguishing supernova signals in backgound \ac{GW} detector noise vs detectr
+distinguishing supernova signals in background \ac{GW} detector noise vs detector
 noise alone. In the table, Conv means convolutional layer, Max-pool means
@@
 radice2019characterizing, yakunin2017gravitational, ott2013general} were from 3D modelling of
-the supernovae while the simulations in~\cite{yakunin2015gravitational,
+the supernovae. 
+In particular, the waveforms from~\cite{10.1093mnrasstz990, muller2012parametrized,  ott2013general} assuming an observer both along the equator and at the pole
+are available, 
+the waveforms from~\cite{kuroda2017correlated, powell2019gravitational} are available for an observer at the pole, and the waveforms from~\cite{yakunin2017gravitational,
+radice2019characterizing} for an equatorial observer.
+The simulations in~\cite{yakunin2015gravitational,
 ott2009gravitational, murphy2009model} were 2D.   These
@@
 the magnetorotational mechanism. The left panel shows a waveform 
-from~\cite{abdikamalov2014measuring}. The progenitor is $12\text{M}_\odot$ with
+from~\cite{abdikamalov2014measuring} for an equatorial observer. The progenitor is $12\text{M}_\odot$ with
 differential rotation parameter $A=10^4~\text{km}$. The initial angular velocity
@@
 sources are assumed to be at a distance of $10$ kpc. The x-axes show the time after 
-core bounce.\label{fig:magwaveforms}} 
+core bounce. The waveforms shown in all panels are for an observer in the equatorial plane.\label{fig:magwaveforms}} 
 \end{figure*}
@@
 $15\text{M}_\odot$, $15\text{M}_\odot$ and $60\text{M}_\odot$ respectively.
+For the left and middle panels, the observer is assumed to be along the pole, 
+while an observer along the equator is assumed for the right panel.
 The sources are assumed to be at $10$ kpc from earth. The x-axes show the time after core bounce.
+The waveform shown in the left panel is for a polar observer, while the other panels show that 
+for an equatorial observer.
 \label{fig:neuwaveforms}} 
@@
 background noise class. The entire data set $\bold{D}$ has
-roughly $l = 1.8 \times 10^{5}$ data samples, where each of the 3 classes
-contains approximately $6\times10^{4}$ data samples.
+roughly $l = 3.0 \times 10^{5}$ data samples, where each of the 3 classes
+contains approximately $1.0\times10^{5}$ data samples.
 %
@@
 from all the detectors in the network. The data samples are then split into 3
-groups, with $1\times10^{4}$ samples being randomly selected for validation,
-$10\%$ of the remainder for testing and $90\%$ for training. When the training
-is finished for a dataset generated at a given distance, the above described
+groups, with $1.0\times10^{4}$ samples being randomly selected for validation.
+Of the remainder, $\sim 1.7\times10^{5}$ for training and $\sim 1.2\times10^{5}$ for tesing. 
+The large number of testing samples is chosen so that low values of \ac{FAP} can be obtained 
+(see section \ref{sec:result} and section \ref{sec:unseen}).
+When the training is finished for a dataset generated at a given distance, the above described
 procedure will be repeated for another distance with a different \ac{CNN} of 
@@
 For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
-of $10\%$, the \ac{CNN} achieves a \ac{TAP} of $94\%$ and $82\%$ for the
+of $1\%$, the \ac{CNN} achieves a \ac{TAP} of $87\%$ and $72\%$ for the
 networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
-$0.1\%$, the \ac{CNN} still achieves \acp{TAP} $86\%$ and $68\%$ for sources at
+$0.01\%$, the \ac{CNN} still achieves \acp{TAP} of $75\%$ and $62\%$ for sources at
 the same distance for the two networks respectively.  For sources that are
-located at a slightly further distance of $60$ kpc, both networks achieve a
-\ac{TAP} of close to or larger than $80\%$ at a \ac{FAP} of $10\%$. Such a range
+located at a slightly further distance of $60$ kpc, the networks achieve a
+\ac{TAP} of $82\%$ (H+L+VK) or $60\%$ (HLVK) at a \ac{FAP} of $1\%$. Such a range
 includes distances associated with the Large and Small Magellanic Clouds and
 covers the satellite galaxies in between~\cite{karachentsev2004catalog,
-belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are close to or
-larger than $60\%$ for H+L+VK for all chosen \acp{FAP} values, and is $73\%$ if
-the \ac{FAP} is $10\%$. Even for sources at $150$ and $200$ kpc, the \acp{TAP}
-are $54\%$ and $38\%$ respectively for the same \ac{FAP}, indicating that with
+belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are no less than $50\%$ 
+for H+L+VK for all chosen \acp{FAP} values, and is $61\%$ if
+the \ac{FAP} is $1\%$. These numbers indicate that with
 such a \ac{GW} network, it is possible to detect magnetorotational \ac{CCSN}
-signals out to such a distance. On the other hand, it is more difficult for the
+signals out to such a distance. For sources at $150$ and $200$ kpc, the \acp{TAP}
+drop to $39\%$ and $21\%$ respectively for \ac{FAP} equal to $1\%$.
+On the other hand, it is more difficult for the
 \ac{CNN} to detect and classify the neutrino-driven signals, due to their
-weaker amplitudes. Nonetheless, for sources at $10$ kpc, the \ac{CNN} achieves
-a \ac{TAP} of $76\%$ and $55\%$ for H+L+VK and HLVK respectively if the
-\ac{FAP} is $10\%$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
-signal it is possible to detect and classify it with either of these \ac{GW}
-detector networks.
+weaker amplitudes. For example, for sources at $10$ kpc, the \ac{CNN} achieves
+a \ac{TAP} of $53\%$ and $22\%$ for H+L+VK and HLVK respectively if the
+\ac{FAP} is $1\%$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
+signal it is possible to detect and classify it with a network of H+L+VK.
 
@@
 lines show the results for the network H+L+VK, and the dashed lines for HLVK.
-Three \acp{FAP} values are chosen, blue for \ac{FAP} $=10\%$, green for \ac{FAP}
-$=1\%$, red for \ac{FAP} $=0.1\%$.\label{fig:eff}}
+Three \acp{FAP} values are chosen, blue for \ac{FAP} $=1\%$, green for \ac{FAP}
+$=0.1\%$, red for \ac{FAP} $=0.01\%$.\label{fig:eff}}
 \end{figure*}
@@
 threshold. We show such a result in Fig.~\ref{fig:ROCfixed}, where we employed
-a threshold probability of $50\%$. This value is chosen because for lower values, 
-there could be more than a class with predicted probabilities from the \ac{CNN} 
-larger than the threshold, while higher values could potentially rule out inputs 
-that may otherwise be correctly identified.
-For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $99\%$. If the distance
-is extended to $80$ kpc, the \ac{TAP} is still close to $80\%$.  For the
-largest distances tested in this work, $150$ and $200$ kpc, the \acp{TAP} are
-$43\%$ and $29\%$ respectively. 
-For HLVK, the \ac{TAP} is $98\%$ and $49\%$ for sources at $10$ and
-$80$ kpc respectively.
+a threshold probability of $95\%$. 
+This value is chosen so that low values of \ac{FAP} can be maintained throughout all tested distances
+as illustrated by the right y-axes of the figures.
+%because for lower values, 
+%there could be more than a class with predicted probabilities from the \ac{CNN} 
+%larger than the threshold, while higher values could potentially rule out inputs 
+%that may otherwise be correctly identified.
+For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $97\%$. If the distance
+is extended to $100$ kpc, the \ac{TAP} is still larger than $50\%$. 
+For HLVK, the \ac{TAP} is $95\%$ for sources at $10$ kpc and drops to $54\%$ at
+$60$ kpc.
 %The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
-For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $4\%$ for
+For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.2\%$ for
 both networks regarding magnetorotational waveforms. For neutrino-driven
-signals, we show that H+L+VK has a \acp{TAP} of $66\%$ at $10$ kpc while it
-is $55\%$ at $10$ kpc for HLVK.  Both of the networks have \acp{FAP} close to
-or less than $20\%$. It should be noted that the results presented in this section are
+signals, we show that H+L+VK has a \acp{TAP} of $39\%$ at $10$ kpc while it
+is $6\%$ at $10$ kpc for HLVK with \acp{FAP} $\sim 0.1\%$. It should be noted that the results presented in this section are
 averaged over all the data samples in the testing samples. The performance on
@@
 panels show the waveforms $\text{R3E1AC}$(left) and $\text{R4E1FC\_L}$(right), 
-modelled by the magnetorotational mechanism.
+for a polar observer, modelled by the magnetorotational mechanism. 
 The inset plots show the $h_{\times}$ polarisations of the waveform, which are at least one order of magnitude weaker than the 
 $h_{+}$ polarisations.
-The waveforms shown in the bottom panels are $\text{SFHx}$(left) and $\text{s}20$(right), 
+The waveforms shown in the bottom panels are $\text{SFHx}$(left) and $\text{s}20$(right), for an equatorial observer,
 modelled by the neutrino-driven mechanism. 
@@
 %
-Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1200$
-samples for each distance and therefore each class has $400$
+Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1.2\times10^5$
+samples for each distance and therefore each class has $4\times10^4$
 samples. The performance of the \ac{CNN} on the test waveforms is shown in
 Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
-at $50$ kpc and a \ac{FAP} of $10\%$, the \ac{CNN} achieves a \ac{TAP} of $87\%$
-with H+L+VK and $59\%$ with HLVK respectively. At $60$ kpc, the \acp{TAP} drops
-slightly to $83\%$ and $52\%$ respectively. This indicates that with the
-\ac{CNN}, it is possible to detect these waveforms from sources that are at
-distances consistent with the Large and Small Magellanic Clouds. For waveforms
-$\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and $70\%$ for the two
-networks if the sources are at $10$ kpc and the \ac{FAP} is $10\%$.  The
+at $60$ kpc and a \ac{FAP} of $1\%$, the \ac{CNN} achieves a \ac{TAP} of $73\%$
+with H+L+VK. This indicates that with the
+\ac{CNN} and a network of H+L+VK, it is possible to detect these waveforms from sources that are at
+distances consistent with the Large and Small Magellanic Clouds.
+For HLVK and a distance of $50$ kpc, a \ac{TAP} of $50\%$ is achieved, showing the possibility of detecting these waveforms out to the Large Magellanic Clouds.
+For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $64\%$ and $36\%$ for the two
+networks if the sources are at $10$ kpc and the \ac{FAP} is $1\%$.  The
 efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
@@
 We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
-was $10\%$, once trained, a \ac{CNN} could achieve a \ac{TAP} close to $80\%$
+was $1\%$, once trained, a \ac{CNN} could achieve a \ac{TAP} of $60\%$
 for magnetorotational signals from sources at $60$ kpc. Using a network of
-H+L+VK, we showed that the \ac{TAP} is increased to $91\%$.  Both the Large and
+H+L+VK, we showed that the \ac{TAP} is increased to $82\%$.  Both the Large and
 Small Magellanic Clouds are within this distance. If the distance is extended
-to $150$ or $200$ kpc, a \ac{TAP} of $54\%$ or $38\%$ respectively are still
-achievable for H+L+VK, indicating the small possibility of detections within
+to $150$ or $200$ kpc, a \ac{TAP} of $39\%$ or $21\%$ respectively are still
+achievable for H+L+VK, indicating a small possibility of detections within
 such distances.
@@
 result in lower \acp{TAP} at the same distances.  For sources at $10$ kpc, the
-trained \ac{CNN}, with a \ac{FAP} of $10\%$, achieved a \ac{TAP} of $55\%$ and
-$76\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
-event would likely be detectable.
+trained \ac{CNN}, with a \ac{FAP} of $1\%$, achieved a \ac{TAP} of $22\%$ and
+$53\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
+event would likely be detectable with H+L+VK.
 
@@
 that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at
-$60$ kpc, the \acp{TAP} are $83\%$ and $52\%$ for H+L+VK and HLVK respectively.
-For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $93\%$ and
-$70\%$ for the two networks respectively. All at \ac{FAP} of $10\%$. 
+$60$ kpc, the \acp{TAP} are $73\%$ and $38\%$ for H+L+VK and HLVK respectively.
+For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the \acp{TAP} are $64\%$ and
+$36\%$ for the two networks respectively. All at \ac{FAP} of $1\%$. 
 The results prove the possibility of
@@
 \section{ACKNOWLEDGEMENTS}
-We would like to thank Jade Powell and Marek Szczepanczyk for their 
+We would like to thank Jade Powell, Marek Szczepanczyk and Miguel-Angel Aloy Torás for their 
 constructive comments on the paper.
+We would also like to express our gratitude to the anonymous reviewers for their 
+thorough and constructive comments on the paper.
 I.S.H. and C.M. are supported by the Science and Technology Research Council

### 2020-03-25 Response_to_PRD_reviewers.txt
Response to the reviewers

We would like to express our gratitude to the reviewers for reading 
through the paper thoroughly and their positive and constructive 
comments. Below are our response to the comments.

Report of Referee A 
------------------------------------------------------------------------------
The manuscript aims at the classification of gravitational wave
signals buried in noise through a convolutional neural network that
takes time series data from gravitational wave detectors as input and
works independently. The authors took into account simulated
waveforms, generated at various distances, for which the explosion
mechanism is modelled by the neutrino-driven mechanism and the
magneto-rotational mechanism. After the training of the convolutional
neural network, the authors estimated the performance of the algorithm
by constructing the receiver operator characteristic curves. The
waveforms excluded from the training session of the convolutional
neural network are used as an extra test for the performance of the
trained CNN. The manuscript is well organised and clearly written, it
offers a complete overview of the state of art and it contains a
significant step forward for the classification of supernova
gravitational waves signals.

Response: Thank you so much for the very positive comments. 
          They are much appreciated.
------------------------------------------------------------------------------

Report of Referee B
------------------------------------------------------------------------------
The authors present a novel analysis pipeline (at the heart of which
is a convolutional neural network - CNN) for the detection and
classification of gravitational waves (GWs) from core-collapse
supernovae (CCSNe). Employing said pipeline, the authors suggest GWs
from Galactic CCSNe are likely to be detected with even the current
generation of ground-based GW detectors. If robust, this result would
provide an improvement in sensitivity by a factor of a few over
similar studies using excess-power methods, which is exciting and much
needed.

The particulars of the conditions for which the flagship paper results
are quoted, however, cause concern. A Galactic CCSN is a once in a
lifetime event, and the first "detection" of GWs from stellar collapse
would certainly not be claimed at any less than 5 sigma. As a
consequence, any results presented at FAP=1% or FAP=10% on
detectability seem a little spurious.

Going through the paper and finding the equivalent
"detection/classification distances" at FAP=0.1% (the most realistic
case presented, and a little over 3 sigma):

* [Fig. 5a] At 20kpc, TAP_HLVK ~ 1%, and TAP_H+L+VK ~ 8%

* [Fig. 5b] At 20kpc,   TAP_HLVK ~ 92% / TAP_H+L+VK ~ 95%
                At 60kpc,   TAP_HLVK ~ 55% / TAP_H+L+VK ~ 80%
                At 100kpc, TAP_HLVK ~ 16% / TAP_H+L+VK ~ 16%

* [Fig. 6a] At 10kpc, TAP_HLVK ~ 12% / TAP_H+L+VK ~ 41%

* [Fig. 6b] At 10kpc, TAP_HLVK ~ 96% / TAP_H+L+VK ~ 98%

* [Fig. 9a] At 10kpc, TAP_HLVK ~ 12% / TAP_H+L+VK ~ 41%

* [Fig. 9b] At 10kpc, TAP_HLVK ~ 96% / TAP_H+L+VK ~ 97%

These numbers (and the above commentary) suggest that a different
region of parameter space might be more appropriate to study here.
Assuming TAP>50% and FAP<0.3% as a (generous) lower limit on realistic
detection claims, it would be instructive to instead show:

* [Fig. 5a] TAP_HLVK vs FAP_HLVK and TAP_H+L+VK vs FAP_H+L+VK between
0.001% < FAP < 1% at 0.2kpc (Betelgeuse), 2kpc, and 10kpc (typical
"Galactic SN" distance)

* [Fig. 5b] TAP_HLVK vs FAP_HLVK and TAP_H+L+VK vs FAP_H+L+VK between
0.001% < FAP < 1% at 2kpc, 20kpc, 60kpc

* [Fig. 6a] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 20kpc at FAP=0.1%, 0.01%, and 0.001%

* [Fig. 6b] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 200kpc at FAP=0.1%, 0.01%, and 0.001%

* [Fig. 9a] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 20kpc at FAP=0.1%, 0.01%, and 0.001%

* [Fig. 9b] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 200kpc at FAP=0.1%, 0.01%, and 0.001%

Looking at Fig. 7, however, I question if it is possible to achieve
such low FAPs with this pipeline, particularly for the neutrino
mechanism waveforms. It would be useful to remake this figure at
distances for which FAP << 0.3% is possible. If not possible, it may
be beneficial to remove the figure. If not removed, the caption and
text should be updated to note the large FAPs used.

Response: We have tested again the trained CNN with 1.2^5 test samples 
          for each distance so that we can achieved a FAP of 1%, 0.1% 
          and 0.01%.

          We appreciate that 0.001% is also one of the requested values
          of FAP and running the testing at closer distance for neutrino
          -driven mechanism is advised. 
          But we also noted that such a low value of FAP would 
          require an even larger set of test samples and a much longer 
          amount of time to generate, which maybe too computationally 
          expensive for us to do. Rerunning the simulations at closer
          distances will even be more computationally expensive.

          The changes in response to this comment includes: 
          1. Only TAP values at FAP equal to 1% are qouted in the      
             abstract and the conclusion. No detection claim is made for 
             FAP higher than 1%. 
             We understand that detection claims are advised to be made 
             at least FAP = 0.1%, but we argue that detections of CCSNe 
             signals will be made simultaneously with electromagnetic 
             observations and/or neutrino observations, and therefore 
             such low FAP may not be absolutely necessary.

          2. The plots and text in the section of results 
             (section IV and section V).

          3. We retracted claims regarding the ability of the 
             network HLVK in detecting Galactic events where the explosion 
             mechanism is neutrino-driven mechanism.

          4. number of training/test samples in the last paragraph of 
             section III has been updated to be consistent with 
             this change.

          5. We would also like to highlight the fact that the plots
             previously submitted as Fig. 9a and Fig. 9b were actually 
             duplicates of previous Fig. 6a and Fig. 6b by accident. 
             Although this mistake was naturaly corrected when we updated
             the results, we would still like to bring this mistake to the
             reviewers' attention.

Overall, the study is a novel and interesting work. It is crucial,
however, to put the authors' pipeline through more rigorous testing
(i.e. at realistic FAPs, perhaps using realistic noise) before stating
its ability to detect GWs from Galactic CCSNe. I would suggest framing
instead the paper as a follow-up pipeline, but take note that the
authors explicitly distinguish their pipeline from that shown in a
similar work by Astone+2018 as designed to take time series directly
from the detectors and find signals, rather than analyzing triggers
found by some external detection pipeline. Given this, it seems
appropriate for appreciable corrections to the text and results to be
requested.

Response: We appreciate this comment and admit that testing/training 
          the CNN using realistic noise would indeed show a more 
          realistic results.
          However, such extension of the current work would require 
          a whole new set of treatment that is beyond the current scope
          of this work. 
          We therefore updated our results with more realistic 
          values of FAP and leave tests using realistic noise for future 
          work.

In the below, I list specific comments by section, denoting the
relevant paragraph number by p.

I: Introduction

p1: LIGO, Virgo, and KAGRA are not introduced or cited here. Suggest
to move discussion of second generation detectors (and references)
from start of p2 here. Aside - has KAGRA now begun operations? If so,
it may be worth updating the text here.

Response: We have updated the text accordingly.

p2: Specifically, the sentence "The nuclear equation of state will
then stiffens by the strong nuclear force above the nuclear density
and stops the core collapse." doesn't really make sense. The equation
of state stiffens (and subsequently stops the core collapsing) as the
core density exceeds nuclear density because the strong nuclear force
becomes repulsive at very small inter-nucleon distances.

Response: Thanks for pointing this out. We have rewritten the sentense 
          to read "The nuclear equation of state will then stiffens by 
          the strong nuclear force as the core exceeds nuclear density
          and stops the core collapse."

II: Convolutional Neural Network & Fig. 1 The technical description of
the CNN pipeline is thorough and instructive - nice work!

Response: Thank you so much.

Tab. 1 caption: typo at end of first sentence, detectr --> detector

Response: This has been corrected.

III: Data

p3: For the 3D simulations, what is the observer angle for the h+,hx
used? As the GW signal for CCSNe varies with orientation of the source
with respect to the observer, it may be useful to add a distribution
of observer angles for each waveform model to the training set, so as
to account for this variance. This could also help remedy the issue
noted in p6 of small sample size of neutrino mechanism waveforms
compared to magnetorotational mechanism waveforms.

Response: the observer angles for all the studies of 3D simulations have
          been added to the text. We appreciate that our data could be 
          augmented by varying the observer angles in the data set. 
          However, we noted that while some of the used studies published 
          the information or parameters to generate waveforms at random 
          observer angles, the same information for other studies is not
          readily available. We therefore decided to use only the published
          waveforms.

Fig. 2 & Fig. 3: What are the observer angles for these waveforms? As
an aside, it could be useful to combine these plots into a 4 panel
figure.

Response: the observer angles for these figures have been added in 
          the caption.

Note: Appreciated the technical detail included on signal injection
methodology - very refreshing to see, and crucial for reproducibility.

Response: Thank you so much.

IV: Results and Discussion

I suggest the results are rerun using the parameters highlighted
above, and the text subsequently rewritten to reflect the updated
results. At the very least, statements on detecting GWs from a
Galactic CCSN should be removed (unless results with FAP < 0.3% show
this is the case), and a clear note/disclaimer on the high FAPs used
must be added.

Note: Figs. 5 and 6 are clear and well presented - very instructive.

Response: As stated above, we have updated section IV and section V.

V: Waveforms Excluded From Training

As for the results section, I suggest reruns using parameters
highlighted above, and the text subsequently rewritten to reflect the
updated results. Similarly to before, at the very least a disclaimer
on the FAPs must be added, and detection statements for FAP>0.3%
removed.

Response: As stated above, we tested again the trained CNN with 
          1.2 * 10^5 test samples to achieve FAP values of 1%, 0.1%, 
          0.01% as was done for section IV. The text and plots 
          are also updated to reflect this change. 
          Claims regarding the ability of the network HLVK in detecting 
          Galatic CCSN signals if the explosion mechanism is the 
          neutrino driven mechanism.

Fig. 8: As for Figs. 2 and 3, what are the observer angles for these
waveforms. As it is noted that h+ >> hx in the caption, I suspect the
waveform is for a polar observer, but this should be confirmed and
noted in the text.

Response: The waveforms shown in Fig. 8a and Fig. 8b are indeed for a 
          polar observer. This as well as that for Fig. 8c and Fig. 8d
          have been added in the caption.

VI: Conclusion

As previously noted, only results at FAP=10% are mentioned. As it is
not realistic to claim detection at such high FAP, the distances
presented are meaningless. This should be rewritten, pointing instead
to the results at FAP=0.1%. If Galactic/Magellanic Cloud detections
are no longer feasible, the abstract (and other relevant sections)
should be rewritten to reflect that.

Response: We updated the text to be consistent with the uses of more realistic 
          FAP and retracted claims of detection of Galactic event with HLVK.
------------------------------------------------------------------------------

### 2020-04-17 Response_to_PRD_reviewers.txt
comments incorporated, samples increased to 1.08e6

@@
 
-Response: We have tested again the trained CNN with 1.2^5 test samples 
-          for each distance so that we can achieved a FAP of 1%, 0.1% 
-          and 0.01%.
+Response: We have tested again the trained CNN with 1.08^6 test samples 
+          for each distance so that we can achieved a FAP of 0.1%, 0.01% 
+          and 0.001%.
 
-          We appreciate that 0.001% is also one of the requested values
-          of FAP and running the testing at closer distance for neutrino
-          -driven mechanism is advised. 
-          But we also noted that such a low value of FAP would 
-          require an even larger set of test samples and a much longer 
-          amount of time to generate, which maybe too computationally 
-          expensive for us to do. Rerunning the simulations at closer
-          distances will even be more computationally expensive.
+          We appreciate that re-running the simulations at closer
+          distances is advised, but doing so would be very 
+          computationally expensive.
 
           The changes in response to this comment includes: 
-          1. Only TAP values at FAP equal to 1% are qouted in the      
+          1. The plots in the section of results 
+             (section IV and section V) have been updated.
+             The text in these two sections are rewritten.
+
+          2. Only TAP values at FAP equal to 0.1% are qouted in the      
              abstract and the conclusion. No detection claim is made for 
-             FAP higher than 1%. 
-             We understand that detection claims are advised to be made 
-             at least FAP = 0.1%, but we argue that detections of CCSNe 
-             signals will be made simultaneously with electromagnetic 
-             observations and/or neutrino observations, and therefore 
-             such low FAP may not be absolutely necessary.
-
-          2. The plots and text in the section of results 
-             (section IV and section V).
+             FAP higher than 0.1%. The text in the abstract and the 
+             conclusion has also been modified to accommodate the changes.
 
           3. We retracted claims regarding the ability of the 
-             network HLVK in detecting Galactic events where the explosion 
-             mechanism is neutrino-driven mechanism.
+             networks in detecting Galactic events where the explosion 
+             mechanism is the neutrino-driven mechanism.
 
@@
           However, such extension of the current work would require 
-          a whole new set of treatment that is beyond the current scope
+          a whole new set of treatments that is beyond the current scope
           of this work. 
@@
 Response: As stated above, we tested again the trained CNN with 
-          1.2 * 10^5 test samples to achieve FAP values of 1%, 0.1%, 
-          0.01% as was done for section IV. The text and plots 
+          1.08 * 10^6 test samples to achieve FAP values of 0.1%, 0.01%, 
+          0.001% as was done for section IV. The text and plots 
           are also updated to reflect this change. 
-          Claims regarding the ability of the network HLVK in detecting 
+          Claims regarding the ability of the networks in detecting 
           Galatic CCSN signals if the explosion mechanism is the 
-          neutrino driven mechanism.
+          neutrino driven mechanism are withdrawn.
 

### 2020-04-17 main.tex
comments incorporated, samples increased to 1.08e6

@@
 advanced VIRGO and KAGRA is likely to detect a magnetorotational core collapse
-supernovae out to the Large or even Small Magellanic Clouds. A Galactic event 
-is likely to be detectable with a network of H+L+VK if the explosion mechanism 
-is the neutrino-driven mechanism.  By testing the convolutional neural network 
-with waveforms not used for training, we show that the true alarm probabilities 
-are $50\%$ and $73\%$ at $50$ kpc for waveforms $\text{R3E1AC}$ and 
-$\text{R4E1FC\_L}$ for networks of HLVK and H+L+VK respectively.  
+supernovae out to the Large or even Small Magellanic Clouds. 
+%A Galactic event is likely to be detectable with a network of H+L+VK 
+%if the explosion mechanism is the neutrino-driven mechanism.  
+By testing the convolutional neural network 
+with waveforms not used for training, we show that the true alarm probability
+is $66\%$ at $60$ kpc for waveforms $\text{R3E1AC}$ and 
+$\text{R4E1FC\_L}$ for networks of H+L+VK.  
 For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, 
-the true alarm probabilities are $64\%$ for a network of H+L+VK. 
-All at false alarm probability equal to $1\%$. 
+the true alarm probabilities are $49\%$ and $20\%$ for a network of H+L+VK 
+and HLVK respectively. 
+All at false alarm probability equal to $0.1\%$. 
 \end{abstract}
@@
 the magnetorotational mechanism. The left panel shows a waveform 
-from~\cite{abdikamalov2014measuring} for an equatorial observer. The progenitor is $12\text{M}_\odot$ with
+from~\cite{abdikamalov2014measuring}. The progenitor is $12\text{M}_\odot$ with
 differential rotation parameter $A=10^4~\text{km}$. The initial angular velocity
@@
 only the $h_{+}$ polarisations are shown because the simulations are
-axis-symmetric or 2D, and therefore described by only one polarisation.  The
-sources are assumed to be at a distance of $10$ kpc. The x-axes show the time after 
-core bounce. The waveforms shown in all panels are for an observer in the equatorial plane.\label{fig:magwaveforms}} 
+axis-symmetric or 2D, and therefore described by only one polarisation. 
+The waveforms shown in all panels are for an observer in the equatorial plane.
+The sources are assumed to be at a distance of $10$ kpc. The x-axes show the time after 
+core bounce.\label{fig:magwaveforms}} 
 \end{figure*}
@@
 $15\text{M}_\odot$, $15\text{M}_\odot$ and $60\text{M}_\odot$ respectively.
-For the left and middle panels, the observer is assumed to be along the pole, 
-while an observer along the equator is assumed for the right panel.
+The waveform shown in the left panel is for a polar observer, while the waveforms in the other panels are 
+for an equatorial observer.
 The sources are assumed to be at $10$ kpc from earth. The x-axes show the time after core bounce.
-The waveform shown in the left panel is for a polar observer, while the other panels show that 
-for an equatorial observer.
 \label{fig:neuwaveforms}} 
@@
 background noise class. The entire data set $\bold{D}$ has
-roughly $l = 3.0 \times 10^{5}$ data samples, where each of the 3 classes
-contains approximately $1.0\times10^{5}$ data samples.
+roughly $l = 1.26 \times 10^{6}$ data samples, where each of the 3 classes
+contains approximately $4.2\times10^{5}$ data samples.
 %
@@
 groups, with $1.0\times10^{4}$ samples being randomly selected for validation.
-Of the remainder, $\sim 1.7\times10^{5}$ for training and $\sim 1.2\times10^{5}$ for tesing. 
+Of the remainder, $1.70\times10^{5}$ for training and $1.08\times10^{6}$ for tesing. 
 The large number of testing samples is chosen so that low values of \ac{FAP} can be obtained 
@@
 The red curve shows the same whitened signal free of
-noise. The original waveform is shown in Fig. \ref{fig:neusample1}.
+noise. The optimal signal to noise ratio for this signal is $5.5$.
+The original waveform is shown in Fig. \ref{fig:neusample1}.
 The source is at a distance of $10$ kpc from earth.
@@
 magnetorotational mechanism. In both panels, the solid lines are for the
-network H+L+VK, while the dashed lines are for HLVK. The black diagonal lines in both plots indicate 
+network H+L+VK, while the dashed lines are for HLVK. The black lines in both plots indicate 
 the worst scenario where a model has zero ability in distinguishing its input.
@@
 For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
-of $1\%$, the \ac{CNN} achieves a \ac{TAP} of $87\%$ and $72\%$ for the
+of $0.1\%$, the \ac{CNN} achieves a \ac{TAP} of $82\%$ and $66\%$ for the
 networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
-$0.01\%$, the \ac{CNN} still achieves \acp{TAP} of $75\%$ and $62\%$ for sources at
+$0.001\%$, the \ac{CNN} still achieves \acp{TAP} of $72\%$ and $55\%$ for sources at
 the same distance for the two networks respectively.  For sources that are
 located at a slightly further distance of $60$ kpc, the networks achieve a
-\ac{TAP} of $82\%$ (H+L+VK) or $60\%$ (HLVK) at a \ac{FAP} of $1\%$. Such a range
+\ac{TAP} of $77\%$ (H+L+VK) or $54\%$ (HLVK) at a \ac{FAP} of $0.1\%$. Such a range
 includes distances associated with the Large and Small Magellanic Clouds and
 covers the satellite galaxies in between~\cite{karachentsev2004catalog,
-belokurov2007cats}.  For sources at $100$ kpc, the \acp{TAP} are no less than $50\%$ 
-for H+L+VK for all chosen \acp{FAP} values, and is $61\%$ if
-the \ac{FAP} is $1\%$. These numbers indicate that with
+belokurov2007cats}.  For sources at $80$ kpc, the \acp{TAP} are no less than $50\%$ 
+for H+L+VK for all chosen \acp{FAP} values, and is $66\%$ if
+the \ac{FAP} is $0.1\%$. These numbers indicate that with
 such a \ac{GW} network, it is possible to detect magnetorotational \ac{CCSN}
-signals out to such a distance. For sources at $150$ and $200$ kpc, the \acp{TAP}
-drop to $39\%$ and $21\%$ respectively for \ac{FAP} equal to $1\%$.
+signals out to such a distance. For sources at $100$, $150$ and $200$ kpc, the \acp{TAP}
+drop to $55\%$, $33\%$ and $16\%$ respectively for \ac{FAP} equal to $0.1\%$.
 On the other hand, it is more difficult for the
@@
 weaker amplitudes. For example, for sources at $10$ kpc, the \ac{CNN} achieves
-a \ac{TAP} of $53\%$ and $22\%$ for H+L+VK and HLVK respectively if the
-\ac{FAP} is $1\%$.  This means that for a \ac{GW} from a Galactic \ac{CCSN}
-signal it is possible to detect and classify it with a network of H+L+VK.
+a \ac{TAP} of $38\%$ and $10\%$ for H+L+VK and HLVK respectively if the
+\ac{FAP} is $0.1\%$. In Fig.~\ref{fig:eff}, only the values of \ac{TAP} that
+are larger than zero will be plotted.
 
@@
 threshold. We show such a result in Fig.~\ref{fig:ROCfixed}, where we employed
-a threshold probability of $95\%$. 
+a threshold probability of $90\%$. 
 This value is chosen so that low values of \ac{FAP} can be maintained throughout all tested distances
@@
 %that may otherwise be correctly identified.
-For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $97\%$. If the distance
-is extended to $100$ kpc, the \ac{TAP} is still larger than $50\%$. 
-For HLVK, the \ac{TAP} is $95\%$ for sources at $10$ kpc and drops to $54\%$ at
+For H+L+VK and magnetorotational signals at $10$ kpc, the \ac{TAP} is $98\%$. 
+If the distance is extended to $100$ kpc, the \ac{TAP} is still larger than $50\%$. 
+For HLVK, the \ac{TAP} is $96\%$ for sources at $10$ kpc and drops to $56\%$ at
 $60$ kpc.
 %The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
-For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.2\%$ for
+For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.3\%$ for
 both networks regarding magnetorotational waveforms. For neutrino-driven
-signals, we show that H+L+VK has a \acp{TAP} of $39\%$ at $10$ kpc while it
-is $6\%$ at $10$ kpc for HLVK with \acp{FAP} $\sim 0.1\%$. It should be noted that the results presented in this section are
+signals, we show that H+L+VK has a \acp{TAP} of $44\%$ at $10$ kpc while it
+is $11\%$ at $10$ kpc for HLVK with \acp{FAP} $< 0.3\%$.
+As we have chosen a large value of threshold, the values of \ac{TAP} decreases rapidly 
+as the distance increases. Again, only the values of \ac{TAP} larger than zero will be plotted.
+
+It should be noted that the results presented in this section are
 averaged over all the data samples in the testing samples. The performance on
@@
 of the waveform. 
-
+In addition, if an accurate time window and/or localisation of en event are available
+(e.g. with electromagnetic and/or neutrino observations), 
+such low values of \ac{FAP} may not be necessary. 
 %Also shown in this figure is a curve showing the \ac{TAP} for all the classes, defined by,
@@
 $h_{+}$ polarisations.
-The waveforms shown in the bottom panels are $\text{SFHx}$(left) and $\text{s}20$(right), for an equatorial observer,
+The waveforms shown in the bottom panels are $\text{SFHx}$(left, for an polar observer) and $\text{s}20$(right, for an equatorial observer),
 modelled by the neutrino-driven mechanism. 
@@
 %
-Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1.2\times10^5$
-samples for each distance and therefore each class has $4\times10^4$
+Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1.08\times10^6$
+samples for each distance and therefore each class has $3.6\times10^5$
 samples. The performance of the \ac{CNN} on the test waveforms is shown in
 Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
-at $60$ kpc and a \ac{FAP} of $1\%$, the \ac{CNN} achieves a \ac{TAP} of $73\%$
+at $60$ kpc and a \ac{FAP} of $0.1\%$, the \ac{CNN} achieves a \ac{TAP} of $66\%$
 with H+L+VK. This indicates that with the
@@
 distances consistent with the Large and Small Magellanic Clouds.
-For HLVK and a distance of $50$ kpc, a \ac{TAP} of $50\%$ is achieved, showing the possibility of detecting these waveforms out to the Large Magellanic Clouds.
-For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $64\%$ and $36\%$ for the two
-networks if the sources are at $10$ kpc and the \ac{FAP} is $1\%$.  The
+For HLVK and a distance of $40$ kpc, a \ac{TAP} of $54\%$ is achieved, showing the possibility of detecting 
+these waveforms out to the satellite galaxies within such a distance.
+For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $49\%$ and $20\%$ for the two
+networks if the sources are at $10$ kpc and the \ac{FAP} is $0.1\%$.  The
 efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
@@
 distinguishing \ac{GW} detector time-series among pure background noise and
-\ac{CCSN} explosion mechanisms. We have trained the \ac{CNN} using
-$1.8\times10^{5}$ samples of simulated time series for each distance at a
+\ac{CCSN} explosion mechanisms. We have trained, valided, and tested 
+the \ac{CNN} using $1.26\times10^{6}$ samples of simulated time series for each distance at a
 number of distances from $10$ kpc to $200$ kpc. The data samples for each
-class consisted of approximately $4\times10^5$ samples.
+class consisted of approximately $4.2\times10^5$ samples.
 
@@
 We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
-was $1\%$, once trained, a \ac{CNN} could achieve a \ac{TAP} of $60\%$
+was $0.1\%$, once trained, a \ac{CNN} could achieve a \ac{TAP} of $54\%$
 for magnetorotational signals from sources at $60$ kpc. Using a network of
-H+L+VK, we showed that the \ac{TAP} is increased to $82\%$.  Both the Large and
+H+L+VK, we showed that the \ac{TAP} is $77\%$.  Both the Large and
 Small Magellanic Clouds are within this distance. If the distance is extended
-to $150$ or $200$ kpc, a \ac{TAP} of $39\%$ or $21\%$ respectively are still
+to $150$ or $200$ kpc, a \ac{TAP} of $33\%$ or $16\%$ respectively are still
 achievable for H+L+VK, indicating a small possibility of detections within
 such distances. 
-
 %
@@
 result in lower \acp{TAP} at the same distances.  For sources at $10$ kpc, the
-trained \ac{CNN}, with a \ac{FAP} of $1\%$, achieved a \ac{TAP} of $22\%$ and
-$53\%$ for HLVK and H+L+VK respectively. This indicates a Galactic \ac{CCSN}
-event would likely be detectable with H+L+VK.
-
+trained \ac{CNN}, with a \ac{FAP} of $0.1\%$, achieved a \ac{TAP} of $10\%$ and
+$38\%$ for HLVK and H+L+VK respectively. 
 %
@@
 %
+
 We used four waveforms that were not used for the training of the \ac{CNN} to
@@
 that for waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$ from sources at
-$60$ kpc, the \acp{TAP} are $73\%$ and $38\%$ for H+L+VK and HLVK respectively.
-For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the \acp{TAP} are $64\%$ and
-$36\%$ for the two networks respectively. All at \ac{FAP} of $1\%$. 
+$60$ kpc, the \ac{TAP} is $66\%$ for H+L+VK.
+For HLVK and sources at $40$ kpc, the \ac{TAP} is $54\%$.
+For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the \acp{TAP} are $49\%$ and
+$20\%$ for the two networks respectively. All at \ac{FAP} of $0.1\%$. 
 The results prove the possibility of

### 2020-04-17 main.tex
comments incorporated, samples increased to 1.08e6

@@
 panel shows the results for the neutrino-driven mechanism, while the right
-shows those for the magnetorotational mechanism. In both panels, the solid
+shows those for the magnetorotational mechanism. 
+At a certain value of \ac{FAP} and a distance, the value of \ac{TAP}
+will be plotted only if it is not zero.
+In both panels, the solid
 lines show the results for the network H+L+VK, and the dashed lines for HLVK.
@@
     \end{center}
-    \caption{Efficiency curves showing the ability of the \ac{CNN} in
-distinguishing input data with a fixed decision threshold $(50\%)$, 
-and their corresponding \acp{FAP} and \ac{TAP}. 
-The left panel shows the results for the neutrino-driven mechanism, and
-the right shows that for the magnetorotational mechanism. In both panels, the
-solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the
+    \caption{The ability of the \ac{CNN} in
+distinguishing input data with a fixed decision threshold $(90\%)$, 
+and their corresponding \acp{FAP} and \acp{TAP}. 
+The left panel shows the results for the neutrino-driven mechanism.
+Since for the neutrino-driven mechanism, the value of \ac{TAP} decreases to zero rapidly
+as distance increases, only the distances at which the corresponding \acp{TAP} are not zero are plotted.
+In the plot, stars are for the network H+L+VK, and the dots are for the network HLVK.
+The right panel shows the results for the magnetorotational mechanism. 
+In the right panel, the solid lines show the \acp{TAP} and \acp{FAP} 
+for the network H+L+VK, and the
 dashed lines show those for HLVK.\label{fig:ROCfixed}}

### 2020-04-28 Response_to_PRD_reviewers.txt
Fixed minor typos in the referee response

@@
           The changes in response to this comment includes: 
-          1. The plots in the section of results 
-             (section IV and section V) have been updated.
-             The text in these two sections are rewritten.
+          1. The plots in the section of results (section IV and section V) 
+             have been updated.  The text in these two sections have been 
+             modified to reflect these updated results.
 
-          2. Only TAP values at FAP equal to 0.1% are qouted in the      
+          2. Only TAP values at FAP equal to 0.1% are quoted in the      
              abstract and the conclusion. No detection claim is made for 
@@
 
-          4. number of training/test samples in the last paragraph of 
+          4. The number of training/test samples in the last paragraph of 
              section III has been updated to be consistent with 
@@
              duplicates of previous Fig. 6a and Fig. 6b by accident. 
-             Although this mistake was naturaly corrected when we updated
+             Although this mistake was naturally corrected when we updated
              the results, we would still like to bring this mistake to the
@@
           realistic results.
-          However, such extension of the current work would require 
-          a whole new set of treatments that is beyond the current scope
+          However, such an extension of the current work would require 
+          a whole new set of treatments that we feel is beyond the current scope
           of this work. 
-          We therefore updated our results with more realistic 
+          We have therefore updated our results with more realistic 
           values of FAP and leave tests using realistic noise for future 
@@
 
-In the below, I list specific comments by section, denoting the
+Below we list specific comments by section, denoting the
 relevant paragraph number by p.
@@
 
-Response: Thanks for pointing this out. We have rewritten the sentense 
+Response: Thanks for pointing this out. We have rewritten the sentence 
           to read "The nuclear equation of state will then stiffens by 
@@
 
-Response: the observer angles for all the studies of 3D simulations have
+Response: The observer angles for all the studies of 3D simulations have
           been added to the text. We appreciate that our data could be 
@@
 
-Response: As stated above, we tested again the trained CNN with 
+Response: As stated above, we again tested the trained CNN with 
           1.08 * 10^6 test samples to achieve FAP values of 0.1%, 0.01%, 
@@
           Claims regarding the ability of the networks in detecting 
-          Galatic CCSN signals if the explosion mechanism is the 
+          Galactic CCSN signals if the explosion mechanism is the 
           neutrino driven mechanism are withdrawn.

### 2020-04-29 Response_to_PRD_reviewers.txt
add a statement to include the use of gaussian noise in the conclusion

@@
           We appreciate that re-running the simulations at closer
-          distances is advised, but doing so would be very 
-          computationally expensive.
+          distances is advised. However, re-running the simulations 
+          at closer distances and generating more testing samples to achieve
+          the requested FAPs are both computationally expensive.
+          We chose to do the latter one as it has the greatest impact on the results 
+          and that aligned more strongly with the referees broader comments.
 
@@
           values of FAP and leave tests using realistic noise for future 
-          work.
+          work. In addition, we modified the first paragraph of conclusion
+          to include a statement about the use of Gaussian noise.
 

### 2020-07-16 main.tex
Fixed plot style
revised paper 2nd

--- 2020-04-17 main.tex
@@
 supernovae out to the Large or even Small Magellanic Clouds. 
-%A Galactic event is likely to be detectable with a network of H+L+VK 
+A neutrino-driven event is likely to be detectable with a network of H+L+VK
+and HLVK if the distances is within $5$ kpc and $3$ kpc respectively.
 %if the explosion mechanism is the neutrino-driven mechanism.  
@@
 is $66\%$ at $60$ kpc for waveforms $\text{R3E1AC}$ and 
-$\text{R4E1FC\_L}$ for networks of H+L+VK.  
-For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, 
-the true alarm probabilities are $49\%$ and $20\%$ for a network of H+L+VK 
-and HLVK respectively. 
+$\text{R4E1FC\_L}$ with a network of H+L+VK.  
+For waveforms $\text{s}20$ and $\text{SFHx}$,
+the true alarm probabilities are $56\%$ for H+L+VK at $7$ kpc and  $50\%$ for HLVK at $5$ kpc 
+respectively.
 All at false alarm probability equal to $0.1\%$. 
@@
 will ensue and continue until the core reaches nuclear density. The nuclear
-equation of state will then stiffens by the strong nuclear force as the core exceeds
+equation of state will then stiffen by the strong nuclear force as the core exceeds
 nuclear density and stops the core collapse. The inner core will bounce back
@@
 mostly been applied to the identifications of detector noise artefacts
-(glitches)~\cite{mukund2017transient, zevin2017gravity, george2017deep} and the
+(glitches)~\cite{mukund2017transient, zevin2017gravity, george2017deep}, the
 detection of astrophysical signals~\cite{george2018deep, gabbard2018matching, astone2018new},
@@
 To train our \ac{CNN}, we use simulated \ac{CCSN} waveforms from a
-number of studies and simulate sources at a range of distances from $10$ to
+number of studies and simulate sources at a range of distances from $0.2$ to
 $200$ kpc for two networks of four \ac{GW} detectors. The first network
@@
 durations, it is necessary to normalise the waveforms before they can be used
-for the generation of the time-series. To do this, we first scale the
+for the generation of the time series. To do this, we first scale the
 amplitudes of the waveforms by moving the sources to $10$ kpc from earth. We
@@
 %
-In this work, we perform simulations for distances equal to $10$, $20$, $30$,
+In this work, we perform simulations for distances equal to $0.2$, $0.5$, $1$, $3$, $5$, $7$, $10$, $20$, $30$,
 $40$, $50$, $60$, $80$, $100$, $150$ and $200$ kpc. If for a training
@@
 %
-The next step is to generate simulated time-series for the \ac{GW} detectors in
+The next step is to generate simulated time series for the \ac{GW} detectors in
 a network using $\bold{S}(t)$.
-%The input data consist of simulated time-series from a network of \ac{GW}
+%The input data consist of simulated time series from a network of \ac{GW}
 %detectors.
 Since the purpose of building a \ac{CNN} is to categorise an input data sample
-into three exclusive classes, in total three types of time-series are
+into three exclusive classes, in total three types of time series are
 generated.  For the time series containing either a magnetorotational signal or
@@
 %
-\begin{equation}
+\begin{multline}
 \bold{d}_j(\alpha, \delta, T, p)=
@@
 \begin{cases}
-\bold{N}_j(T)~~~~~~~~~~~~~~~~~T < T_{\text{max}} p; \\
+\bold{N}_j(T)~~~~~~~~~~~~~~~~~T < T_{\text{max}} p,~T > \tau + T_{\text{max}} p; \\
 \bold{N}_j(T) + \bold{h}_j(\alpha, \delta, t)~ T_{\text{max}} p \leq T \leq \tau + T_{\text{max}} p; \\
-\bold{N}_j(T)~~~~~~~~~~~~~~~~~T > \tau + T_{\text{max}} p, \\
 \end{cases}
-\end{equation}
+\end{multline}
 %
@@
 the signals always starting at the same place.
-For each time-series of the background noise class, independently simulated Gaussian
+For each time series of the background noise class, independently simulated Gaussian
 background noise of the
@@
 iterating over $\bold{S}(t)$ until for each waveform in $\bold{S}(t)$, we have
-$31$ data samples $\bold{d}$ generated using the procedure described above.
+$310$ data samples $\bold{d}$ generated using the procedure described above.
 This step is essential for the \ac{CNN} to learn the features of the waveforms
@@
 In Fig.~\ref{fig:sample}, we show a representative example of a pre-processed
-input time-series for a single detector. A data sample consists of such a
-time-series containing a signal from the same source or simply background noise
+input time series for a single detector. A data sample consists of such a
+time series containing a signal from the same source or simply background noise
 from all the detectors in the network. The data samples are then split into 3
@@
 \includegraphics[width=0.475\textwidth]{datasample.png}
-\caption{A representative example of the simulated time-series used to
-train/validate/test the \ac{CNN}. The blue shows a whitened time-series with a
+\caption{A representative example of the simulated time series used to
+train/validate/test the \ac{CNN}. The blue shows a whitened time series with a
 signal added to Gaussian noise generated using the power spectral density of \ac{aLIGO}. 
@@
 %
+
+Although the \ac{CNN} has been trained for all the distances, 
+for the neutrino-driven mechanism, only results for distances $\leq 10$ kpc
+will be shown. Similarly, only results for distances $\geq 10$ kpc will be displayed 
+for the magnetorotational mechanism,. 
+This is because the intrinsic amplitudes for magnetorotational signals are
+higher than those of neutrino-driven signals and the detectable distances for the two mechanisms 
+are generally different.
 In Fig.~\ref{fig:ROClog}, we show the \acp{ROC} for both of the \ac{CCSN}
 mechanisms and \ac{GW} detector networks tested in this work. For simplicity,
-we show only the results for three distances, namely, $20$, $60$ and $100$ kpc.
-For all the distances tested, the \ac{CNN} achieves a higher \ac{TAP} for any
-given \acp{FAP} for magnetorotational than neutrino-driven signals.  That is
-not surprising as the intrinsic amplitudes for magnetorotational signals are
-higher than those of neutrino-driven signals.
+for each mechanism, we show only the results for three distances, 
+namely, $0.2$, $1$, $7$ kpc for the neutrino-driven mechanism, and 
+$20$, $60$ and $100$ kpc for the magnetorotational mechanism.
 
@@
      \begin{center}
-        \subfigure[]{
+        \subfigure[the neutrino-driven mechanism]{
             \label{fig:ROClog1}
@@
         }\quad
-        \subfigure[]{
+        \subfigure[the magnetorotational mechanism]{
             \label{fig:ROClog2}
@@
 \ac{CNN} for \ac{CCSN} signals of different explosion mechanisms at three
-distances, $20$, $60$, and $100$ kpc. The left panel shows the results for the
+distances, $0.2$, $1$ and $7$ kpc for the neutrino-driven mechanism, and $20$, $60$, 
+and $100$ kpc for the magnetorotational mechanism. 
+The left panel shows the results for the
 neutrino-driven mechanism, while the panel on the right shows those for the
@@
 distance.  This is done by fixing the \ac{FAP} and plotting the \ac{TAP}.  The
-results for three chosen \acp{FAP} values are shown in Fig.~\ref{fig:eff}.  In
-this figure, a similar trend is seen that magnetorotational signals are easier
-for the \ac{CNN} to identify than neutrino-driven signals at a given distance.
+results for three chosen \acp{FAP} values are shown in Fig.~\ref{fig:eff}.  
+%In this figure, a similar trend is seen that magnetorotational signals are easier
+%for the \ac{CNN} to identify than neutrino-driven signals at a given distance.
 For magnetorotational signals from sources located at $50$ kpc and a \ac{FAP}
-of $0.1\%$, the \ac{CNN} achieves a \ac{TAP} of $82\%$ and $66\%$ for the
+of $0.1\%$, the \ac{CNN} obtains a \ac{TAP} of $82\%$ and $66\%$ for the
 networks H+L+VK and HLVK respectively. At more restrict \acp{FAP} such as
@@
 drop to $55\%$, $33\%$ and $16\%$ respectively for \ac{FAP} equal to $0.1\%$.
-On the other hand, it is more difficult for the
-\ac{CNN} to detect and classify the neutrino-driven signals, due to their
-weaker amplitudes. For example, for sources at $10$ kpc, the \ac{CNN} achieves
-a \ac{TAP} of $38\%$ and $10\%$ for H+L+VK and HLVK respectively if the
-\ac{FAP} is $0.1\%$. In Fig.~\ref{fig:eff}, only the values of \ac{TAP} that
-are larger than zero will be plotted.
+On the other hand, it is more difficult for the CNN to detect and classify the
+neutrino-driven signals, due to their weaker amplitudes.
+Nonetheless, the \ac{CNN} obtains a \ac{TAP} of $90\%$ and $75\%$ for sources 
+at $3.0$ kpc at a \ac{FAP} of $0.1\%$ with
+a network of H+L+VK and HLVK respectively.
+The \ac{TAP} drops to  $67\%$ for H+L+VK at $5$ kpc.
+%it is more difficult for the
+%\ac{CNN} to detect and classify the neutrino-driven signals, due to their
+%weaker amplitudes. 
+%For example, for sources at $10$ kpc, the \ac{CNN} achieves
+%a \ac{TAP} of $38\%$ and $10\%$ for H+L+VK and HLVK respectively if the
+%\ac{FAP} is $0.1\%$. In Fig.~\ref{fig:eff}, only the values of \ac{TAP} that
+%are larger than zero will be plotted.
 
@@
      \begin{center}
-        \subfigure[]{
+        \subfigure[the neutrino-driven mechanism]{
             \label{fig:eff1}
@@
         }\quad
-        \subfigure[]{
+        \subfigure[the magnetorotational mechanism]{
             \label{fig:eff2}
@@
 panel shows the results for the neutrino-driven mechanism, while the right
-shows those for the magnetorotational mechanism. In both panels, the solid
-lines show the results for the network H+L+VK, and the dashed lines for HLVK.
+shows those for the magnetorotational mechanism. 
+In both panels, the solid lines show the results for the network H+L+VK, and the dashed lines for HLVK.
 Three \acp{FAP} values are chosen, blue for \ac{FAP} $=1\%$, green for \ac{FAP}
@@
      \begin{center}
-        \subfigure[]{
+        \subfigure[the neutrino-driven mechanism]{
             \label{fig:ROCfixed1}
@@
         }\quad
-        \subfigure[]{
+        \subfigure[the magnetorotational mechanism]{
             \label{fig:ROCfixed2}
@@
     \end{center}
-    \caption{Efficiency curves showing the ability of the \ac{CNN} in
-distinguishing input data with a fixed decision threshold $(50\%)$, 
-and their corresponding \acp{FAP} and \ac{TAP}. 
-The left panel shows the results for the neutrino-driven mechanism, and
-the right shows that for the magnetorotational mechanism. In both panels, the
-solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the
+    \caption{The ability of the \ac{CNN} in
+distinguishing input data with a fixed decision threshold $(90\%)$, 
+and their corresponding \acp{FAP} and \acp{TAP}. 
+The left panel shows the results for the neutrino-driven mechanism.
+The right panel shows the results for the magnetorotational mechanism. 
+In both panels, the solid lines show the \acp{TAP} and \acp{FAP} 
+for the network H+L+VK, and the
 dashed lines show those for HLVK.\label{fig:ROCfixed}}
@@
 a threshold probability of $90\%$. 
-This value is chosen so that low values of \ac{FAP} can be maintained throughout all tested distances
+This value is chosen so that low values of \ac{FAP} can be maintained throughout all 
+tested distances
 as illustrated by the right y-axes of the figures.
@@
 %The \acp{TAP} decrease to $10\%$ and $9\%$ for sources at $150$ and $200$ kpc.
-For all distances, the \ac{CNN} maintains a \ac{FAP} no larger than $0.3\%$ for
-both networks regarding magnetorotational waveforms. For neutrino-driven
-signals, we show that H+L+VK has a \acp{TAP} of $44\%$ at $10$ kpc while it
-is $11\%$ at $10$ kpc for HLVK with \acp{FAP} $< 0.3\%$.
-As we have chosen a large value of threshold, the values of \ac{TAP} decreases rapidly 
-as the distance increases. Again, only the values of \ac{TAP} larger than zero will be plotted.
-
-It should be noted that the results presented in this section are
+For neutrino-driven
+signals, we show that H+L+VK achieves a \ac{TAP} of $90\%$ for sources at $3$ kpc 
+and still $50\%$ at $7$ kpc. 
+For HLVK, the \ac{TAP} for $3$ kpc are $78\%$.
+For both mechanisms, the \ac{CNN} maintains a \ac{FAP} no larger than $0.3\%$ for
+the displayed distances.
+
+Although the waveforms used in different studies in the literatures 
+are not entirely identical and that the statistics used are not always directly comparable,
+by comparing the results obtained from the \ac{CNN} with those existing in the literature
+such as \cite{astone2018new, gill2018enhancing, hayama2015coherent, roma2019astrophysics}, 
+our \ac{CNN} has demonstrated a detection and classification efficiency that is at least consistent 
+or in some cases more promising for both mechanisms.
+In addition, it should be noted that the results presented in this section are
 averaged over all the data samples in the testing samples. The performance on
@@
 of the waveform. 
-In addition, if an accurate time window and/or localisation of en event are available
-(e.g. with electromagnetic and/or neutrino observations), 
+Further, if an accurate time window and/or localisation 
+of en event are available (e.g. with electromagnetic and/or neutrino observations), 
 such low values of \ac{FAP} may not be necessary. 
+Finally, as mentioned, the magnetorotational waveforms
+used in this study are linearly polarised and only have the $h_{+}$ polarisation. 
+This could potentially cause the \ac{CNN} to perform differently in reality. 
+This problem can be solved by training the \ac{CNN} 
+using $3$D simulated waveforms when a larger number of them become available.
+
 %Also shown in this figure is a curve showing the \ac{TAP} for all the classes, defined by,
@@
      \begin{center}
-        \subfigure[]{
+        \subfigure[the neutrino-driven mechanism]{
             \label{fig:extra_waveform_test_neu}
@@
         }\quad
-        \subfigure[]{
+        \subfigure[the magnetorotational mechanism]{
             \label{fig:extra_waveform_test_mag}
@@
 these waveforms out to the satellite galaxies within such a distance.
-For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $49\%$ and $20\%$ for the two
-networks if the sources are at $10$ kpc and the \ac{FAP} is $0.1\%$.  The
-efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
+For waveforms $\text{s}20$ and $\text{SFHx}$ and a \ac{FAP} of $0.1\%$, 
+the \acp{TAP} for H+L+VK are $91\%$ and $56\%$ for $3$ and $7$ kpc respectively.
+For HLVK, the \acp{TAP} is $79\%$ and $50\%$ at $3$ and $5$ kpc.
+The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
 higher than that for the neutrino-driven mechanism in Fig.~\ref{fig:eff} for
@@
 We have demonstrated that a \ac{CNN} can be applied for the purpose of
-distinguishing \ac{GW} detector time-series among pure background noise and
+distinguishing \ac{GW} detector time series among pure background noise and
 \ac{CCSN} explosion mechanisms. We have trained, valided, and tested 
 the \ac{CNN} using $1.26\times10^{6}$ samples of simulated time series for each distance at a
-number of distances from $10$ kpc to $200$ kpc. The data samples for each
-class consisted of approximately $4.2\times10^5$ samples.
-
+number of distances from $0.2$ kpc to $200$ kpc, where the background noise is Gaussian noise. 
+The data samples for each class consisted of approximately $4.2\times10^5$ samples. 
+Our results have been shown to be at least consistent with or in some situations may even be 
+more promising than the results in the literature.
 %
@@
 %
+
 We have shown that with a \ac{GW} detector network of HLVK, when the \ac{FAP}
@@
 Small Magellanic Clouds are within this distance. If the distance is extended
-to $150$ or $200$ kpc, a \ac{TAP} of $33\%$ or $16\%$ respectively are still
+to $150$ or $200$ kpc, a \ac{TAP} of $33\%$ or $16\%$ respectively are
 achievable for H+L+VK, indicating a small possibility of detections within
@@
 %
-For the neutrino-driven mechanism, the weaker amplitudes of the waveforms
-result in lower \acp{TAP} at the same distances.  For sources at $10$ kpc, the
-trained \ac{CNN}, with a \ac{FAP} of $0.1\%$, achieved a \ac{TAP} of $10\%$ and
-$38\%$ for HLVK and H+L+VK respectively. 
-%
-% statement about out of treaining data extra test samples
+
+For the neutrino-driven mechanism, with a network of HLVK or H+L+VK, 
+a \ac{TAP} of $75\%$ or $90\%$ respectively was shown for sources at $3$ kpc. 
+The \acp{TAP} drop to $67\%$ for H+L+VK for sources at $5$ kpc. 
+The closer detectable distances are a results of the intrinsic weaker amplitudes of the signals.
+%
+% statement about out of training data extra test samples
 %
@@
 For HLVK and sources at $40$ kpc, the \ac{TAP} is $54\%$.
-For waveforms $\text{s}20$ and $\text{SFHx}$ at $10$ kpc, the \acp{TAP} are $49\%$ and
-$20\%$ for the two networks respectively. All at \ac{FAP} of $0.1\%$. 
+For waveforms $\text{s}20$ and $\text{SFHx}$, the \acp{TAP} are $50\%$ for HLVK at $5$ kpc 
+and $56\%$ for H+L+VK at $7$ kpc. All at \ac{FAP} of $0.1\%$. 
 The results prove the possibility of
@@
 Technology (COST) action CA17137. 
-
+\clearpage 
 \bibliography{main}

### 2020-07-16 main.tex
correct misspelled words

@@
 distinguishing \ac{GW} detector time series among pure background noise and
-\ac{CCSN} explosion mechanisms. We have trained, valided, and tested 
+\ac{CCSN} explosion mechanisms. We have trained, validated, and tested 
 the \ac{CNN} using $1.26\times10^{6}$ samples of simulated time series for each distance at a
